### 2022-05-09 paper/main.tex
Create main.tex

\documentclass[two column]{article}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphicx}

\graphicspath{ {./images/} }

% Keywords command
\providecommand{\keywords}[1]
{
  \small
  \textbf{\textit{Keywords:}} #1
}

\title{\textbf{Elimination Of Jump Statements}}
\author{\textbf{author}}
\date{May 2022}

\begin{document}

\maketitle

\begin{abstract}
In this article we raise the problem of the so-called Jump Statements. Getting rid of the use of operators such as \textbf{goto}, \textbf{return}, \textbf{continue}, \textbf{break}, and \textbf{throw} in code is the task of most modern programming languages, as the program becomes unreadable, poorly optimized and the probability of fixing errors in such a program is extremely high.

The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing \textbf{GOTO} objects into a semantically similar one, but without using them.
\end{abstract}

\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}

\section{Introduction}
The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of \textbf{goto} has disastrous effect and proposed to remove it from all programming languages, Even though a few years later Knuth showed a manner for structuring programs with the \textbf{goto} statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating \textbf{goto} statements.

Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called \textbf{GOTO}-patches, which are design techniques for eliminating \textbf{goto} statements; Erosa suggested an algorithm fir automatic elimination of \textbf{goto} statements in C; Zegour explained how \textbf{goto} elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing \textbf{goto} with IF-THEN-ELSE constructs; Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate \textbf{goto} during migration of legacy code to Java,

To our knowledge, there is still no software tool available, which would implement any of the suggested methods and enable automatic elimination of jump statements in programs. However, the main reason for finding a solution to this problem for us is the development of EOLANG, an experimental \(\varphi\)-calculus-based object-oriented programming language, which is used as an Intermediate Representation (IR) in Polystat, a new polyglot static analyzer. The method of program analysis used in Polystat is functional: we find bugs by 1) transforming source code to formulas of \(\varphi\)-calculus, 2) mapping them to \(\lambda\)-terms, and 3) reasoning on terms using their inverses.

Such an analysis works well with statements which are easy to map to functions, for example if and switch. Jump statements, on the other hand, can't be easily mapped to functions, The presence of jump statements in the source code makes it impossible to use the functional method of analysis just explained.

We propose an algorithm that replaces code fragments using the GOTO object with similar fragments, but without using it. Two algorithms are semantically equivalent if with the same set of input arguments they return the same results.

\section{Methods}
In EOLANG, all jump statements are implemented as a single \textbf{GOTO}-object. The main task is to distinguish what this object is in different places of the program - \textbf{goto}, \textbf{continue}, \textbf{break} or \textbf{return}. We need to learn to recognize the type of implied object and replace it with similar code accordingly.

\subsection{GOTO statement}
There are two types of \textbf{goto}-statements in the program - "forward jumps" and "backward jumps".
\subsubsection{forward jumps}
In a program "forward jump" can be used within the body of \textbf{if}-statement. In this case program will look like this:

\includegraphics{forward1}

Let's look at the following code on EOLANG:
\begin{lstlisting}
[x] > f
 memory > r
 seq > @
  r.write 0
  goto
   [g]
    seq > @
     if.
      x.eq 0
      g.forward
      TRUE
     r.write (42.div x)
  r
\end{lstlisting}

In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within \textbf{if}-statement is TRUE. By inverting the condition in \textbf{if}-statement, you can write the code block between the \textbf{goto} call and its label into a separate \textbf{if}-statement:

\includegraphics{forward2}

\begin{lstlisting}
[x] > f
 memory > r
 seq > @
  r.write 0
  if.
   not (x.eq 0)?? IS THIS SYNTAX WRONG??
   r.write (42.div x)
   TRUE
  r
\end{lstlisting}

\subsubsection{backward jumps}
Backward jump is usually used similarly to a while loop and can be easily replaced by it (considering programs that are compiled and executed).

??? INSERT IMAGE

Consider the following code:
\begin{lstlisting}
[] > f
 memory > i
 seq > @
  i.write 1
  goto
   [g]
    seq > @
     i.write (i.add 1)
     if.
      i.less 10
      g.backward
      TRUE
 stdout "Finished!"
\end{lstlisting}

In this case we could easily replace construction using \textbf{goto} with the \textbf{while}:
\begin{lstlisting}
[] > f
 memory > i
 seq > @
  i.write 1
  i.write (i.add 1)
  while.
   i.less 10
   seq
    i.write (i.add 1)
 stdout "Finished!"
\end{lstlisting}

\subsubsection{Complex case}
??? when forward and then backward jump

\subsection{continue}

\subsection{break}

\end{document}
\endinput

### 2022-05-09 paper/main.tex
Update main.tex

@@
 Getting rid of the use of operators such as \textbf{goto}, \textbf{return}, \textbf{continue}, \textbf{break}, and \textbf{throw} in code is the task of most modern programming languages, as the program becomes unreadable, poorly optimized and the probability of fixing errors in such a program is extremely high.
+We are trying to answer the following research question: “Is it possible to completely get rid of the \textbf{GOTO} operator in the code?”
 
-The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing \textbf{GOTO} objects into a semantically similar one, but without using them.
 \end{abstract}
@@
 
+The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing \textbf{GOTO} objects into a semantically similar one, but without using them.
 We propose an algorithm that replaces code fragments using the GOTO object with similar fragments, but without using it.
-Two algorithms are semantically equivalent if with the same set of input arguments they return the same results.
+We claim that two algorithms are semantically equivalent if with the same set of input arguments they return the same results.
 
@@
 In EOLANG, all jump statements are implemented as a single \textbf{GOTO}-object.
-The main task is to distinguish what this object is in different places of the program - \textbf{goto}, \textbf{continue}, \textbf{break} or \textbf{return}.
-We need to learn to recognize the type of implied object and replace it with similar code accordingly.
+The \textbf{GOTO}-object represents two types of jumps: \textit{forward jump} and \textit{backward jump}.
+Operators such as \textbf{break}, \textbf{return} and \textbf{goto forward} are implemented via \textit{forward jump}; \textbf{continue} and \textbf{goto backward} are implemented via \textit{backward jump}.
 
-\subsection{GOTO statement}
-There are two types of \textbf{goto}-statements in the program - "forward jumps" and "backward jumps".
-\subsubsection{forward jumps}
-In a program "forward jump" can be used within the body of \textbf{if}-statement. In this case program will look like this:
+For each of them, a semantically identical replacement is required so that the algorithm returns the same output with the same input parameters.
+
+\subsection{forward jump}
+\textbf{\textit{Goto forward}} is implemented in the language as:
+\begin{lstlisting}
++import org.eolang.gray.goto
++import org.eolang.io.stdout
+
+goto
+ [g]
+  seq
+   g.forward TRUE
+   stdout "Will never be printed"
+\end{lstlisting}
+
+In a program \textit{forward jump} can be used within the body of \textbf{if}-statement. In this case program will look like this:
 
@@
 
+Modified code:
 \begin{lstlisting}
@@
   if.
-   not (x.eq 0)?? IS THIS SYNTAX WRONG??
+   not. (eq. (x 0))
    r.write (42.div x)
@@
 
-\subsubsection{backward jumps}
+If the program encountered unconditional \textit{forward jump}, we need to transform it as \textbf{goto} with an additional condition: \textbf{if (true) goto forward}.
+Then the replacement occurs just as if the condition exists.
+
+\subsubsection{return}
+As mentioned above, return statement is also implemented via \textit{goto forward} object. Consider the following code:
+\begin{lstlisting}
+[a b] > max
+ goto > @
+  [g]
+   seq > @
+    if.
+     a.greater b
+     g.forward a
+     TRUE
+    b
+\end{lstlisting}
+When using goto as \textit{return} statement, an additional attribute is added to the \textbf{goto}-object, similar to the return value of a procedure.
+In this case, it can easily be transformed into an \textbf{if}-statement as shown in the paragraph above:
+\begin{lstlisting}
+[a b] > max
+ if.
+  a.greater b
+  a
+  TRUE
+ b
+\end{lstlisting}
+
+\subsubsection{break}
+Break is a control-flow statement which could also be implemented using \textbf{goto forward}.
+Since the break statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
+In this case, we need to invert the \textit{if}-condition and add it to the condition of the loop with the logical operator \textit{AND}.
+After that, we easily get rid of the \textit{if}-condition itself.
+
+Let's look at the example:
+\begin{lstlisting}
+[]
+ memory > i
+ goto > @
+  [g]
+   seq > @
+    while.
+     i.less 10
+     seq
+      i.write (i.add 1)
+      if.
+       eq. (i.mod 5 0)
+       g.forward
+       TRUE
+\end{lstlisting}
+
+We invert \textit{condition} and add it to \textbf{while}-condition:
+\begin{lstlisting}
+[]
+ memory > i
+ seq > @
+  while.
+   and.
+    i.less 10
+    not. (eq. (i.mod 5 0))
+   seq
+    i.write (i.add 1)
+\end{lstlisting}
+
+\subsection{backward jumps}
 Backward jump is usually used similarly to a while loop and can be easily replaced by it (considering programs that are compiled and executed).
+Substitution will look like \textbf{do-while} construction.
 
-??? INSERT IMAGE
+\includegraphics{backward1}
 
@@
 In this case we could easily replace construction using \textbf{goto} with the \textbf{while}:
+
+\includegraphics{backward2}
+
 \begin{lstlisting}
@@
 
-\subsubsection{Complex case}
+\subsubsection{continue}
+Continue is also a control-flow statement, which occurs in loops and is implemented through the EO object \textbf{GOTO}.
+In order to replace it, we need to invert the \textit{if}-condition in the loop and all the statements that occur after \textbf{goto} are put in the \textit{if} body with the inverted condition.
+
+Example of using \textit{continue} via \textbf{goto backward}:
+\begin{lstlisting}
+[]
+ memory > i
+ goto > @
+  [g]
+   seq > @
+    while.
+     i.less 10
+     seq
+      i.write (i.add 1)
+      if.
+       eq. (i.mod 5 0)
+       g.backward
+       TRUE
+      stdout "Not divisible by 5!\n"
+\end{lstlisting}
+
+Replace the GOTO object with the described method:
+\begin{lstlisting}
+[]
+ memory > i
+ seq > @
+ while.
+  i.less 10
+  seq
+   i.write (i.add 1)
+   if.
+    not. (eq. (i.mod 5 0))
+    stdout "Not divisible by 5!\n"
+    TRUE
+\end{lstlisting}
+
+\subsection{Complex cases}
 ??? when forward and then backward jump
+??? and mb add throw ???
 
-\subsection{continue}
-
-\subsection{break}
+\subsection{Final algorithm}
+Knowing how to replace a goto-forward statement and a goto-backward statement, we can present a final algorithm to get rid of all the GOTO objects in the EOlang code.
 

### 2022-05-10 paper/main.tex
Update main.tex

@@
 \usepackage{graphicx}
+\usepackage{xcolor}
 
@@
 
+\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+
+\lstdefinestyle{mystyle}{
+  %%backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
+  %%keywordstyle=\color{magenta},
+  numberstyle=\tiny\color{codegray},
+  %%stringstyle=\color{codepurple},
+  basicstyle=\ttfamily\footnotesize,
+  breakatwhitespace=false,         
+  breaklines=true,
+  frame=leftline,
+  captionpos=b,                    
+  keepspaces=true,                 
+  numbers=left,                    
+  numbersep=5pt,                  
+  showspaces=false,                
+  showstringspaces=false,
+  showtabs=false,                  
+  tabsize=2
+}
+
 \title{\textbf{Elimination Of Jump Statements}}
@@
 
+\lstset{style=mystyle}
 \begin{document}
@@
 \section{Introduction}
-The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of \textbf{goto} has disastrous effect and proposed to remove it from all programming languages, Even though a few years later Knuth showed a manner for structuring programs with the \textbf{goto} statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating \textbf{goto} statements.
+The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages, Even though a few years later Knuth showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements.
 
-Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called \textbf{GOTO}-patches, which are design techniques for eliminating \textbf{goto} statements; Erosa suggested an algorithm fir automatic elimination of \textbf{goto} statements in C; Zegour explained how \textbf{goto} elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing \textbf{goto} with IF-THEN-ELSE constructs; Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate \textbf{goto} during migration of legacy code to Java,
+Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements; Erosa suggested an algorithm fir automatic elimination of GOTO statements in C; Zegour explained how GOTO elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs; Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate GOTO during migration of legacy code to Java,
 
@@
 
-The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing \textbf{GOTO} objects into a semantically similar one, but without using them.
+The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing GOTO objects into a semantically similar one, but without using them.
 We propose an algorithm that replaces code fragments using the GOTO object with similar fragments, but without using it.
@@
 \section{Methods}
-In EOLANG, all jump statements are implemented as a single \textbf{GOTO}-object.
-The \textbf{GOTO}-object represents two types of jumps: \textit{forward jump} and \textit{backward jump}.
+In EOLANG, all jump statements are implemented as a single \textbf{goto}-object.
+The \textbf{goto}-object represents two types of jumps: \textit{forward jump} and \textit{backward jump}.
 Operators such as \textbf{break}, \textbf{return} and \textbf{goto forward} are implemented via \textit{forward jump}; \textbf{continue} and \textbf{goto backward} are implemented via \textit{backward jump}.
 
+We need to find a solution for both, how to replace them in different situations.
 For each of them, a semantically identical replacement is required so that the algorithm returns the same output with the same input parameters.
@@
 \subsection{forward jump}
-\textbf{\textit{Goto forward}} is implemented in the language as:
+\textbf{Goto forward} is implemented in EOLANG as:
 \begin{lstlisting}
@@
 
-In a program \textit{forward jump} can be used within the body of \textbf{if}-statement. In this case program will look like this:
+In a program \textit{forward jump} can be used within the body of \textit{if-statement}.
+Structure of an algorithm can be represented by a scheme on Figure 1.
+Inside \textit{if-statement} are located some statements (stmt1), after that \textbf{goto-forward}, some other statements (stmt2) and the label of \textbf{goto}, where the program will continue to work if the condition in \textit{if-statement} was equal to \textit{TRUE}.
 
+\begin{figure}[h]
+    \centering
     \includegraphics{forward1}
+    \caption{\textit{forward jump} scheme}
+    \label{fig:my_label}
+\end{figure}
 
-Let's look at the following code on EOLANG:
+Let's look at the following code:
 \begin{lstlisting}
@@
 
-In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within \textbf{if}-statement is TRUE.
-By inverting the condition in \textbf{if}-statement, you can write the code block between the \textbf{goto} call and its label into a separate \textbf{if}-statement:
+In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within \textit{if-statement} is TRUE.
+By inverting the condition, you can write the code block between the \textbf{goto} call and its label into a separate \textit{if-statement}.
+This approach is illustrated in Figure 2.
 
+\begin{figure}[h]
+    \centering
     \includegraphics{forward2}
+    \caption{\textit{forward jump} elimination}
+    \label{fig:my_label}
+\end{figure}
 
@@
 \subsubsection{return}
-As mentioned above, return statement is also implemented via \textit{goto forward} object. Consider the following code:
+As mentioned above, \textbf{return} statement is also implemented via \textit{goto forward} object. Consider the following code:
 \begin{lstlisting}
@@
 \subsubsection{break}
-Break is a control-flow statement which could also be implemented using \textbf{goto forward}.
-Since the break statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
+\textit{Break} is a control-flow statement which could also be implemented using \textbf{goto forward}.
+Since the \textit{break} statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
 In this case, we need to invert the \textit{if}-condition and add it to the condition of the loop with the logical operator \textit{AND}.
@@
 
-\subsection{backward jumps}
-Backward jump is usually used similarly to a while loop and can be easily replaced by it (considering programs that are compiled and executed).
+Thus, at each iteration of the \textit{while} loop, the added condition will be checked, and as soon as it becomes \textit{FALSE}, the loop will be terminated because of the \textit{AND} statement.
+
+\subsection{backward jump}
+\textit{Backward jump} is usually used similarly to a while loop and can be easily replaced by it (considering programs that are compiled and executed).
 Substitution will look like \textbf{do-while} construction.
 
+\begin{figure}[h]
+    \centering
     \includegraphics{backward1}
+    \caption{\textit{backward jump} scheme}
+    \label{fig:my_label}
+\end{figure}
 
@@
 
-In this case we could easily replace construction using \textbf{goto} with the \textbf{while}:
+\textbf{Goto backward} will work as long as the condition in if-statement is TRUE. In this case we could easily replace construction using \textbf{goto} with the \textit{while}:
 
+\begin{figure}[h]
+    \centering
     \includegraphics{backward2}
+    \caption{\textit{backward jump} elimination}
+    \label{fig:my_label}
+\end{figure}
 
@@
 
+The first iteration will always work, and all subsequent ones only as long as the condition in the loop is \textit{TRUE}.
+
 \subsubsection{continue}
-Continue is also a control-flow statement, which occurs in loops and is implemented through the EO object \textbf{GOTO}.
+\textit{Continue} is also a control-flow statement, which occurs in loops and is implemented through the EO object \textbf{GOTO}.
 In order to replace it, we need to invert the \textit{if}-condition in the loop and all the statements that occur after \textbf{goto} are put in the \textit{if} body with the inverted condition.
@@
 
-Replace the GOTO object with the described method:
+Since the \textbf{while} loop is an attribute of the \textbf{goto} object, \textit{if-condition} is executed a "jump up" that emulates the \textit{continue} statement.
+To get rid of this "jump" we should replace the GOTO object with the method described above:
 \begin{lstlisting}

### 2022-05-17 paper/main.tex
Update main.tex

@@
 
-\begin{abstract}
-In this article we raise the problem of the so-called Jump Statements.
-Getting rid of the use of operators such as \textbf{goto}, \textbf{return}, \textbf{continue}, \textbf{break}, and \textbf{throw} in code is the task of most modern programming languages, as the program becomes unreadable, poorly optimized and the probability of fixing errors in such a program is extremely high.
-We are trying to answer the following research question: “Is it possible to completely get rid of the \textbf{GOTO} operator in the code?”
-
-\end{abstract}
+%%\begin{abstract}
+%%In this article we raise the problem of the so-called Jump Statements.
+Getting rid of the use of operators such as goto, return, continue, break, and throw in code is the task of most modern programming languages, as the program becomes unreadable, poorly optimized and the probability of fixing errors in such a program is extremely high.
+%%We are trying to answer the following research question: “Is it possible to completely get rid of the GOTO operator in the code?”
+%%\end{abstract}
 
@@
 \section{Introduction}
-The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages, Even though a few years later Knuth showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements.
+The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages,
+Even though a few years later Knuth showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements.
 
-Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements; Erosa suggested an algorithm fir automatic elimination of GOTO statements in C; Zegour explained how GOTO elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs; Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate GOTO during migration of legacy code to Java,
+Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements;
+Erosa suggested an algorithm fir automatic elimination of GOTO statements in C;
+Zegour explained how GOTO elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
+Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate GOTO during migration of legacy code to Java,
 
 To our knowledge, there is still no software tool available, which would implement any of the suggested methods and enable automatic elimination of jump statements in programs.
-However, the main reason for finding a solution to this problem for us is the development of EOLANG, an experimental \(\varphi\)-calculus-based object-oriented programming language, which is used as an Intermediate Representation (IR) in Polystat, a new polyglot static analyzer.
-The method of program analysis used in Polystat is functional: we find bugs by 1) transforming source code to formulas of \(\varphi\)-calculus, 2) mapping them to \(\lambda\)-terms, and 3) reasoning on terms using their inverses.
+However, the main reason for finding a solution to this problem for us is the development of EOLANG, an experimental $\varphi$-calculus-based object-oriented programming language, which is used as an Intermediate Representation (IR) in Polystat, a new polyglot static analyzer.
+The method of program analysis used in Polystat is functional: we find bugs by 1) transforming source code to formulas of $\varphi$-calculus, 2) mapping them to $\lambda$-terms, and 3) reasoning on terms using their inverses.
 
@@
 \section{Methods}
-In EOLANG, all jump statements are implemented as a single \textbf{goto}-object.
-The \textbf{goto}-object represents two types of jumps: \textit{forward jump} and \textit{backward jump}.
-Operators such as \textbf{break}, \textbf{return} and \textbf{goto forward} are implemented via \textit{forward jump}; \textbf{continue} and \textbf{goto backward} are implemented via \textit{backward jump}.
+In EOLANG, all jump statements are implemented as a single goto-object. The goto-object represents two types of jumps: forward jump and backward jump.
+Operators such as break, return and goto forward are implemented via forward jump; continue and goto backward are implemented via backward jump.
 
@@
 \subsection{forward jump}
-\textbf{Goto forward} is implemented in EOLANG as:
+Goto forward is implemented in EOLANG as:
 \begin{lstlisting}
@@
 
-In a program \textit{forward jump} can be used within the body of \textit{if-statement}.
+In a program forward jump can be used within the body of if-statement.
 Structure of an algorithm can be represented by a scheme on Figure 1.
-Inside \textit{if-statement} are located some statements (stmt1), after that \textbf{goto-forward}, some other statements (stmt2) and the label of \textbf{goto}, where the program will continue to work if the condition in \textit{if-statement} was equal to \textit{TRUE}.
+Inside if-statement are located some statements (stmt1), after that goto-forward, some other statements (stmt2) and the label of goto, where the program will continue to work if the condition in if-statement was equal to TRUE.
 
-\begin{figure}[h]
+\begin{figure}
     \centering
@@
 
-In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within \textit{if-statement} is TRUE.
-By inverting the condition, you can write the code block between the \textbf{goto} call and its label into a separate \textit{if-statement}.
+In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within if-statement is TRUE.
+By inverting the condition, you can write the code block between the goto call and its label into a separate if-statement.
 This approach is illustrated in Figure 2.
 
-\begin{figure}[h]
+\begin{figure}
     \centering
@@
 
-If the program encountered unconditional \textit{forward jump}, we need to transform it as \textbf{goto} with an additional condition: \textbf{if (true) goto forward}.
+If the program encountered unconditional forward jump, we need to transform it as goto with an additional condition: if (true) goto forward.
 Then the replacement occurs just as if the condition exists.
@@
 \subsubsection{return}
-As mentioned above, \textbf{return} statement is also implemented via \textit{goto forward} object. Consider the following code:
+As mentioned above, return statement is also implemented via goto forward object. Consider the following code:
 \begin{lstlisting}
@@
 \end{lstlisting}
-When using goto as \textit{return} statement, an additional attribute is added to the \textbf{goto}-object, similar to the return value of a procedure.
-In this case, it can easily be transformed into an \textbf{if}-statement as shown in the paragraph above:
+When using goto as return statement, an additional attribute is added to the goto-object, similar to the return value of a procedure.
+In this case, it can easily be transformed into an if-statement as shown in the paragraph above:
 \begin{lstlisting}
@@
  if.
-  a.greater b
+  not. (a.greater b)
+  b
+  TRUE
  a
-  TRUE
- b
 \end{lstlisting}
@@
 \subsubsection{break}
-\textit{Break} is a control-flow statement which could also be implemented using \textbf{goto forward}.
-Since the \textit{break} statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
-In this case, we need to invert the \textit{if}-condition and add it to the condition of the loop with the logical operator \textit{AND}.
-After that, we easily get rid of the \textit{if}-condition itself.
+Break is a control-flow statement which could also be implemented using goto forward.
+Since the break statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
+In this case, we need to invert the if-condition and add it to the condition of the loop with the logical operator AND.
+After that, we easily get rid of the if-condition itself.
 
@@
 
-\textbf{Goto backward} will work as long as the condition in if-statement is TRUE. In this case we could easily replace construction using \textbf{goto} with the \textit{while}:
+\textbf{Goto backward} will work as long as the condition in if-statement is TRUE. In this case we could easily replace construction using \textbf{goto} with the \textit{while} loop:
 
@@
 ??? when forward and then backward jump
-??? and mb add throw ???
+???
+goto obj inside another goto obj????
+and mb add throw ???
 
 \subsection{Final algorithm}
-Knowing how to replace a goto-forward statement and a goto-backward statement, we can present a final algorithm to get rid of all the GOTO objects in the EOlang code.
+Knowing how to replace a \textit{goto-forward} statement and a \textit{goto-backward} statement, we can present a final algorithm to get rid of all the GOTO objects in the EOLANG code.
+First, we have to determine which kind of jump we need to replace: \textit{forward jump} or \textit{backward jump}.
+If several GOTO objects are located inside each other, then we should first replace the internal object, then the one that is located outside, and so on.
+If the \textit{goto forward} object is in front of us, we should check if it has a \textbf{while}-loop attribute to change its condition when replacing this piece of code.
+Also, if a \textit{forward jump} appears in the code, we should consider whether this object has an additional attribute as the return value - then we should return this value in the replaced piece of code.
+In another case, if we have \textit{goto backward}, we should also check for a loop to add an \textit{if-statement} inside it, not create a new \textbf{while} loop.
+
+All \textbf{goto}-objects in a program we will store in the form of a tree to make it more convenient to make replacements going from sons to parents - from more nested objects to external objects.
+
+The pseudocode of the algorithm may look like this:
+
+\begin{lstlisting}
+//find all goto-objects and store them as a tree
+goto_obj[] = ...
+//walk through objects in tree walk order
+for_each curr_obj in goto_obj:
+  //if unconditional goto, add condition
+  if "if." not in curr_obj:
+    add condition "if (true)" as an attribute of obj curr_obj
+
+  if curr_obj.equal goto.forward:
+    // inverting condition
+    curr_cond = !curr_cond
+    if "while." in curr_obj:
+      add curr_cond to while condition with logical operator AND
+    else:
+      add if-condition with curr_cond
+      add stmts that goes after g.forward inside if-body
+      add stmts that goes before g.forward
+  else:
+    if "while." in curr_obj:
+      curr_cond = !curr_cond
+      add if-condition with curr_cond
+      add stmts that goes after g.backward inside if-body
+    else:
+      add stmts before "if."
+      add while-loop with curr_cond condition
+      add stmts which occur when "if." stmt is TRUE
+      add stmts before and inside "if."
+
+  eliminate curr_obj
+\end{lstlisting}
 

### 2022-05-17 paper/ske.tex
Create ske.tex

\documentclass[two column]{article}
\usepackage[utf8]{inputenc}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{xcolor}

\graphicspath{ {./images/} }

% Keywords command
\providecommand{\keywords}[1]
{
  \small
  \textbf{\textit{Keywords:}} #1
}

\definecolor{codegray}{rgb}{0.5,0.5,0.5}

\lstdefinestyle{mystyle}{
  %%backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
  %%keywordstyle=\color{magenta},
  numberstyle=\tiny\color{codegray},
  %%stringstyle=\color{codepurple},
  basicstyle=\ttfamily\footnotesize,
  breakatwhitespace=false,         
  breaklines=true,
  frame=leftline,
  captionpos=b,                    
  keepspaces=true,                 
  numbers=left,                    
  numbersep=5pt,                  
  showspaces=false,                
  showstringspaces=false,
  showtabs=false,                  
  tabsize=2
}

\title{\textbf{Elimination Of Jump Statements}}
\author{\textbf{author}}
\date{May 2022}

\lstset{style=mystyle}
\begin{document}

\maketitle

\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}

\section{Introduction}
The problem is known both computer science and soft-
ware engineering communities for a few decades and formulated by several scientists.

Many of them have offered solutions to this problem. (Look at Related Work)

The presence of jump statements in the source code makes it impossible to use the functional method of analysis.

We are trying to answer the following research question: “Is it possible to completely get rid of the GOTO operator in the code?”

\section{Related work}
To solve related problems, the following works were published:
Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs.
Ramshow proposed an algorithm for Pascal programs.
Ceccato suggested how to eliminate GOTO during migration of legacy code to Java.

To our knowledge, there is still no software tool  which enable automatic elimination of jump statements in programs.

In this article, we will describe an algorithm that will convert a program to EOLANG in such a way that the output returns a semantically equivalent program, but without using the GOTO object.

We will also provide a formal proof of our algorithm, using phi-calculus.

\section{Methods}
In EOLANG, all jump statements are implemented as a
single ATOM-object GOTO. The goto-object represents two types of jumps: forward jump and backward jump.
The algorithm we propose contains two types of transformations for the goto object - forward jump and backward jump.
We also assume that all jumps are conditional. If this is not the case, then we can easily convert an unconditional goto to a conditional goto by adding an additional if (true) condition.

The algorithm itself consists in applying these transformations to replace both types of jumps.

\subsection{forward jump}
Forward jump is implemented as:

(Forward jump object usage code example)

In the simple case, replacing forward jump is reduced to inverting the jump condition and executing statements in reverse order

In cases where forward jump is used to implement return and break, the transformations will look slightly different.

\subsubsection{return}
Forward jump can be used to implement return-statement.

The only difference here is the return parameter on the jump, which we have to return. Transformation is similar to a simple case.

\subsubsection{break}
Break occurs in constructs that emulate the operation of loops - EOLANG implements a generator that works as a while loop.

In this case, the inverted condition is added to the while loop itself with the logical AND operator.

\subsection{backward jump}
Backward jump is implemented as:

(Backward jump object usage code example)

Backward jump works the same as do-while construction in other languages: the first iteration of the loop is always executed, and the next only if the condition is TRUE.
Transformation is to replace a piece of code with a while loop with a backward jump condition.

In cases where backward jump is used to implement continue, the transformation will look slightly different.

\subsubsection{continue}
Backward jump is used to implement continue statement. In this case, the transformation consists in inverting the jump condition and executing the remaining statements in the body of the new if statement.

\subsection{Complex cases}

\subsection{final algorithm}

\section{Results}

\section{Discussion}

\end{document}
\endinput

### 2022-05-24 paper/ske.tex
Update ske.tex

@@
-\documentclass[two column]{article}
+\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
+\settopmatter{printfolios=false,printccs=false,printacmref=false}
+\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
 \usepackage[utf8]{inputenc}
@@
 \usepackage{xcolor}
+\usepackage{ffcode}
 
@@
 
-\lstdefinestyle{mystyle}{
-  %%backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
-  %%keywordstyle=\color{magenta},
-  numberstyle=\tiny\color{codegray},
-  %%stringstyle=\color{codepurple},
-  basicstyle=\ttfamily\footnotesize,
-  breakatwhitespace=false,         
-  breaklines=true,
-  frame=leftline,
-  captionpos=b,                    
-  keepspaces=true,                 
-  numbers=left,                    
-  numbersep=5pt,                  
-  showspaces=false,                
-  showstringspaces=false,
-  showtabs=false,                  
-  tabsize=2
-}
-
-\title{\textbf{Elimination Of Jump Statements}}
+\title{\textbf{Elimination Of Jump Objects}}
 \author{\textbf{author}}
@@
 
-\lstset{style=mystyle}
 \begin{document}
@@
 
-We are trying to answer the following research question: “Is it possible to completely get rid of the GOTO operator in the code?”
+There are an "object-flow" languages where we can control flow through an objects.
+An example of such language is EO (Elementary Objects language).
+This is a strictly object-oriented programming language in which any action is described by creating a new object, or decorating an existing one.
+
+We are trying to answer the following research question: "Is it possible for any program, written on "object-flow" language like EO and containing GOTO objects to find a semantically equivalent program, but without using them?"
 
 \section{Related work}
-To solve related problems, the following works were published:
-Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs.
-Ramshow proposed an algorithm for Pascal programs.
+To solve the problem of eliminating Jump statements in other programming languages, the following works were published:
+Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
+Ramshow proposed an algorithm for Pascal programs;
 Ceccato suggested how to eliminate GOTO during migration of legacy code to Java.
 
-To our knowledge, there is still no software tool  which enable automatic elimination of jump statements in programs.
+To our knowledge, there is still no method which enables automatic elimination of jump objects in programs written in such an object-flow languages.
 
-In this article, we will describe an algorithm that will convert a program to EOLANG in such a way that the output returns a semantically equivalent program, but without using the GOTO object.
+\section{Method}
+In this article, we will describe an algorithm that will convert an EO program in such a way that the output returns a semantically equivalent program, but without using the GOTO object.
 
-We will also provide a formal proof of our algorithm, using phi-calculus.
+Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called atoms. 
+In EO, all jump statements are implemented as a
+single atom-object GOTO. The goto-object represents two types of jumps: goto-forward and goto-backward.
 
-\section{Methods}
-In EOLANG, all jump statements are implemented as a
-single ATOM-object GOTO. The goto-object represents two types of jumps: forward jump and backward jump.
 The algorithm we propose contains two types of transformations for the goto object - forward jump and backward jump.
-We also assume that all jumps are conditional. If this is not the case, then we can easily convert an unconditional goto to a conditional goto by adding an additional if (true) condition.
+We also assume that all jumps are conditional. If this is not the case, then we can easily convert an unconditional goto to a conditional goto by adding an additional condition: \emph{if (true)}.
 
@@
 
-(Forward jump object usage code example)
+\begin{ffcode}
++import org.eolang.gray.goto
++import org.eolang.io.stdout
 
-In the simple case, replacing forward jump is reduced to inverting the jump condition and executing statements in reverse order
+goto
+ [g]
+  seq
+   g.forward TRUE
+   stdout "Will never be printed"
+\end{ffcode}
+
+It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
+If the condition is true, then statements following the goto object itself are executed.
+So we can swap statements and invert the condition into if-statement to get rid of the goto-forward object (Look at Image1).
+
+{INSERT AN IMAGE1}
+
+Let's take a look at the following example of how to use goto-forward:
+\begin{ffcode}
+[x] > f
+ memory > r
+ seq > @
+  r.write 0
+  goto
+   [g]
+    seq > @
+     if.
+      x.eq 0
+      g.forward TRUE
+      TRUE
+     r.write (42.div x)
+  r
+\end{ffcode}
+
+In this case, the jump condition looks like:
+\emph{if (x equals 0)}.
+After the body if-statement there is an expression: \emph{r = 42 / x}.
+By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
+\begin{ffcode}
+[x] > f
+ memory > r
+ seq > @
+  r.write 0
+  if.
+   not. (eq. (x 0))
+   r.write (42.div x)
+   TRUE
+  r
+\end{ffcode}
 
@@
 \subsubsection{return}
-Forward jump can be used to implement return-statement.
+Forward jump can be used to implement the return-statement:
+\begin{ffcode}
+[a b] > max
+ goto > @
+  [g]
+   seq > @
+    if.
+     a.greater b
+     g.forward a
+     TRUE
+    b
+\end{ffcode}
 
-The only difference here is the return parameter on the jump, which we have to return. Transformation is similar to a simple case.
+The only difference here is the return parameter on the jump, which we have to return. Transformation is similar to a simple case, described at Section 3.1 .
+
+So, the transformation will look like this:
+\begin{ffcode}
+[a b] > max
+ if.
+  not. (a.greater b)
+  b
+  TRUE
+ a
+\end{ffcode}
 
 \subsubsection{break}
-Break occurs in constructs that emulate the operation of loops - EOLANG implements a generator that works as a while loop.
+Break occurs in constructs that emulate the operation of loops - EO implements a generator that works as a while loop.
 
-In this case, the inverted condition is added to the while loop itself with the logical AND operator.
+Let's consider how break is implemented on the next example:
+\begin{ffcode}
+[]
+ memory > i
+ goto > @
+  [g]
+   seq > @
+    while.
+     i.less 10
+     seq
+      i.write (i.add 1)
+      if.
+       eq. (i.mod 5 0)
+       g.forward TRUE
+       TRUE
+      stdout "After break!"
+\end{ffcode}
+
+In this case, goto-forward is used to exit the body of the while loop. However, every iteration of a while loop checks its own condition if it is true.
+
+Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false.
+We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
+So by combining the jump condition and the while loop condition do not violate the program logic.
+But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
+So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary variable \emph{flag} that will be TRUE as soon as the jump condition is met.
+Otherwise, all statements that came after the jump in the while loop will be executed.
+So the combined condition of the while loop will look like: while (!flag AND condOfWhile).
+
+In this example, break-statement transformation looks like this:
+\begin{ffcode}
+[]
+ memory > i
+ memory > flag
+ flag.write 0
+ while.
+  and.
+   not. (eq. (flag 1))
+   i.less 10
+  seq
+   i.write (i.add 1)
+   if.
+    not. (eq. (i.mod 5 0))
+    stdout "After break!"
+    flag.write 1
+\end{ffcode}
+
+Thus we reduced the break statement transformation to the transformation described in section 3.1 with inverting the jump condition and replacing the statements places.
 
 \subsection{backward jump}
-Backward jump is implemented as:
+Backward jump in EO is implemented as:
 
-(Backward jump object usage code example)
+\begin{ffcode}
++import org.eolang.gray.goto
++import org.eolang.io.stdout
+
+goto
+ [g]
+  seq
+   stdout "Will be printed forever"
+   g.backward
+\end{ffcode}
 
 Backward jump works the same as do-while construction in other languages: the first iteration of the loop is always executed, and the next only if the condition is TRUE.
+So, all statemets that met before the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop (Look at Image2).
+
+{INSERT AN IMAGE2}
+
+Consider the following code:
+\begin{ffcode}
+[] > f
+ memory > i
+ seq > @
+  i.write 1
+  goto
+   [g]
+    seq > @
+     i.write (i.add 1)
+     if.
+      i.less 10
+      g.backward
+      TRUE
+ stdout "Finished!"
+\end{ffcode}
+
 Transformation is to replace a piece of code with a while loop with a backward jump condition.
+
+Equivalent replacement of the example described above:
+\begin{ffcode}
+[] > f
+ memory > i
+ seq > @
+  i.write 1
+  i.write (i.add 1)
+  while.
+   i.less 10
+   seq
+    i.write (i.add 1)
+ stdout "Finished!"
+\end{ffcode}
 
@@
 \subsubsection{continue}
-Backward jump is used to implement continue statement.
+Backward jump is used to implement continue statement:
+
+\begin{ffcode}
+[]
+ memory > i
+ goto > @
+  [g]
+   seq > @
+    while.
+     i.less 10
+     seq
+      i.write (i.add 1)
+      if.
+       eq. (i.mod 5 0)
+       g.backward
+       TRUE
+      stdout "Not divisible by 5!\n"
+\end{ffcode}
+
+This statement is logically the same as a break statement, except that after a break is executed the entire while loop stops.
+When you execute the continue statement, the next iteration of the loop is simply started.
+So from a logical standpoint, replacing continue statement is identical to replacing break statement described in section 3.1.2, except that now we don't have to create an auxiliary variable to abort the execution of the while loop.
 In this case, the transformation consists in inverting the jump condition and executing the remaining statements in the body of the new if statement.
 
+Modification of the given example code will look like:
+\begin{ffcode}
+[]
+ memory > i
+ seq > @
+ while.
+  i.less 10
+  seq
+   i.write (i.add 1)
+   if.
+    not. (eq. (i.mod 5 0))
+    stdout "Not divisible by 5!\n"
+    TRUE
+\end{ffcode}
+
 \subsection{Complex cases}
+In complex cases, when one goto object is nested in another, the transformations will be similar to cases, described in sections 3.1 - 3.2.
+When Backward jump, we should insert a while loop into the body all the statements that stand between the declaration of the object and the jump itself, as described at Section 3.2 .
+When Forward jump, remember all statements that follow in the body of if-statement where the jump is made and execute these statements after the GOTO object, as decribed at Section 3.1 .
 
-\subsection{final algorithm}
+Consider the following complex example with nested goto-objects:
+\begin{ffcode}
+[g1]
+ ..._1
+ [g2]
+  ..._2
+  [g3]
+   ..._3
+   if.
+    cond
+    g2.forward
+    TRUE
+   ..._4
+   [g4]
+    ..._5
+    if.
+     cond
+     g3.backward
+     TRUE
+    ..._6
+    if.
+     cond
+     g3.forward
+     TRUE
+    ..._7
+   ..._8
+   if.
+    cond
+    g2.backward
+    TRUE
+   ..._9
+  ..._10
+ ..._11
+..._12
+\end{ffcode}
 
-\section{Results}
+Considering all the jumps that appear in the code (the jumps themselves, not the declaration of goto objects), we apply the transformations already discussed and proved by us above one by one.
+
+Applying all the transformations to each encountered goto object, we get the following code:
+\begin{ffcode}
+[g1]
+ ..._1
+ [g2]
+  ..._2
+  [g3]
+   ..._3
+   if.
+    !cond
+
+    seq
+     ..._4
+     [g4]
+      ..._5
+      while.
+       cond
+
+       seq
+        ..._3
+        if.
+         !cond
+         seq
+          ..._4
+          [g4]
+           ..._5
+         TRUE
+
+      ..._6
+      if.
+       !cond
+       seq
+        ..._7
+       TRUE
+     ..._8
+     while.
+      cond
+
+      seq
+       ..._2
+       [g3]
+       ..._3
+       if.
+        !cond
+
+        seq
+         ..._4
+         [g4]
+          ..._5
+          while.
+           cond
+
+           seq
+            ..._3
+            if.
+             !cond
+             seq
+              ..._4
+              [g4]
+               ..._5
+             TRUE
+
+          ..._6
+          if.
+           !cond
+           seq
+            ..._7
+           TRUE
+         ..._8
+        TRUE
+     ..._9
+    TRUE    
+   ..._10 
+ ..._11
+..._12
+\end{ffcode}
+
+\subsection{Final algorithm}
+Summarizing the points above, we can fully describe the algorithm itself.
+It consists of three steps (See Image3).
+The first step is to convert all unconditional goto objects to conditional goto objects.
+In the second step, applying the transformations described above, we replace jumps with semantically equivalent pieces of code.
+In the third step, remove all the declarations of the GOTO objects themselves.
+
+{INSERT IMAGE3}
+
+\section{Conclusion}
+As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the ATOM object GOTO.
+They also showed that the program at the output will contain the same logic as the program at the input (TODO).
 
 \section{Discussion}
+Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, a formal proof makes it possible to remove all GOTO constructs from programs.
 

### 2022-05-27 paper/ske.tex
Update ske.tex

@@
 Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called atoms. 
-In EO, all jump statements are implemented as a
-single atom-object GOTO. The goto-object represents two types of jumps: goto-forward and goto-backward.
+So all jump statements are implemented as a
+single atom-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
 
-The algorithm we propose contains two types of transformations for the goto object - forward jump and backward jump.
-We also assume that all jumps are conditional. If this is not the case, then we can easily convert an unconditional goto to a conditional goto by adding an additional condition: \emph{if (true)}.
+Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can contain others.
+It should be noted that each object in the program has its own level of \emph{nesting} relative to other objects.
 
+\emph{Definition:} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
+
+The solution we propose contains two types of transformations - forward jump and backward jump.
 The algorithm itself consists in applying these transformations to replace both types of jumps.
 
-\subsection{forward jump}
-Forward jump is implemented as:
+\emph{Designations:}
+
+$\sigma$ - Means that there can be an arbitrary number of objects, a chain of nested objects or there can be no objects at all.
+
+$\delta$ - Means that there should necessarily be an object that returns a non-NULL value when accessed.
+
+$\mu$ - Means that there must be an object that returns a boolean value (TRUE/FALSE) when executed.
+
+\newcommand\sgm[1]{$\sigma_#1$}
+\newcommand\dlt[1]{$\delta_#1$}
+\newcommand\m[1]{$\mu_#1$}
+
+%%We also assume that all jumps are conditional. If this is not the case, then we can easily convert an unconditional goto to a conditional goto by adding an additional condition: \emph{if (TRUE)}.
+
+\subsection{Forward jump}
+Goto forward in EO is implemented as:
 
@@
   [g]
-  seq
-   g.forward TRUE
+    |\sgm{1}|
+      g.forward |\dlt{1}|
       stdout "Will never be printed"
@@
 
+It consists of the goto atom-object, the abstract object \emph{g}, and the g.forward attribute.
+Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.
+
+\subsubsection{Simple Forward}
+This is the simplest example of using goto-forward:
+
+\begin{ffcode}
+goto
+  [g]
+    g.forward |\dlt{1}|
+\end{ffcode}
+
+Note that in this example, g.forward is simply an attribute of the abstract object g and is executed as soon as the queue reaches it.
+Our transformation only considers the jumps that are made when a condition for it is fulfilled.
+In cases where there is unconditional jump, first of all we transform it into conditional jump by adding an additional if-statement - if (TRUE).
+This will not violate the program logic, because without the added if-statement, the jump would always be executed, and statements coming after this jump with a nesting not less that the nesting of the abstract object \emph{g} would never be executed:
+
+\begin{ffcode}
+goto
+  [g]
+    if.
+      TRUE
+      g.forward |\dlt{1}|
+      TRUE
+\end{ffcode}
+
+\subsubsection{Goto forward wrapped in an object}
+So, after the conversion described in section 3.1.1, in general cases, forward jumps will look like this:
+\begin{ffcode}
+goto
+  [g]
+    |\sgm{1}|
+      |\sgm{2}|
+      if.
+        |\m{1}|
+        g.forward |\dlt{1}|
+        |\dlt{2}|
+      |\sgm{3}|
+\end{ffcode}
+
+Let's denote lines 20-26 as X.
+
 It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
-If the condition is true, then statements following the goto object itself are executed.
-So we can swap statements and invert the condition into if-statement to get rid of the goto-forward object (Look at Image1).
+Otherwise statements following the goto object itself are executed.
+So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic (Look at Image1).
+
+Also, after replacing the jump, we must create an additional \emph{flag} object, which will change if the jump condition is met, i.e.
+in the new if-statement, the 'ELSE' branch will be executed.
+We need this so that when a series of nested objects are nested one in another, when the jump condition is met, subsequent objects whose nesting is less than the nesting of the original object containing goto forward and more than the abstract object \emph{g} and following after the original object are not executed.
+
+By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example: the \m{1} object must be inverted with not.
+(\m{1}); in 'THEN' brunch of if-statement creates an object \emph{seq} with \dlt{2} and \sgm{3} inside of it; the 'ELSE' branch an object \emph{seq} with \dlt{1} object that was previously called when the jump is made and changes the value of the \emph{flag} object to 1.
 
@@
 
-Let's take a look at the following example of how to use goto-forward:
+Thus, after transformation, the program will look like this:
 \begin{ffcode}
-[x] > f
- memory > r
- seq > @
-  r.write 0
+memory > flag
+flag.write 0
+|\sgm{1}|
+  |\sgm{2}|
+    if.
+      not. (|\m{1}|)
+      seq
+        |\dlt{2}|
+        |\sgm{3}|
+      seq
+        |\dlt{1}|
+        flag.write 1
+\end{ffcode}
+
+Let's denote lines 27-34 as X'.
+
+\subsubsection{Goto forward inside the while-loop}
+In order to realize the functionality of cycles in EO, generators are provided. A generator is a routine that can be used to control the iteration behaviour of a loop.
+
+The language currently provides a while generator, on which other generators are implemented.
+
+A goto-object can also be called inside such a while-loop.
+In this case, the transformation is slightly different from that described in Section 3.1.2, because the behavior of while is different from other objects in the language.
+
+In general, using goto forward inside a while-loop will look like this:
+\begin{ffcode}
 goto
   [g]
-    seq > @
+    |\sgm{0}|
+      while.
+        |\m{0}|
+        |\sgm{1}|
+          |\sgm{2}|
           if.
-      x.eq 0
-      g.forward TRUE
-      TRUE
-     r.write (42.div x)
-  r
+            |\m{1}|
+            g.forward |\dlt{1}|
+            |\dlt{2}|
+          |\sgm{3}|
 \end{ffcode}
 
-In this case, the jump condition looks like:
-\emph{if (x equals 0)}.
-After the body if-statement there is an expression: \emph{r = 42 / x}.
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
-\begin{ffcode}
-[x] > f
- memory > r
- seq > @
-  r.write 0
-  if.
-   not. (eq. (x 0))
-   r.write (42.div x)
-   TRUE
-  r
-\end{ffcode}
-
-In cases where forward jump is used to implement return and break, the transformations will look slightly different.
-
-\subsubsection{return}
-Forward jump can be used to implement the return-statement:
-\begin{ffcode}
-[a b] > max
- goto > @
-  [g]
-   seq > @
-    if.
-     a.greater b
-     g.forward a
-     TRUE
-    b
-\end{ffcode}
-
-The only difference here is the return parameter on the jump, which we have to return. Transformation is similar to a simple case, described at Section 3.1 .
-
-So, the transformation will look like this:
-\begin{ffcode}
-[a b] > max
- if.
-  not. (a.greater b)
-  b
-  TRUE
- a
-\end{ffcode}
-
-\subsubsection{break}
-Break occurs in constructs that emulate the operation of loops - EO implements a generator that works as a while loop.
-
-Let's consider how break is implemented on the next example:
-\begin{ffcode}
-[]
- memory > i
- goto > @
-  [g]
-   seq > @
-    while.
-     i.less 10
-     seq
-      i.write (i.add 1)
-      if.
-       eq. (i.mod 5 0)
-       g.forward TRUE
-       TRUE
-      stdout "After break!"
-\end{ffcode}
+Let's denote lines 37-46 as Y.
 
@@
 But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
-So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary variable \emph{flag} that will be TRUE as soon as the jump condition is met.
+So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
 Otherwise, all statements that came after the jump in the while loop will be executed.
@@
 
-In this example, break-statement transformation looks like this:
+Thus, transformation will look like this:
 \begin{ffcode}
-[]
- memory > i
 memory > flag
@@
     not. (eq. (flag 1))
-   i.less 10
+    |\m{0}|
+  |\sgm{1}|
+    |\sgm{2}|
+    if.
+      not. (|\m{1}|)
       seq
-   i.write (i.add 1)
-   if.
-    not. (eq. (i.mod 5 0))
-    stdout "After break!"
+        |\dlt{2}|
+        |\sgm{3}|
+      seq
+        |\dlt{1}|
         flag.write 1
@@
 
-Thus we reduced the break statement transformation to the transformation described in section 3.1 with inverting the jump condition and replacing the statements places.
+Let's denote lines 49-62 as Y'.
+
+We create an additional \emph{flag} object that will be equal to 1 when the jump condition is triggered and add this condition to the loop body; modify if-statement as described in Section 3.1.2, except that in the 'ELSE' branch we are changing the flag value because the jump condition has been met and the next iteration of the loop should not be executed.
+
+It is worth noting that if goto forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
+So, every while that has a nesting less than the original nesting and more than the nesting of the abstract object \emph{g} will end without performing the next iteration.
+
+For example, a program with nested while-loops may look like this:
+\begin{ffcode}
+goto
+  [g]
+    while.
+      |\m{9}|
+      |\sgm{9}|
+        Y
+        |\sgm{4}|
+\end{ffcode}
+
+After transformation it will look like:
+\begin{ffcode}
+memory > flag
+flag.write 0
+while.
+  and.
+    not. (eq. (flag 1))
+    |\m{9}|
+  |\sgm{9}|
+    Y'
+    if.
+      not. (eq. (flag 1))
+      |\sgm{4}|
+\end{ffcode}
 
@@
 Backward jump works the same as do-while construction in other languages: the first iteration of the loop is always executed, and the next only if the condition is TRUE.
-So, all statemets that met before the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop (Look at Image2).
+So, all statements that met before the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop (Look at Image2).
 
@@
 \begin{ffcode}
-[g1]
- ..._1
- [g2]
-  ..._2
-  [g3]
-   ..._3
-   if.
-    cond
-    g2.forward
-    TRUE
-   ..._4
-   [g4]
-    ..._5
-    if.
-     cond
-     g3.backward
-     TRUE
-    ..._6
-    if.
-     cond
-     g3.forward
-     TRUE
-    ..._7
-   ..._8
-   if.
-    cond
-    g2.backward
-    TRUE
-   ..._9
-  ..._10
- ..._11
-..._12
+
 \end{ffcode}
@@
 \begin{ffcode}
-[g1]
- ..._1
- [g2]
-  ..._2
-  [g3]
-   ..._3
-   if.
-    !cond
 
-    seq
-     ..._4
-     [g4]
-      ..._5
-      while.
-       cond
-
-       seq
-        ..._3
-        if.
-         !cond
-         seq
-          ..._4
-          [g4]
-           ..._5
-         TRUE
-
-      ..._6
-      if.
-       !cond
-       seq
-        ..._7
-       TRUE
-     ..._8
-     while.
-      cond
-
-      seq
-       ..._2
-       [g3]
-       ..._3
-       if.
-        !cond
-
-        seq
-         ..._4
-         [g4]
-          ..._5
-          while.
-           cond
-
-           seq
-            ..._3
-            if.
-             !cond
-             seq
-              ..._4
-              [g4]
-               ..._5
-             TRUE
-
-          ..._6
-          if.
-           !cond
-           seq
-            ..._7
-           TRUE
-         ..._8
-        TRUE
-     ..._9
-    TRUE    
-   ..._10 
- ..._11
-..._12
 \end{ffcode}

### 2022-06-03 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.0.1

@@ -1,0 +1,39 @@
+package com.parsers;
+
+import java.util.ArrayList;
+
+public class GetRidOfGOTO {
+    final String fileName;
+
+    public GetRidOfGOTO(String FileName) {
+        fileName = FileName;
+    }
+    ArrayList<StringBuffer> separate(String code, Character sep) {
+        int id = 0;
+        ArrayList <StringBuffer> ret = new ArrayList<>();
+        StringBuffer cur = new StringBuffer();
+        for (int i = 0; i < code.length(); i++) {
+            Character c = code.charAt(i);
+            if (c.equals(sep)) {
+                ret.add(cur);
+                cur = new StringBuffer();
+            }
+            else cur.append(cur);
+        }
+        return ret;
+    }
+    void GotoForward(int beg, int en) {
+
+    }
+    void GotoBackward(int beg, int en) {
+
+    }
+    public String eliminate(String code) {
+        ArrayList <StringBuffer> ar = separate(code, '\n');
+        for (StringBuffer s : ar) {
+            /*
+            
+             */
+        }
+    }
+}

### 2022-06-03 EliminationOfJumpObjects/src/main/java/com/parsers/Main.java

@@ -1,0 +1,9 @@
+package com.parsers;
+
+public class Main {
+    public static void main(String[] args) {
+        String XMIRFileName = args[0];
+        GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
+
+    }
+}

### 2022-06-03 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.0.2

@@ -1,14 +1,19 @@
 package com.parsers;
 
+import org.eolang.parser.XMIR;
+
 import java.util.ArrayList;
 
 public class GetRidOfGOTO {
     final String fileName;
+    String code;
 
     public GetRidOfGOTO(String FileName) {
         fileName = FileName;
+        XMIR xmir = new XMIR(fileName);
+        code = xmir.toEO();
     }
-    ArrayList<StringBuffer> separate(String code, Character sep) {
+    ArrayList<StringBuffer> separate(Character sep) {
         int id = 0;
         ArrayList <StringBuffer> ret = new ArrayList<>();
         StringBuffer cur = new StringBuffer();
@@ -28,12 +33,14 @@ public class GetRidOfGOTO {
     void GotoBackward(int beg, int en) {
 
     }
-    public String eliminate(String code) {
-        ArrayList <StringBuffer> ar = separate(code, '\n');
+    public String eliminate() {
+        ArrayList <StringBuffer> ar = separate('\n');
+        String ret = "";
         for (StringBuffer s : ar) {
             /*
-            
+
              */
         }
+        return ret;
     }
 }

### 2022-06-03 EliminationOfJumpObjects/src/main/java/com/parsers/Main.java

@@ -4,6 +4,7 @@ public class Main {
     public static void main(String[] args) {
         String XMIRFileName = args[0];
         GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
+        getRidOfGOTO.eliminate();
 
     }
 }

### 2022-06-04 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.1.0

@@ -1,18 +1,83 @@
 package com.parsers;
 
+import org.eolang.parser.Syntax;
 import org.eolang.parser.XMIR;
 
-import java.util.ArrayList;
+import java.util.*;
 
 public class GetRidOfGOTO {
     final String fileName;
+    int cntOfFlags;
     String code;
-
     public GetRidOfGOTO(String FileName) {
         fileName = FileName;
-        XMIR xmir = new XMIR(fileName);
-        code = xmir.toEO();
+        //XMIR xmir = new XMIR(fileName);
+        //code = xmir.toEO();
+        code = """
+                goto
+                  [g]
+                    seq
+                      stdout "kek"
+                      if.
+                        2 < 4
+                        g.forward 228
+                        1337
+                      stdout "lol"
+                """;
+        cntOfFlags = 0;
     }
+    void sendException(String msg) {
+        throw new RuntimeException(msg);
+    }
+    int getLevel(StringBuffer s) {
+        int id = 0;
+        while (id < s.length() && s.charAt(id) == ' ') id++;
+        return id / 2;
+    }
+    // Set Tab to desired level
+    void setTab(ArrayList <StringBuffer> ar, int id, int lvl) {
+        int currLvl = getLevel(ar.get(id));
+        if (currLvl < lvl) {
+            StringBuffer tmp = new StringBuffer();
+            for (int i = 0; i < lvl - currLvl; i++){
+                tmp.append("  ");
+            }
+            tmp.append(ar.get(id));
+            ar.set(id, tmp);
+        }
+        else {
+            try {
+                for (int i = 0; i < currLvl - lvl; i++){
+                    if (!ar.get(id).substring(0, 2).equals("  ")) sendException("Error in Tabulation!");
+                    StringBuffer tmp = new StringBuffer(ar.get(id).delete(0, 2));
+                    ar.set(id, tmp);
+                }
+            }
+            catch (RuntimeException e) {
+                System.out.println(Arrays.toString(e.getStackTrace()));
+            }
+        }
+    }
+    // Returns the end of the scope of an object
+    int findObjectEnding(ArrayList <StringBuffer> ar, int beg) {
+        int initLevel = getLevel(ar.get(beg));
+        int pos = beg + 1;
+        while (pos < ar.size() && getLevel(ar.get(pos)) > initLevel) pos++;
+        return pos;
+    }
+    StringBuffer invertingCond(StringBuffer cond) {
+        int begStat = -1, enStat = -1;
[…]

### 2022-06-04 EliminationOfJumpObjects/src/main/java/com/parsers/Main.java

@@ -2,9 +2,10 @@ package com.parsers;
 
 public class Main {
     public static void main(String[] args) {
-        String XMIRFileName = args[0];
+        String XMIRFileName = "asfsaafsfs";//args[0];
         GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
-        getRidOfGOTO.eliminate();
+        String ret = getRidOfGOTO.eliminate();
 
+        System.out.println(ret);
     }
 }

### 2022-06-04 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.1.1

@@ -18,10 +18,7 @@ public class GetRidOfGOTO {
                   [g]
                     seq
                       stdout "kek"
-                      if.
-                        2 < 4
-                        g.forward 228
-                        1337
+                      g.forward TRUE
                       stdout "lol"
                 """;
         cntOfFlags = 0;
@@ -109,7 +106,7 @@ public class GetRidOfGOTO {
         beg += 2;
         jump += 2;
 
-        int initLevel = getLevel(ar.get(beg));
+        int initLevel = getLevel(ar.get(jump));
         StringBuffer retValueOfJump = new StringBuffer(ar.get(jump).substring(ar.get(jump).indexOf(".forward") + 9));
         int en = findObjectEnding(ar, beg);
 
@@ -154,10 +151,55 @@ public class GetRidOfGOTO {
             pos = currEn + 3;
         }
 
-        return en;
-    }
-    void GotoBackward(int beg, int jump) {
+        // Deleting declaration of goto-object
+        for (int i = beg; i < en; i++) {
+            setTab(ar, i, getLevel(ar.get(i)) - 2);
+        }
+        ar.remove(beg - 1);
+        ar.remove(beg - 2);
 
+        return en - 2;
+    }
+
+
+    int GotoBackward(int beg, int jump, ArrayList <StringBuffer> ar) {
+        // Adding flag
+        StringBuffer currFlag = new StringBuffer("flag" + String.valueOf(cntOfFlags));
+        ar.add(0, new StringBuffer("memory > " + currFlag));
+        ar.add(1, new StringBuffer(currFlag + ".write 0"));
+        cntOfFlags++;
+        beg += 2;
+        jump += 2;
+
+        int initLevel = getLevel(ar.get(jump));
+        int en = findObjectEnding(ar, beg);
+
+        // Adding if-statement if Simple backward
+        if (ar.get(jump - 2).indexOf("if.") == -1) {
+            ar.add(jump, new StringBuffer("if."));
+            ar.add(jump + 1, new StringBuffer("TRUE"));
+            ar.add(jump + 3, new StringBuffer("TRUE"));
+            setTab(ar, jump, initLevel);
+            setTab(ar, jump + 1, initLevel + 1);
+            setTab(ar, jump + 2, initLevel + 1);
+            setTab(ar, jump + 3, initLevel + 1);
+            jump += 2;
+            en += 3;
+        }
+
[…]

### 2022-06-05 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.1.3

@@ -9,6 +9,7 @@ public class GetRidOfGOTO {
     final String fileName;
     int cntOfFlags;
     String code;
+
     public GetRidOfGOTO(String FileName) {
         fileName = FileName;
         //XMIR xmir = new XMIR(fileName);
@@ -16,10 +17,18 @@ public class GetRidOfGOTO {
         code = """
                 goto
                   [g]
-                    seq
-                      stdout "kek"
-                      g.forward TRUE
-                      stdout "lol"
+                    seq1
+                      o1
+                      if.
+                        st1
+                        seq2
+                          o2
+                          if.
+                            st2
+                            o3
+                            g.forward TRUE1
+                          o4
+                        g.forward FALSE
                 """;
         cntOfFlags = 0;
     }
@@ -74,6 +83,17 @@ public class GetRidOfGOTO {
         cond.insert(enStat + 2, ").not");
         return cond;
     }
+    void addIfStatement(ArrayList <StringBuffer> ar, int jump, int initLevel) {
+        if (ar.get(jump - 2).indexOf("if.") == -1) {
+            ar.add(jump, new StringBuffer("if."));
+            ar.add(jump + 1, new StringBuffer("TRUE"));
+            ar.add(jump + 3, new StringBuffer("TRUE"));
+            setTab(ar, jump, initLevel);
+            setTab(ar, jump + 1, initLevel + 1);
+            setTab(ar, jump + 2, initLevel + 1);
+            setTab(ar, jump + 3, initLevel + 1);
+        }
+    }
     //Splits code into an array of strings by separator
     ArrayList<StringBuffer> separate(Character sep) {
         int id = 0;
@@ -110,19 +130,6 @@ public class GetRidOfGOTO {
         StringBuffer retValueOfJump = new StringBuffer(ar.get(jump).substring(ar.get(jump).indexOf(".forward") + 9));
         int en = findObjectEnding(ar, beg);
 
-        // Adding if-statement if Simple forward
-        if (ar.get(jump - 2).indexOf("if.") == -1) {
-            ar.add(jump, new StringBuffer("if."));
-            ar.add(jump + 1, new StringBuffer("TRUE"));
-            ar.add(jump + 3, new StringBuffer("TRUE"));
-            setTab(ar, jump, initLevel);
-            setTab(ar, jump + 1, initLevel + 1);
[…]

### 2022-06-05 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.1.4

@@ -14,21 +14,51 @@ public class GetRidOfGOTO {
         fileName = FileName;
         //XMIR xmir = new XMIR(fileName);
         //code = xmir.toEO();
+        String tt = """
+                goto
+                  [g]
+                    o0
+                      o1
+                        o2
+                        if.
+                          st1
+                          g.backward
+                          TRUE
+                        o3
+                      o4
+                      
+                o0
+                  o1
+                    o2
+                    while.
+                      st1
+                      o0
+                        o1
+                          o2
+                          if.
+                            st1.not
+                            TRUE
+                            flag.write 1
+                          if.
+                            (eq. (flag 1)).not
+                            o3
+                            TRUE
+                        if.
+                          (eq. (flag 1)).not
+                          o4
+                          TRUE
+                          
+                    o3
+                  o4
+                
+                """;
         code = """
                 goto
                   [g]
-                    seq1
-                      o1
-                      if.
-                        st1
-                        seq2
-                          o2
-                          if.
-                            st2
-                            o3
-                            g.forward TRUE1
-                          o4
-                        g.forward FALSE
+                    if.
+                      st1
+                      g.backward
+                      TRUE
                 """;
         cntOfFlags = 0;
     }
@@ -130,6 +160,24 @@ public class GetRidOfGOTO {
         StringBuffer retValueOfJump = new StringBuffer(ar.get(jump).substring(ar.get(jump).indexOf(".forward") + 9));
         int en = findObjectEnding(ar, beg);
 
+        // Finding all while-loops
+        for (int i = beg; i < jump; ) {
+            if (ar.get(i).indexOf("while.") != -1) {
+                int curEn = findObjectEnding(ar, i + 1);
+                for (int j = i + 1; j < curEn; j++) {
+                    setTab(ar, j, getLevel(ar.get(j)) + 1);
+                }
+                ar.add(i + 1, new StringBuffer("and."));
+                setTab(ar, i + 1, getLevel(ar.get(i + 2)) - 1);
[…]

### 2022-06-06 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.4.0

@@ -10,11 +10,55 @@ public class GetRidOfGOTO {
     int cntOfFlags;
     String code;
 
+    StringBuffer currFlag;
+
     public GetRidOfGOTO(String FileName) {
         fileName = FileName;
         //XMIR xmir = new XMIR(fileName);
         //code = xmir.toEO();
         String tt = """
+goto
+  [g]
+    o0
+      o1
+        o2
+        if.
+          st1
+          g.backward
+          TRUE
+        o3
+      o4
+      
+o0
+  o1
+    o2
+    if.
+      st1.not
+      TRUE
+      while.
+        st1
+        seq
+          o0
+            o1
+              o2
+              if.
+                st1.not
+                TRUE
+                flag.write 1
+              if.
+                (eq. (flag 1)).not
+                o3
+                TRUE
+            if.
+              (eq. (flag 1)).not
+              o4
+              TRUE
+          flag.write 0
+    o3
+  o4
+                
+                """;
+        code = """
                 goto
                   [g]
                     o0
@@ -26,39 +70,6 @@ public class GetRidOfGOTO {
                           TRUE
                         o3
                       o4
-                      
-                o0
-                  o1
-                    o2
-                    while.
-                      st1
-                      o0
-                        o1
-                          o2
-                          if.
-                            st1.not
-                            TRUE
-                            flag.write 1
-                          if.
-                            (eq. (flag 1)).not
-                            o3
-                            TRUE
-                        if.
-                          (eq. (flag 1)).not
-                          o4
-                          TRUE
-                          
-                    o3
-                  o4
-                
-                """;
-        code = """
-                goto
-                  [g]
-                    if.
-                      st1
-                      g.backward
-                      TRUE
                 """;
         cntOfFlags = 0;
     }
@@ -113,6 +124,35 @@ public class GetRidOfGOTO {
         cond.insert(enStat + 2, ").not");
[…]

### 2022-06-06 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
0.4.0

@@ -69,7 +69,7 @@ o0
                           g.backward
                           TRUE
                         o3
-                      o4
+                      g.backward
                 """;
         cntOfFlags = 0;
     }
@@ -260,7 +260,7 @@ o0
         int remIdOfJump = -1;
         for (int i = beg; i < en; i++) {
             tmp.add(ar.get(i));
-            if (ar.get(i).indexOf(".backward") != -1)
+            if (ar.get(i).indexOf(".backward") != -1 && remIdOfJump == -1)
                 remIdOfJump = tmp.size() - 1;
         }
 
@@ -299,6 +299,11 @@ o0
 
         // Deleting declaration of goto-object
         int ret = rmvDclr(ar, beg, en);
+
+        for (StringBuffer now : ar){
+            System.out.println(now);
+        }
+        System.out.println("----------------------");
 
         return ret;
     }
@@ -351,7 +356,9 @@ o0
                     if (pos > posNext) sendException("Initialisation of Jump is wrong!");
                     String nameOfObject = ar.get(i).substring(pos, posNext + 1);
                     if (!mp.containsKey(nameOfObject)) sendException("Initialisation of Jump is wrong!");
-                    i = GotoForward(mp.get(nameOfObject), i, ar);
+                    int ret = GotoForward(mp.get(nameOfObject), i, ar);
+                    //mp.put(nameOfObject, ret);
+                    i = ret;
                 }
                 catch (RuntimeException e) {
                     System.out.println(Arrays.toString(e.getStackTrace()));
@@ -368,13 +375,15 @@ o0
                     if (pos > posNext) sendException("Initialisation of Jump is wrong!");
                     String nameOfObject = ar.get(i).substring(pos, posNext + 1);
                     if (!mp.containsKey(nameOfObject)) sendException("Initialisation of Jump is wrong!");
-                    i = GotoBackward(mp.get(nameOfObject), i, ar);
+                    int ret = GotoBackward(mp.get(nameOfObject), i, ar);
+                    //mp.put(nameOfObject, ret);
+                    i = ret;
                 }
                 catch (RuntimeException e) {
                     System.out.println(Arrays.toString(e.getStackTrace()));
                 }
             }
-            i++;
+            else i++;
         }
 
         return toString(ar);

### 2022-06-06 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
1.0.0
Works both transformations except multiple jumps inside one goto-object

@@ -9,55 +9,12 @@ public class GetRidOfGOTO {
     final String fileName;
     int cntOfFlags;
     String code;
-
     StringBuffer currFlag;
 
     public GetRidOfGOTO(String FileName) {
         fileName = FileName;
         //XMIR xmir = new XMIR(fileName);
         //code = xmir.toEO();
-        String tt = """
-goto
-  [g]
-    o0
-      o1
-        o2
-        if.
-          st1
-          g.backward
-          TRUE
-        o3
-      o4
-      
-o0
-  o1
-    o2
-    if.
-      st1.not
-      TRUE
-      while.
-        st1
-        seq
-          o0
-            o1
-              o2
-              if.
-                st1.not
-                TRUE
-                flag.write 1
-              if.
-                (eq. (flag 1)).not
-                o3
-                TRUE
-            if.
-              (eq. (flag 1)).not
-              o4
-              TRUE
-          flag.write 0
-    o3
-  o4
-                
-                """;
         code = """
                 goto
                   [g]
@@ -69,7 +26,6 @@ o0
                           g.backward
                           TRUE
                         o3
-                      g.backward
                 """;
         cntOfFlags = 0;
     }
@@ -153,6 +109,12 @@ o0
         }
         else return beg;
     }
+    int getHigherObj(ArrayList <StringBuffer> ar, int id, int beg) {
+        int lvl = getLevel(ar.get(id));
+        int pos = id - 1;
+        while (pos >= beg && getLevel(ar.get(pos)) >= lvl) pos--;
+        return pos;
+    }
     void addIfStatement(ArrayList <StringBuffer> ar, int jump, int initLevel) {
         if (ar.get(jump - 2).indexOf("if.") == -1) {
             ar.add(jump, new StringBuffer("if."));
@@ -222,13 +184,14 @@ o0
         ar.set(jump - 1, invertingCond(ar.get(jump - 1)));
 
         // REWRITE !!!!!!!!
-        Collections.swap(ar, jump, jump + 1);
-        ar.set(jump + 1, new StringBuffer("seq"));
-        ar.add(jump + 2, retValueOfJump);
-        ar.add(jump + 3, new StringBuffer(currFlag + ".write 1"));
-        setTab(ar, jump + 1, getLevel(ar.get(jump)));
-        setTab(ar, jump + 2, getLevel(ar.get(jump)) + 1);
-        setTab(ar, jump + 3, getLevel(ar.get(jump)) + 1);
[…]

### 2022-06-06 EliminationOfJumpObjects/src/main/java/com/parsers/Main.java

@@ -1,11 +1,26 @@
 package com.parsers;
 
+import java.io.FileNotFoundException;
+import java.io.FileReader;
+import java.io.IOException;
+
 public class Main {
     public static void main(String[] args) {
+        /*try (FileReader fileReader = new FileReader(args[0])) {
+            StringBuffer txt = new StringBuffer();
+            int c;
+            while ((c = fileReader.read()) != -1) txt.append((char)c);
+            String XMIRFileName = String.valueOf(txt);
+            GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
+            String ret = getRidOfGOTO.eliminate();
+            System.out.println(ret);
+
+        } catch (IOException e) {
+            throw new RuntimeException(e);
+        }*/
         String XMIRFileName = "asfsaafsfs";//args[0];
         GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
         String ret = getRidOfGOTO.eliminate();
-
         System.out.println(ret);
     }
 }

### 2022-06-06 paper/skeleton.tex

--- 2022-05-27 paper/ske.tex
@@
 
-\title{\textbf{Elimination Of Jump Objects}}
-\author{\textbf{author}}
-\date{May 2022}
+\title{Elimination Of Jump Objects}
+\author{author}
 
@@
 
-%%We also assume that all jumps are conditional. If this is not the case, then we can easily convert an unconditional goto to a conditional goto by adding an additional condition: \emph{if (TRUE)}.
-
 \subsection{Forward jump}
@@
   [g]
-    |\sgm{1}|
+    |\sgm{1}| |$\label{ln:ret0}$|
       |\sgm{2}|
@@
         |\dlt{2}|
-      |\sgm{3}|
+      |\sgm{3}| |$\label{ln:ret1}$|
 \end{ffcode}
 
-Let's denote lines 20-26 as X.
+Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as X.
 
@@
 in the new if-statement, the 'ELSE' branch will be executed.
-We need this so that when a series of nested objects are nested one in another, when the jump condition is met, subsequent objects whose nesting is less than the nesting of the original object containing goto forward and more than the abstract object \emph{g} and following after the original object are not executed.
+We need this so that when a series of nested objects are nested one in another, when the jump condition is met, subsequent objects whose nesting is less than the nesting of the original object containing goto forward and more than the nesting of an abstract object \emph{g} and following after the original object are not executed.
 
@@
 flag.write 0
-|\sgm{1}|
+|\sgm{1}||$\label{ln:ret2}$|
   |\sgm{2}|
   if.
-      not. (|\m{1}|)
-      seq
+    |\m{1}|.not
     |\dlt{2}|
-        |\sgm{3}|
     seq
@@
       flag.write 1
+  if.
+    (eq. (flag 1)).not
+    |\sgm{3}|
+    TRUE|$\label{ln:ret3}$|
 \end{ffcode}
 
-Let's denote lines 27-34 as X'.
+Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as X'.
+
+Now let's look at an example program with nested objects containing goto forward:
+\begin{ffcode}
+goto
+  [g]
+    |\sgm{0}|
+      X
+      |\sgm{4}|
+\end{ffcode}
+
+Applying the transformation, we get:
+\begin{ffcode}
+memory > flag
+flag.write 0
+|\sgm{0}|
+  X'
+  if.
+    (eq. (flag 1)).not
+    |\sgm{4}|
+    TRUE
+\end{ffcode}
 
@@
   [g]
-    |\sgm{0}|
+    |\sgm{0}||$\label{ln:ret4}$|
       while.
@@
             |\dlt{2}|
-          |\sgm{3}|
+          |\sgm{3}||$\label{ln:ret5}$|
 \end{ffcode}
 
-Let's denote lines 37-46 as Y.
+Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as Y.
 
@@
 flag.write 0
+|\sgm{0}||$\label{ln:ret6}$|
   while.
     and.
-    not. (eq. (flag 1))
+      (eq. (flag 1)).not
       |\m{0}|
@@
       if.
-      not. (|\m{1}|)
-      seq
+        |\m{1}|.not
         |\dlt{2}|
-        |\sgm{3}|
         seq
@@
           flag.write 1
+      if.
+        (eq. (flag 1)).not
+        |\sgm{3}|
+        TRUE|$\label{ln:ret7}$|
 \end{ffcode}
 
-Let's denote lines 49-62 as Y'.
+Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as Y'.
 
@@
   and.
-    not. (eq. (flag 1))
+    (eq. (flag 1)).not
     |\m{9}|
@@
     if.
-      not. (eq. (flag 1))
+      (eq. (flag 1)).not
       |\sgm{4}|
+      TRUE
 \end{ffcode}
 
-\subsection{backward jump}
-Backward jump in EO is implemented as:
+\subsection{Backward jump}
+Goto backward in EO is implemented as:
 
@@
   [g]
-  seq
+    |\sgm{1}|
       stdout "Will be printed forever"
@@
 
-Backward jump works the same as do-while construction in other languages: the first iteration of the loop is always executed, and the next only if the condition is TRUE.
-So, all statements that met before the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop (Look at Image2).
+Same as with goto forward, there is the goto atom-object, the abstract object \emph{g}, and the g.backward attribute.
+Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
+
+\subsubsection{Simple Backward} The simplest example of using goto-backward:
+
+\begin{ffcode}
+goto
+  [g]
+    g.backward
+\end{ffcode}
+
+This is identical to that discussed in Section 3.1.1.
+In cases where the jump is performed without condition, you need to add an additional if-statement, similar to the example in Section 3.1.1 but with goto-backward:
+
+\begin{ffcode}
+goto
+  [g]
+    if.
+      TRUE
+      g.backward
+      TRUE
+\end{ffcode}
+
+\subsubsection{Goto backward wrapped in an object}
+After the conversion decribed in Section 3.2.1, in general cases, backward jumps will look like this:
+
+\begin{ffcode}
+goto
+  [g]
+    |\sgm{1}||$\label{ln:ret8}$|
+      |\sgm{2}|
+      if.
+        |\m{1}|
+        g.backward
+        |\dlt{1}|
+      |\sgm{3}||$\label{ln:ret9}$|
+\end{ffcode}
+
+Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as W.
+
+Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition is TRUE.
+So, all objects that occurs between the "jump" itself and the declaration of an abstract object \emph{g} should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop (Look at Image2).
+
+As soon as the execution of the program reaches the jump condition, the first iteration of the new do-while loop will already be executed.
+After that, if the jump conditions are met, all objects that are between the declaration of the abstract object \emph{g} and the jump itself will be executed again.
+And that means that we can create a while loop at the point of the jump, so that every time we check the condition, we don't make a jump, but just start a new iteration of the loop.
+
+Inside the body of the new while loop, we copy all objects that are inside the abstract object g - with nesting at least the object g itself, except for the call of the jump itself with its condition.
+At the point of the jump, we should create an if-statement with an inverted jump condition: in the 'THEN' branch there will be objects that were returned in the 'ELSE' branch of the original if for the jump; in the 'THEN' branch, the value of the flag object will be changed, which will mean that the condition for the jump is met, and all subsequent objects with nesting at least the nesting of the added while loop will not be executed.
+To do this, for all these objects, going down the nesting from the object where the jump was made to the while loop, we need to add an if-statement that will check whether the condition for the jump has been met before.
+
+This transformation does not violate the program logic, because if the jump condition is fulfilled, then all the objects going after the jump itself will not be executed due to the added if-statements.
 
@@
 
-Consider the following code:
+So, after transformation, the program will look like this:
 \begin{ffcode}
-[] > f
- memory > i
- seq > @
-  i.write 1
+memory > flag
+flag.write 0
+|\sgm{1}||$\label{ln:ret10}$|
+  |\sgm{2}|
+  if.
+    |\m{1}|.not
+    |\dlt{1}|
+    while.
+      |\m{1}|
+      seq
+        |\sgm{1}|
+          |\sgm{2}|
+          if.
+            |\m{1}|.not
+            |\dlt{1}|
+            flag.write 1
+          if.
+            (eq. (flag 1)).not
+            |\sgm{3}|
+            TRUE
+        flag.write 0
+  |\sgm{3}||$\label{ln:ret11}$|
+
+\end{ffcode}
+
+Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as W'.
+
+Let's look at an example of a chain of nested objects containing a goto backward:
+
+\begin{ffcode}
 goto
   [g]
-    seq > @
-     i.write (i.add 1)
-     if.
-      i.less 10
-      g.backward
-      TRUE
- stdout "Finished!"
+    |\sgm{0}|
+      W
+      |\sgm{4}|
 \end{ffcode}
 
-Transformation is to replace a piece of code with a while loop with a backward jump condition.
-
-Equivalent replacement of the example described above:
+Applying transformation, we get:
 \begin{ffcode}
-[] > f
- memory > i
- seq > @
-  i.write 1
-  i.write (i.add 1)
-  while.
-   i.less 10
-   seq
-    i.write (i.add 1)
- stdout "Finished!"
-\end{ffcode}
-
-In cases where backward jump is used to implement continue, the transformation will look slightly different.
-
-\subsubsection{continue}
-Backward jump is used to implement continue statement:
-
-\begin{ffcode}
-[]
- memory > i
- goto > @
-  [g]
-   seq > @
-    while.
-     i.less 10
-     seq
-      i.write (i.add 1)
+memory > flag
+flag.write 0
+|\sgm{0}|
+  W'
   if.
-       eq. (i.mod 5 0)
-       g.backward
-       TRUE
-      stdout "Not divisible by 5!\n"
-\end{ffcode}
-
-This statement is logically the same as a break statement, except that after a break is executed the entire while loop stops.
-When you execute the continue statement, the next iteration of the loop is simply started.
-So from a logical standpoint, replacing continue statement is identical to replacing break statement described in section 3.1.2, except that now we don't have to create an auxiliary variable to abort the execution of the while loop.
-In this case, the transformation consists in inverting the jump condition and executing the remaining statements in the body of the new if statement.
-
-Modification of the given example code will look like:
-\begin{ffcode}
-[]
- memory > i
- seq > @
- while.
-  i.less 10
-  seq
-   i.write (i.add 1)
-   if.
-    not. (eq. (i.mod 5 0))
-    stdout "Not divisible by 5!\n"
+    (eq. (flag 1)).not
+    |\sgm{4}|
     TRUE
@@
 
-\subsection{Complex cases}
-In complex cases, when one goto object is nested in another, the transformations will be similar to cases, described in sections 3.1 - 3.2.
-When Backward jump, we should insert a while loop into the body all the statements that stand between the declaration of the object and the jump itself, as described at Section 3.2 .
-When Forward jump, remember all statements that follow in the body of if-statement where the jump is made and execute these statements after the GOTO object, as decribed at Section 3.1 .
+\subsubsection{Goto backward inside the while-loop}
+Goto backward, like goto forward, can be called inside a while-loop body.
+As discussed in section 3.1.3, the behavior of while is different from other objects in the language. Therefore, the transformation will be slightly different from that described in section 3.2.2.
 
-Consider the following complex example with nested goto-objects:
+In general cases, a goto backward call inside a while loop will look like this:
+
 \begin{ffcode}
+goto
+  [g]
+    |\sgm{0}||$\label{ln:ret12}$|
+      while.
+        |\m{0}|
+        |\sgm{1}|
+          |\sgm{2}|
+          if.
+            |\m{1}|
+            g.backward
+            |\dlt{1}|
+          |\sgm{3}||$\label{ln:ret13}$|
 
@@
 
-Considering all the jumps that appear in the code (the jumps themselves, not the declaration of goto objects), we apply the transformations already discussed and proved by us above one by one.
+Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as Z.
 
-Applying all the transformations to each encountered goto object, we get the following code:
+As described in section 3.2.2, the program runs from top to bottom until it meets goto forward and if the jump condition is met, the abstract object g is executed again.
+Similar to what was said in section 3.2.2, all objects inside the abstract object g should be copied at the jump point.
+
+The only difference, when the jump itself frames a while loop, is that when the jump condition is met, we need to interrupt the execution of all the internal while loops inside the new while loop, which we replaced the jump with.
+
+In order to interrupt the execution of each of the internal while loops, we can add an additional condition to each of them, whether the jump condition is met or not.
+This can be done with an additional flag object that will signal for each inner while loop whether the jump condition has been met.
+
+So, all internal while loops will not be executed further if flag shows that the jump condition is met and the logic of the program is not violated.
+For all other objects inside our new while loop, we should apply the transformation described in section 3.2.2.
+
+The transformation will look like this:
+
 \begin{ffcode}
+memory > flag
+flag.write 0
+|\sgm{0}||$\label{ln:ret14}$|
+  while.
+    |\m{0}|
+    |\sgm{1}|
+      |\sgm{2}|
+      while.
+        |\m{1}|
+        |\sgm{0}|
+          while.
+            and.
+              (eq. (flag 1)).not
+              |\m{0}|
+            |\sgm{1}|
+              |\sgm{2}|
+              if.
+                |\m{1}|.not
+                |\dlt{1}|
+                flag.write 1
+              if.
+                (eq. (flag 1)).not
+                |\sgm{3}|
+                TRUE
+      |\sgm{3}||$\label{ln:ret15}$|
 
@@
 
+Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as Z'.
+
+Let's take a look on a program with nested while-loops:
+\begin{ffcode}
+goto
+  [g]
+    while.
+      |\m{9}|
+      |\sgm{9}|
+        Z
+        |\sgm{4}|
+\end{ffcode}
+
+After transformation it will look like:
+\begin{ffcode}
+memory > flag
+flag.write 0
+while.
+  |\m{9}|
+  |\sgm{9}|
+    Z'
+    if.
+      (eq. (flag 1)).not
+      |\sgm{4}|
+      TRUE
+\end{ffcode}
+
 \subsection{Final algorithm}
-Summarizing the points above, we can fully describe the algorithm itself.
-It consists of three steps (See Image3).
-The first step is to convert all unconditional goto objects to conditional goto objects.
-In the second step, applying the transformations described above, we replace jumps with semantically equivalent pieces of code.
-In the third step, remove all the declarations of the GOTO objects themselves.
+To sum up, we can now fully describe the algorithm itself.
+The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
+The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if you need to make a replacement in the while loop, containing a jump - we use transformations 3.1.3 and 3.2.3 accordingly.
+If you want to make a replacement for a normal object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
 

### 2022-06-07 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
1.0.1
Need to change Inverting condition-function

@@ -1,8 +1,5 @@
 package com.parsers;
 
-import org.eolang.parser.Syntax;
-import org.eolang.parser.XMIR;
-
 import java.util.*;
 
 public class GetRidOfGOTO {
@@ -10,22 +7,32 @@ public class GetRidOfGOTO {
     int cntOfFlags;
     String code;
     StringBuffer currFlag;
+    HashMap <String, Boolean> delDclr = new HashMap<String, Boolean>();
+    HashMap <String, Boolean> initBack = new HashMap<String, Boolean>();
+    HashMap <String, StringBuffer> flagForBack = new HashMap<String, StringBuffer>();
 
     public GetRidOfGOTO(String FileName) {
         fileName = FileName;
         //XMIR xmir = new XMIR(fileName);
         //code = xmir.toEO();
         code = """
-                goto
-                  [g]
-                    o0
-                      o1
-                        o2
-                        if.
-                          st1
-                          g.backward
-                          TRUE
-                        o3
+goto
+  [g]
+    o0
+      o1
+        goto
+          [g1]
+            o9
+              o2
+              if.
+                st1
+                g.backward
+                TRUE
+              o3
+                o4
+                g1.forward val
+                o5
+              o6
                 """;
         cntOfFlags = 0;
     }
@@ -61,7 +68,10 @@ public class GetRidOfGOTO {
             }
         }
     }
-    // Returns the end of the scope of an object
+
+    /*
+     * Returns the end of the scope of an object
+     */
     int findObjectEnding(ArrayList <StringBuffer> ar, int beg) {
         int initLevel = getLevel(ar.get(beg));
         int pos = beg + 1;
@@ -80,12 +90,12 @@ public class GetRidOfGOTO {
         cond.insert(enStat + 2, ").not");
         return cond;
     }
-    int procOtherObjects(ArrayList <StringBuffer> ar, int pos, int en) {
+    void procOtherObjects(ArrayList <StringBuffer> ar, int pos, int en, int valOfFlag) {
         while (pos < en) {
             int currEn = findObjectEnding(ar, pos);
             int currLevel = getLevel(ar.get(pos));
             ar.add(pos, new StringBuffer("if."));
-            ar.add(pos + 1, new StringBuffer("(eq. (" + currFlag + " 1)).not"));
[…]

### 2022-06-07 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
1.0.2
Just added Comments

@@ -3,6 +3,15 @@ package com.parsers;
 import java.util.*;
 
 public class GetRidOfGOTO {
+    /*
+     * fileName -
+     * cntOfFlags - to count number of flags
+     * code -
+     * currFlag - Current flag for adding
+     * delDclr - Checks if declaration of goto-object is deleted
+     * initBack - Checks if main while-loop for GotoBackward is added
+     * flagForBack - Gives a flag of goto-object with backward Jump
+     */
     final String fileName;
     int cntOfFlags;
     String code;
@@ -20,31 +29,32 @@ goto
   [g]
     o0
       o1
-        goto
-          [g1]
-            o9
-              o2
-              if.
-                st1
-                g.backward
-                TRUE
-              o3
-                o4
-                g1.forward val
-                o5
-              o6
+        o2
+        if.
+          st1
+          g.backward
+          TRUE
+        o3
+      g.backward
                 """;
         cntOfFlags = 0;
     }
     void sendException(String msg) {
         throw new RuntimeException(msg);
     }
+
+    /*
+     * Returns nesting of an Object
+     */
     int getLevel(StringBuffer s) {
         int id = 0;
         while (id < s.length() && s.charAt(id) == ' ') id++;
         return id / 2;
     }
-    // Set Tab to desired level
+
+    /*
+     * Sets Tab to desired level
+     */
     void setTab(ArrayList <StringBuffer> ar, int id, int lvl) {
         int currLvl = getLevel(ar.get(id));
         if (currLvl < lvl) {
@@ -78,18 +88,23 @@ goto
         while (pos < ar.size() && getLevel(ar.get(pos)) > initLevel) pos++;
         return pos;
     }
-    StringBuffer invertingCond(StringBuffer cond) {
-        int begStat = -1, enStat = -1;
-        for (int i = 0; i < cond.length(); i++) {
-            if (cond.charAt(i) != ' ') {
-                if (begStat == -1) begStat = i;
-                enStat = i;
-            }
+
+    /*
+     * Inverting Condition to opposite
+     */
+    void invertingCond(ArrayList <StringBuffer> ar, int line) {
+        int begStmt = getHigherObj(ar, line) + 1;
+        ar.add(begStmt, new StringBuffer("not."));
+        setTab(ar, begStmt, getLevel(ar.get(begStmt + 1)));
[…]

### 2022-06-09 EliminationOfJumpObjects/src/main/java/com/parsers/GetRidOfGOTO.java
1.0.3
If parsing Xmir, gets Logger's Warning

@@ -1,30 +1,33 @@
 package com.parsers;
 
+import org.eolang.parser.Syntax;
+import org.eolang.parser.XMIR;
+
 import java.util.*;
 
 public class GetRidOfGOTO {
     /*
      * fileName -
      * cntOfFlags - to count number of flags
-     * code -
+     * inputCode -
      * currFlag - Current flag for adding
      * delDclr - Checks if declaration of goto-object is deleted
      * initBack - Checks if main while-loop for GotoBackward is added
      * flagForBack - Gives a flag of goto-object with backward Jump
      */
-    final String fileName;
+    //final String fileName;
     int cntOfFlags;
-    String code;
+    String inputCode;
     StringBuffer currFlag;
     HashMap <String, Boolean> delDclr = new HashMap<String, Boolean>();
     HashMap <String, Boolean> initBack = new HashMap<String, Boolean>();
     HashMap <String, StringBuffer> flagForBack = new HashMap<String, StringBuffer>();
 
-    public GetRidOfGOTO(String FileName) {
-        fileName = FileName;
-        //XMIR xmir = new XMIR(fileName);
-        //code = xmir.toEO();
-        code = """
+    public GetRidOfGOTO(String givenCode) {
+        XMIR xmir = new XMIR(givenCode);
+        inputCode = xmir.toEO();
+        System.out.println(inputCode);
+        /*inputCode = """
 goto
   [g]
     o0
@@ -36,7 +39,7 @@ goto
           TRUE
         o3
       g.backward
-                """;
+                """;*/
         cntOfFlags = 0;
     }
     void sendException(String msg) {
@@ -171,8 +174,8 @@ goto
         int id = 0;
         ArrayList <StringBuffer> ret = new ArrayList<>();
         StringBuffer cur = new StringBuffer();
-        for (int i = 0; i < code.length(); i++) {
-            Character c = code.charAt(i);
+        for (int i = 0; i < inputCode.length(); i++) {
+            Character c = inputCode.charAt(i);
             if (c.equals(sep)) {
                 ret.add(cur);
                 cur = new StringBuffer();
@@ -205,12 +208,10 @@ goto
          * initLevelOfJump - nesting of Beginning of goto-object
          * retValueOfJump - object that will return if Jump statement is TRUE
          * endOfObj - last line in goto-object (exclusive)
-         * cond - condition of Jump
          */
         int initLevelOfJump = getLevel(ar.get(jump));
[…]

### 2022-06-09 EliminationOfJumpObjects/src/main/java/com/parsers/Main.java

@@ -2,25 +2,38 @@ package com.parsers;
 
 import java.io.FileNotFoundException;
 import java.io.FileReader;
+import java.io.FileWriter;
 import java.io.IOException;
 
 public class Main {
-    public static void main(String[] args) {
-        /*try (FileReader fileReader = new FileReader(args[0])) {
-            StringBuffer txt = new StringBuffer();
+    public static String readFromDirectory(String inp) {
+        try (FileReader fileReader = new FileReader(inp)) {
+            StringBuffer text = new StringBuffer();
             int c;
-            while ((c = fileReader.read()) != -1) txt.append((char)c);
-            String XMIRFileName = String.valueOf(txt);
-            GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
-            String ret = getRidOfGOTO.eliminate();
-            System.out.println(ret);
-
-        } catch (IOException e) {
+            while ((c = fileReader.read()) != -1) {
+                text.append((char)c);
+            }
+            String code = String.valueOf(text);
+            return code;
+        }
+        catch (IOException e) {
             throw new RuntimeException(e);
-        }*/
-        String XMIRFileName = "asfsaafsfs";//args[0];
-        GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(XMIRFileName);
+        }
+    }
+    public static void writeToDirectory(String out) {
+        try (FileWriter fileWriter = new FileWriter("", false)) {
+            fileWriter.write(out);
+            fileWriter.flush();
+        }
+        catch (IOException e) {
+            throw new RuntimeException(e);
+        }
+    }
+    public static void main(String[] args) throws FileNotFoundException {
+        String code = readFromDirectory(args[0]);
+        GetRidOfGOTO getRidOfGOTO = new GetRidOfGOTO(code);
         String ret = getRidOfGOTO.eliminate();
         System.out.println(ret);
+        //writeToDirectory(ret);
     }
 }

### 2022-06-18 paper/skeleton.tex
Update skeleton.tex

@@
 \usepackage{ffcode}
+\usepackage{amsmath}
+
+\newtheorem{definition}{Definition}[section]
 
 \graphicspath{ {./images/} }
-
-% Keywords command
-\providecommand{\keywords}[1]
-{
-  \small
-  \textbf{\textit{Keywords:}} #1
-}
-
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
 
@@
 
-Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called atoms. 
+Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called \emph{atoms}. 
 So all jump statements are implemented as a
-single atom-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
+single \emph{atom}-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
 
@@
 
-\emph{Definition:} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
+\begin{definition} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
+\end{definition}
 
@@
 
+\vspace{5mm}
+
 \emph{Designations:}
 
-$\sigma$ - Means that there can be an arbitrary number of objects, a chain of nested objects or there can be no objects at all.
+\begin{itemize}
+\item $\sigma$ - Denotes either an object, a chain of nested objects or the absence of an object.
 
-$\delta$ - Means that there should necessarily be an object that returns a non-NULL value when accessed.
+\item $\delta$ - Denotes a not-empty object or a chain of nested objects that return a not-NULL value when accessed.
 
-$\mu$ - Means that there must be an object that returns a boolean value (TRUE/FALSE) when executed.
+\item $\mu$ - Denotes an object or a chain of nested objects that return a boolean value (TRUE/FALSE) when executed.
+\end{itemize}
 
@@
 \newcommand\m[1]{$\mu_#1$}
+
+We will also look at our transformations in the form of $\varphi$-calculus, on which EO is based.
+The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application, and decoration.
+The calculus introduces a formal apparatus for manipulations with objects.
+
+$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
 
@@
   [g]
-    |\sgm{1}|
+    |\sgm{1}| > @
       g.forward |\dlt{1}|
@@
 \subsubsection{Simple Forward}
-This is the simplest example of using goto-forward:
+Consider the simplest example of using goto-forward:
 
@@
   [g]
-    g.forward |\dlt{1}|
+    g.forward |\dlt{1}| > @
 \end{ffcode}
 
-Note that in this example, g.forward is simply an attribute of the abstract object g and is executed as soon as the queue reaches it.
+In terms of $\varphi$-calculus, this code will appear as:
+
+\begin{equation}
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{forward} (\delta_1) \rrbracket ) \\
+\end{split}
+\end{equation}
+
+Note that in this example, g.forward is simply an attribute of the abstract object \emph{g} and is executed as soon as the queue reaches it.
 Our transformation only considers the jumps that are made when a condition for it is fulfilled.
@@
 
+\begin{equation}
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket) 
+\end{split}
+\end{equation}
+
+Same example on EO:
+
 \begin{ffcode}
@@
   [g]
-    if.
+    if. > @
       TRUE
@@
 \subsubsection{Goto forward wrapped in an object}
-So, after the conversion described in section 3.1.1, in general cases, forward jumps will look like this:
+
+After the conversion described in section 3.1.1, the simplest call of forward jump will be presented as:
+
+\begin{equation}
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+\end{split}
+\end{equation}
+
+The transformation under consideration involves the following steps:
+
+\begin{equation}
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
+\end{split}
+\end{equation}
+
+\begin{theorem}
+Expression 3 is semantically equivalent to expression 6:
+\end{theorem}
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+\end{split}
+\end{equation}
+
+\hline
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
+\end{split}
+\end{equation}
+
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.
+
+Consider the following code:
+
 \begin{ffcode}
@@
   [g]
-    |\sgm{1}| |$\label{ln:ret0}$|
+    |\sgm{1}| > @ |$\label{ln:ret0}$|
       |\sgm{2}|
@@
 It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
-Otherwise statements following the goto object itself are executed.
-So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic (Look at Image1).
+Otherwise statements following the goto-object itself are executed.
+So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic.
 
-Also, after replacing the jump, we must create an additional \emph{flag} object, which will change if the jump condition is met, i.e.
-in the new if-statement, the 'ELSE' branch will be executed.
-We need this so that when a series of nested objects are nested one in another, when the jump condition is met, subsequent objects whose nesting is less than the nesting of the original object containing goto forward and more than the nesting of an abstract object \emph{g} and following after the original object are not executed.
+Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e.
+when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change.
+This is required so that all objects following the if-statement that are attributes of the abstract object g are not executed.
+So, by wrapping each object following the jump condition and whose nesting is at least that of the g object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
 
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example: the \m{1} object must be inverted with not.
-(\m{1}); in 'THEN' brunch of if-statement creates an object \emph{seq} with \dlt{2} and \sgm{3} inside of it; the 'ELSE' branch an object \emph{seq} with \dlt{1} object that was previously called when the jump is made and changes the value of the \emph{flag} object to 1.
+By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example: the \m{1} object must be inverted with (\m{1}).not; in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object seq, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
 
-{INSERT AN IMAGE1}
-
-Thus, after transformation, the program will look like this:
+Thus, after transformation, the program converts to:
 \begin{ffcode}
@@
   [g]
-    |\sgm{0}|
+    |\sgm{0}| > @
       X
@@
 
-A goto-object can also be called inside such a while-loop.
-In this case, the transformation is slightly different from that described in Section 3.1.2, because the behavior of while is different from other objects in the language.
+The simplest way to call goto forward inside a while-loop is represented as:
 
-In general, using goto forward inside a while-loop will look like this:
+\begin{equation}
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
+& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+The transformation under consideration involves the following steps:
+
+%%\begin{equation}
+%%\begin{split}
+%%& \ff{memory}(flag), \\
+%%& flag.\ff{write}(0), \\
+%%& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} %%\mapsto \varnothing, \\
+%%& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
+%%& \quad \ff{if}.(\mu_1, %%\ff{g}.\ff{forward}(\delta_1), \delta_2) \\
+%%& \quad )\rrbracket) \\
+%%\end{split}
+%%\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
+& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
+& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
+& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
+& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
+& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
+& \quad \quad ) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{while}.(\ff{and}.( \\
+& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
+& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
+& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
+& \quad ) \\
+& ) \\
+\end{split}
+\end{equation}
+
+\begin{theorem}
+Expression 7 is semantically equivalent to expression 10:
+\end{theorem}
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
+& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\hline
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{while}.(\ff{and}.( \\
+& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
+& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
+& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) \\
+& \quad )\\
+& ) \\
+\end{split}
+\end{equation}
+
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.
+
+Consider the following code on EO:
+
 \begin{ffcode}
@@
   [g]
-    |\sgm{0}||$\label{ln:ret4}$|
+    |\sgm{0}| > @ |$\label{ln:ret4}$|
       while.
@@
 
-Thus, transformation will look like this:
+Thus, the transformation is:
+
 \begin{ffcode}
@@
 
-It is worth noting that if goto forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
+It is worth noting that if goto-forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
 So, every while that has a nesting less than the original nesting and more than the nesting of the abstract object \emph{g} will end without performing the next iteration.
@@
   [g]
-    while.
+    while. > @
       |\m{9}|
@@
   [g]
-    |\sgm{1}|
+    |\sgm{1}| > @
       stdout "Will be printed forever"
@@
 
-Same as with goto forward, there is the goto atom-object, the abstract object \emph{g}, and the g.backward attribute.
+Same as with goto forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
 Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
@@
   [g]
-    g.backward
+    g.backward > @
 \end{ffcode}
 
-This is identical to that discussed in Section 3.1.1.
-In cases where the jump is performed without condition, you need to add an additional if-statement, similar to the example in Section 3.1.1 but with goto-backward:
+which in terms of $\varphi$-calculus appears as:
+
+\begin{equation}
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{backward} \rrbracket ) \\
+\end{split}
+\end{equation}
+
+This is identical to that discussed in Section 3.1.1. In cases where the jump is performed without condition, you need to add an additional if-statement, similar to the example in Section 3.1.1:
+
+\begin{equation}
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \\
+\end{split}
+\end{equation}
+
+Same code on EO:
 
@@
 \subsubsection{Goto backward wrapped in an object}
-After the conversion decribed in Section 3.2.1, in general cases, backward jumps will look like this:
+After the conversion described in Section 3.2.1, the simplest call of backward jump will be presented as:
+
+\begin{equation}
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
+\end{split}
+\end{equation}
+
+The transformation under consideration involves the following steps:
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
+& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
+& \quad \quad ) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \ff{seq}(flag.\ff{write}(1), \\
+& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
+& \quad ) \\
+& ) \\
+\end{split}
+\end{equation}
+
+\begin{theorem}
+Expression 13 is semantically equivalent to expression 16:
+\end{theorem}
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
+\end{split}
+\end{equation}
+
+\hline
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \ff{seq}(flag.\ff{write}(1), \\
+& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
+& \quad ) \\
+& ) \\
+\end{split}
+\end{equation}
+
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.
+
+Consider the following code on EO:
 
@@
 Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition is TRUE.
-So, all objects that occurs between the "jump" itself and the declaration of an abstract object \emph{g} should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop (Look at Image2).
+So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.
 
-As soon as the execution of the program reaches the jump condition, the first iteration of the new do-while loop will already be executed.
-After that, if the jump conditions are met, all objects that are between the declaration of the abstract object \emph{g} and the jump itself will be executed again.
-And that means that we can create a while loop at the point of the jump, so that every time we check the condition, we don't make a jump, but just start a new iteration of the loop.
+Since there is no direct implementation of the do-while construct in EO, but there is an implementation of the while generator, we can resort to a little trick.
 
-Inside the body of the new while loop, we copy all objects that are inside the abstract object g - with nesting at least the object g itself, except for the call of the jump itself with its condition.
-At the point of the jump, we should create an if-statement with an inverted jump condition: in the 'THEN' branch there will be objects that were returned in the 'ELSE' branch of the original if for the jump; in the 'THEN' branch, the value of the flag object will be changed, which will mean that the condition for the jump is met, and all subsequent objects with nesting at least the nesting of the added while loop will not be executed.
-To do this, for all these objects, going down the nesting from the object where the jump was made to the while loop, we need to add an if-statement that will check whether the condition for the jump has been met before.
+To create a do-while emission, we can create a flag globally that will be a condition for our outer loop, whose execution condition will depend on this value.
+The initial value of this flag will be such that the condition for the execution of the added while loop is fulfilled.
+Then, in the body of the loop, we change the value of the flag to the opposite.
+When the jump condition is met, we again change the value of the flag so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop execution condition will be met.
 
-This transformation does not violate the program logic, because if the jump condition is fulfilled, then all the objects going after the jump itself will not be executed due to the added if-statements.
+In order to ensure that when the jump condition is met, all other objects in the body of the newly added while loop are not executed, we wrap them in an additional if-statement, in which we will check whether the jump condition was previously executed.
 
-{INSERT AN IMAGE2}
+So, after transformation, the program converts to:
+\begin{ffcode}
 
-So, after transformation, the program will look like this:
-\begin{ffcode}
 memory > flag
 flag.write 0
+while.
+  eq. (flag 0)
+  seq
+    flag.write 1
     |\sgm{1}||$\label{ln:ret10}$|
@@
       if.
-    |\m{1}|.not
+        (|\m{1}|).not
         |\dlt{1}|
-    while.
-      |\m{1}|
-      seq
-        |\sgm{1}|
-          |\sgm{2}|
+        flag.write 0
       if.
-            |\m{1}|.not
-            |\dlt{1}|
-            flag.write 1
-          if.
-            (eq. (flag 1)).not
+        (eq. (flag 0)).not
         |\sgm{3}|
-            TRUE
-        flag.write 0
-  |\sgm{3}||$\label{ln:ret11}$|
+        TRUE|$\label{ln:ret11}$|
 
@@
 \begin{ffcode}
+
 goto
@@
       |\sgm{4}|
+
 \end{ffcode}
@@
 \begin{ffcode}
+
 memory > flag
 flag.write 0
+while.
+  eq. (flag 0)
+  seq
+    flag.write 1
     |\sgm{0}|
@@
       if.
-    (eq. (flag 1)).not
+        (eq. (flag 0)).not
         |\sgm{4}|
         TRUE
+
 \end{ffcode}
@@
 \subsubsection{Goto backward inside the while-loop}
-Goto backward, like goto forward, can be called inside a while-loop body.
+Goto backward also can be called inside a while-loop body.
+
+The simplest way to call goto-backward inside a while-loop is represented as:
+
+\begin{equation}
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
+& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+The transformation under consideration involves the following steps:
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \quad \ff{while}.(\mu_0, \\
+& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
+& \quad \quad ) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
+& \quad \quad \quad \ff{while}.( \\
+& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
+& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
+& \quad \quad \quad ) \\
+& \quad \quad ) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\begin{equation}
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \ff{seq}(flag.\ff{write}(1), \\
+& \quad \quad \ff{while}.( \\
+& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
+& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
+& \quad \quad ) \\
+& \quad ) \\
+&  ) \\
+\end{split}
+\end{equation}
+
+\begin{theorem}
+Expression 17 is semantically equivalent to expression 20:
+\end{theorem}
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
+& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
+& \quad ) \\
+& \rrbracket) \\
+\end{split}
+\end{equation}
+
+\hline
+
+\begin{equation} \nonumber
+\begin{split}
+& \ff{memory}(flag), \\
+& flag.\ff{write}(0), \\
+& \ff{while}.(\ff{eq}.(flag 0), \\
+& \quad \ff{seq}(flag.\ff{write}(1), \\
+& \quad \quad \ff{while}.( \\
+& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
+& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
+& \quad \quad ) \\
+& \quad ) \\
+&  ) \\
+\end{split}
+\end{equation}
+
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.
+
 As discussed in section 3.1.3, the behavior of while is different from other objects in the language. Therefore, the transformation will be slightly different from that described in section 3.2.2.
 
-In general cases, a goto backward call inside a while loop will look like this:
+To understand that the logic is not broken, let's look at a special case of calling goto backward inside a while-loop.
+
+Let's consider the following code:
 
@@
   [g]
-    |\sgm{0}||$\label{ln:ret12}$|
+    |\sgm{0}| > @|$\label{ln:ret12}$|
       while.
@@
 \begin{ffcode}
+
 memory > flag
 flag.write 0
+while.
+  eq. (flag 0)
+  seq
+    flag.write 1
     |\sgm{0}||$\label{ln:ret14}$|
       while.
-    |\m{0}|
-    |\sgm{1}|
-      |\sgm{2}|
-      while.
-        |\m{1}|
-        |\sgm{0}|
-          while.
         and.
-              (eq. (flag 1)).not
+          (eq. (flag 0)).not
           |\m{0}|
@@
             |\dlt{1}|
-                flag.write 1
+            flag.write 0
           if.
-                (eq. (flag 1)).not
+            (eq. (flag 0)).not
             |\sgm{3}|
-                TRUE
-      |\sgm{3}||$\label{ln:ret15}$|
+            TRUE|$\label{ln:ret15}$|
 
@@
 \begin{ffcode}
+
 goto
   [g]
-    while.
+    while. > @
       |\m{9}|
@@
         |\sgm{4}|
+
 \end{ffcode}
@@
 \begin{ffcode}
+
 memory > flag
@@
 while.
+  eq. (flag 0)
+  seq
+    flag.write 1
+    while.
+      and.
+        (eq. (flag 0)).not
         |\m{9}|
@@
         if.
-      (eq. (flag 1)).not
+          (eq. (flag 0)).not
           |\sgm{4}|
           TRUE
+
 \end{ffcode}
@@
 The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if you need to make a replacement in the while loop, containing a jump - we use transformations 3.1.3 and 3.2.3 accordingly.
-If you want to make a replacement for a normal object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
-
-{INSERT IMAGE3}
+If you need to make a replacement for a normal object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
 
 \section{Conclusion}
-As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the ATOM object GOTO.
-They also showed that the program at the output will contain the same logic as the program at the input (TODO).
+As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the \emph{atom} object GOTO.
+We also showed that the program at the output will contain the same logic as the program at the input.
 
 \section{Discussion}
-Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, a formal proof makes it possible to remove all GOTO constructs from programs.
+Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, our proof makes it possible to remove all GOTO constructs from programs.
 

### 2022-06-21 JumpEliminationTool/src/main/java/org/eolang/jump/Main.java
0.0.0

@@ -1,0 +1,10 @@
+package org.eolang.jump;
+
+import javax.xml.transform.TransformerFactory;
+
+public class Main {
+    public static void main(String[] args) {
+        TransformerFactory transformerFactory = TransformerFactory.newDefaultInstance();
+
+    }
+}

### 2022-06-28 src/main/java/org/eolang/jump/Main.java
0.0._

@@ -1,12 +1,9 @@
 package org.eolang.jump;
 
-import com.jcabi.xml.XSLDocument;
-import com.yegor256.xsline.Xsline;
+import java.io.IOException;
 
 public class Main {
-    public static void main(String[] args) {
-
-        System.out.println("Hello world!");
-        //Xsline xsline = new Xsline(new XSLDocument());
+    public static void main(String[] args) throws IOException {
+        RemoveGOTO.exec();
     }
 }

### 2022-06-28 src/main/java/org/eolang/jump/RemoveGOTO.java

@@ -1,0 +1,20 @@
+package org.eolang.jump;
+
+import com.jcabi.xml.XML;
+import com.jcabi.xml.XMLDocument;
+import com.jcabi.xml.XSLDocument;
+import com.yegor256.xsline.StXSL;
+import com.yegor256.xsline.TrDefault;
+import com.yegor256.xsline.Xsline;
+
+import java.io.IOException;
+
+public class RemoveGOTO {
+    public static void exec() throws IOException {
+        XML input = new XMLDocument(Main.class.getResource("test.xml"));
+        XML output = new Xsline(
+                new TrDefault<>()
+                        .with(new StXSL(new XSLDocument(Main.class.getResource("add-brackets.xsl"))))
+        ).pass(input);
+    }
+}

### 2022-06-28 src/test/java/RemoveGOTOTest.java

@@ -1,0 +1,9 @@
+import org.junit.Test;
+
+public class RemoveGOTOTest {
+
+    @Test
+    public void check() {
+
+    }
+}

### 2022-06-28 src/main/java/org/eolang/jump/Main.java
0.0._

@@ -4,6 +4,7 @@ import java.io.IOException;
 
 public class Main {
     public static void main(String[] args) throws IOException {
-        RemoveGOTO.exec();
+        RemoveGOTO run = new RemoveGOTO();
+        run.exec();
     }
 }

### 2022-06-28 src/main/java/org/eolang/jump/RemoveGOTO.java

@@ -3,18 +3,16 @@ package org.eolang.jump;
 import com.jcabi.xml.XML;
 import com.jcabi.xml.XMLDocument;
 import com.jcabi.xml.XSLDocument;
-import com.yegor256.xsline.StXSL;
-import com.yegor256.xsline.TrDefault;
-import com.yegor256.xsline.Xsline;
+import com.yegor256.xsline.*;
 
 import java.io.IOException;
 
 public class RemoveGOTO {
-    public static void exec() throws IOException {
-        XML input = new XMLDocument(Main.class.getResource("test.xml"));
-        XML output = new Xsline(
-                new TrDefault<>()
-                        .with(new StXSL(new XSLDocument(Main.class.getResource("add-brackets.xsl"))))
-        ).pass(input);
+    public void exec() throws IOException {
+        final Train<Shift> train = new TrDefault<>()
+                .with(new StXSL(new XSLDocument(this.getClass().getResource("add-brackets.xsl"))));
+        
+        XML input = new XMLDocument(this.getClass().getResource("test.xml"));
+        XML output = new Xsline(train).pass(input);
     }
 }

### 2022-06-29 paper/skeleton.tex
Update skeleton.tex

@@
 \usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
-\usepackage[utf8]{inputenc}
 \usepackage{listings}
@@
 \usepackage{xcolor}
+
+\usepackage[T2A,T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage[russian,english]{babel}
+  \renewcommand\ttdefault{cmtt}
+\usepackage{csquotes}
 \usepackage{ffcode}
+\usepackage{CJKutf8}
+\usepackage{paralist}
+\usepackage{cancel} % to enable \cancel command
+\usepackage{anyfontsize} % To get rid of font not found warnings
+\usepackage{tabularx} % for special tables
 \usepackage{amsmath}
+\usepackage{to-be-determined}
+\usepackage{href-ul}
+\usepackage{amsthm}
+\usepackage{tcolorbox} % for algorithm
+  \tcbuselibrary{skins}
+\usepackage{fdsymbol} % for \mathbb
+\usepackage{algpseudocode} % for algorithms
+\usepackage{multicol} % for two cols in BNF
+\usepackage{pgffor} % to enable \foreach
+\usepackage{stmaryrd}
+\usepackage{mathtools}
+
+\newcommand\br{\\[-4pt]}
+\newcounter{rule}
+\renewcommand\therule{R\arabic{rule}}
+\newcommand\rr{\smalltriangleright{}}
+\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
+\newcommand{\jrule}[1]{%
+  \refstepcounter{rule}\label{rule:#1}%
+  \text{\textbf{\rrule{#1}}}}
 
@@
 \maketitle
-
-\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}
 
@@
 
-It consists of the goto atom-object, the abstract object \emph{g}, and the g.forward attribute.
+It consists of the goto \emph{atom}-object, the abstract object \emph{g}, and the g.forward attribute.
 Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.
@@
 \begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket) 
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing,\br
+& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket)\\
 \end{split}
@@
 \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
 & \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
@@
 \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \br
 \end{split}
@@
 \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \br
 \end{split}
@@
 \begin{split}
-& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
+& \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1) \br
 \end{split}
@@
 
-\begin{equation} \nonumber
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
-\end{split}
-\end{equation}
+\begin{equation*}
+\dfrac
+    {\begin{matrix}
+    \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
+    \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket)
+    \end{matrix}}
+    {\ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1)}
+    \jrule{1}
+\end{equation*}
 
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
-\end{split}
-\end{equation}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
 
@@
 
-Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as X.
+Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as $X$.
 
@@
 when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change.
-This is required so that all objects following the if-statement that are attributes of the abstract object g are not executed.
-So, by wrapping each object following the jump condition and whose nesting is at least that of the g object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
+This is required so that all objects following the if-statement that are attributes of the abstract object \emph{g} are not executed.
+So, by wrapping each object following the jump condition and whose nesting is at least that of the \emph{g} object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
 
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example: the \m{1} object must be inverted with (\m{1}).not; in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object seq, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
+By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
+the \m{1} object must be inverted with (\m{1}).not;
+in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object \emph{seq}, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
 
@@
 
-Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as X'.
+Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as $X'$.
 
-Now let's look at an example program with nested objects containing goto forward:
+Now let's look at an example program with nested objects containing goto-forward:
+
 \begin{ffcode}
@@
 
-The language currently provides a while generator, on which other generators are implemented.
+The language currently provides a \emph{while} generator, on which other generators are implemented.
 
-The simplest way to call goto forward inside a while-loop is represented as:
+The simplest way to call goto-forward inside a \emph{while}-loop is represented as:
 
@@
 \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
+& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) ) \rrbracket) \br
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
-& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\br
+& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
+& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) )\rrbracket)\\[-1pt]
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
-& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\br
+& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
+& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
+& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \rrbracket )\\[-1pt]
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{while}.(\ff{and}.( \\
-& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
-& \quad ) \\
-& ) \\
+& \ff{while}.(\br
+& \quad \ff{and}.(\mu_0, \ff{eq}.(flag  1).\ff{not}), \br
+& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
+& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \\[-1pt]
 \end{split}
@@
 
-\begin{equation} \nonumber
-\begin{split}
+\begin{equation*}
+\dfrac
+    {\begin{matrix}
     & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
     & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
+    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2))\rrbracket) \\
+    \end{matrix}}
+    {\begin{matrix}
     & \ff{memory}(flag), \\
@@
     & \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) \\
-& \quad )\\
-& ) \\
-\end{split}
-\end{equation}
+    & \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0))) \\
+    \end{matrix}}
+    \jrule{2}
+\end{equation*}
 
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
 
@@
 
-Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as Y.
+Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as $Y$.
 
@@
 So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
+
+If the jump condition is met, all objects inside the abstract object \emph{g} and following the goto-forward will not be executed.
+To do this, each of these objects should be wrapped in an additional if-statement, which will check the value of the flag, in other words - whether the jump condition is met or not.
+
 Otherwise, all statements that came after the jump in the while loop will be executed.
-So the combined condition of the while loop will look like: while (!flag AND condOfWhile).
+So the combined condition of the while loop will be presented as: while (!flag AND condOfWhile).
 
-Thus, the transformation is:
+Thus, the transformation will be presented as:
 
@@
 
-Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as Y'.
+Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as $Y'$.
 
@@
 
-Same as with goto forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
+Same as with goto-forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
 Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
@@
 
-This is identical to that discussed in Section 3.1.1. In cases where the jump is performed without condition, you need to add an additional if-statement, similar to the example in Section 3.1.1:
+This is identical case to that discussed in Section 3.1.1. In cases where the jump is performed without condition, we need to add an additional if-statement, similar to the example in Section 3.1.1:
 
@@
 \begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \br
 \end{split}
@@
 \begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \br
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
+& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ))\rrbracket) \\[-1pt]
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
+& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
+& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))\rrbracket) \\[-1pt]
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad ) \\
-& ) \\
+& \ff{while}.(\ff{eq}.(flag 0), \br
+& \quad \ff{seq}(flag.\ff{write}(1), \br
+& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\[-1pt]
 \end{split}
@@
 
-\begin{equation} \nonumber
-\begin{split}
+\begin{equation*}
+\dfrac
+    {\begin{matrix}
     & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
     & \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
-\end{split}
-\end{equation}
-
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
+    \end{matrix}}
+    {\begin{matrix}
     & \ff{memory}(flag), \\
@@
     & \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad ) \\
-& ) \\
-\end{split}
-\end{equation}
+    & \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\
+    \end{matrix}}
+    \jrule{3}
+\end{equation*}
 
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
 
@@
   [g]
-    |\sgm{1}||$\label{ln:ret8}$|
+    |\sgm{1}| > @ |$\label{ln:ret8}$|
       |\sgm{2}|
@@
 
-Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as W.
+Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as $W$.
 
-Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition is TRUE.
+Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
 So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.
@@
 
-Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as W'.
+Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as $W'$.
 
-Let's look at an example of a chain of nested objects containing a goto backward:
+Let's look at an example of a chain of nested objects containing a goto-backward:
 
@@
   [g]
-    |\sgm{0}|
+    |\sgm{0}| > @
       W
@@
 \begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
+& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2))\rrbracket) \br
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{while}.(\mu_0, \\
-& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
+& \quad \quad \ff{while}.(\mu_0, \br
+& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 )))\rrbracket) \\[-1pt]
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \quad \ff{while}.( \\
-& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad \quad ) \\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
+& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
+& \quad \quad \quad \ff{while}.( \br
+& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
+& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))))\rrbracket) \\[-1pt]
 \end{split}
@@
 & flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{while}.( \\
-& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad ) \\
-& \quad ) \\
-&  ) \\
+& \ff{while}.(\ff{eq}.(flag 0), \br
+& \quad \ff{seq}(flag.\ff{write}(1), \br
+& \quad \quad \ff{while}.( \br
+& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
+& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\[-1pt]
 \end{split}
@@
 
-\begin{equation} \nonumber
-\begin{split}
+\begin{equation*}
+\dfrac
+    {\begin{matrix}
     & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
     & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
+    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) ) \rrbracket ) \\
+    \end{matrix}}
+    {\begin{matrix}
     & \ff{memory}(flag), \\
@@
     & \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad ) \\
-& \quad ) \\
-&  ) \\
-\end{split}
-\end{equation}
+    & \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\
+    \end{matrix}}
+    \jrule{4}
+\end{equation*}
 
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.
+To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
 
@@
 
-To understand that the logic is not broken, let's look at a special case of calling goto backward inside a while-loop.
+To understand that the logic is not broken, let's look at an abstract case of calling goto-backward inside a while-loop.
 
@@
 
-Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as Z.
+Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as $Z$.
 
-As described in section 3.2.2, the program runs from top to bottom until it meets goto forward and if the jump condition is met, the abstract object g is executed again.
-Similar to what was said in section 3.2.2, all objects inside the abstract object g should be copied at the jump point.
+Similar to the technique we used in section 3.1.3 with goto-forward inside the while loop, in this case, to avoid all subsequent iterations of the inside while loop, we combine its condition with the jump condition.
+As in Section 3.2.2, we create a global flag object, which will be an indicator of the execution of the jump condition.
+As soon as the jump condition is met, we change the flag value, and the next iteration of the inside while loop will fail during the check due to our added combined execution condition.
 
-The only difference, when the jump itself frames a while loop, is that when the jump condition is met, we need to interrupt the execution of all the internal while loops inside the new while loop, which we replaced the jump with.
+The rest of the transformation looks identical to that described in section 3.2.2: create a global while loop with a check for moisture values, Invert the jump condition and if the goto-backward condition is met, change the value of the flag object.
+It is also necessary to wrap all objects that lie inside the abstract object \emph{g} in an additional if-statement with a check for the flag value, so that all of them are not fulfilled as soon as the jump condition is met.
 
-In order to interrupt the execution of each of the internal while loops, we can add an additional condition to each of them, whether the jump condition is met or not.
-This can be done with an additional flag object that will signal for each inner while loop whether the jump condition has been met.
-
-So, all internal while loops will not be executed further if flag shows that the jump condition is met and the logic of the program is not violated.
-For all other objects inside our new while loop, we should apply the transformation described in section 3.2.2.
-
-The transformation will look like this:
+The transformation will be presented as:
 
@@
 
-Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as Z'.
+Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as $Z'$.
 
@@
 The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
-The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if you need to make a replacement in the while loop, containing a jump - we use transformations 3.1.3 and 3.2.3 accordingly.
-If you need to make a replacement for a normal object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
+The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if needs to make a replacement in the while loop, containing a jump - use transformations 3.1.3 and 3.2.3 accordingly.
+If needs to make a replacement for a simple object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
 

### 2022-06-30 paper/skeleton.tex
Update skeleton.tex

@@
 \usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
+\usepackage{debate}
 \usepackage{listings}
@@
 
+\newtheorem{theorem}{Theorem}[section]
 \newtheorem{definition}{Definition}[section]
+\newtheorem{corollary}{Corollary}[theorem]
 
@@
 
+The proposed algorithm is a series of transformations that are performed depending on the type of "jump".
+In total, we describe 6 types of transformations: \emph{Simple forward}/\emph{backward} (further \emph{SF}/\emph{SB}), \emph{Goto forward/backward wrapped by object} (further \emph{OF}/\emph{OB}) and \emph{Goto forward/ backward inside the while-loop} (further \emph{WF}/\emph{WB}).
+Transformations are not sequential and independent, and each one is executed in its own particular case.
+For example, \emph{SF}/\emph{SB} is only a "preparation" for the actual replacement of the jump by a semantically equivalent analog and is executed if there is no condition before the jump itself.
+\emph{OF}/\emph{OB} is the main transformation, as it contains the jump replacement itself and covers most possible cases of calling forward or backward jump.
+\emph{WF}/\emph{WB} is a "addition" for the previous transformation, since the behavior of the \emph{while.} object in EO is different from all other objects and the call of the jump inside the loop requires separate consideration.
+
+Thus, the algorithm itself consists of the following steps: 
+\begin{inparaenum}[1)]
+\item Apply \emph{SF}/\emph{SB} transformation if necessary,
+\item Find all occurrences of forward/backward jump's calls,
+\item Apply \emph{OF}/\emph{OB} transformations to all of them,
+\item If there is a \emph{while.} object that wraps the jump call, apply the \emph{WF}/\emph{WB} transformation.
+\end{inparaenum}
+
+The combination of all 6 transformations makes a complete algorithm for getting rid of the GOTO object, as they cover all possible cases of using GOTO and forward/backward jumps in the language.
+
 Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can contain others.
@@
 \end{definition}
-
-The solution we propose contains two types of transformations - forward jump and backward jump.
-The algorithm itself consists in applying these transformations to replace both types of jumps.
-
-\vspace{5mm}
 
@@
 
-\item $\mu$ - Denotes an object or a chain of nested objects that return a boolean value (TRUE/FALSE) when executed.
+\item $\mu$ - Denotes a not-empty object or a chain of nested objects that return a boolean value (TRUE/FALSE) when accessed.
 \end{itemize}
@@
 
-We will also look at our transformations in the form of $\varphi$-calculus, on which EO is based.
+We will also consider our transformations in the form of $\varphi$-calculus, on which EO is based.
 The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application, and decoration.
@@
 
-$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
+%%$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
 
@@
 \subsubsection{Simple Forward}
-Consider the simplest example of using goto-forward:
+
+The \ff{goto} object may be used for unconditional forward jumps. In general case, covering most of the cases of calling goto-forward, it appears as:
 
@@
   [g]
-    g.forward |\dlt{1}| > @
+    |\sgm{1}| > @
+      |\sgm{2}|
+      g.forward |\dlt{1}|
+      |\sgm{3}|
 \end{ffcode}
 
-In terms of $\varphi$-calculus, this code will appear as:
+Here, \dlt{1} is any object, which will become the result of dataization of the \ff{goto} object, $\sigma_1$, $\sigma_2$ are ob
+In terms of $\varphi$-calculus, this code may be expressed as:
 
@@
 \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{forward} (\delta_1) \rrbracket ) \\
+& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
+& \quad \quad \quad \varphi \mapsto \sigma_1( \sigma_2, \ff{g}.\ff{forward} (\delta_1), \sigma_3) \rrbracket ) \\
 \end{split}
 \end{equation}
+
+Where in parentheses are denoted free attributes, in square brackets are denoted bound attributes and the symbol $\mapsto$ denotes application/decoration of an object.
 
@@
 \begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing,\br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket)\\
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \sigma_1 (\sigma_2, \br
+& \quad \quad \quad \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ), \sigma_3) \rrbracket)\\
 \end{split}
@@
 
-Same example on EO:
+Same example in EO:
 
@@
 
-\subsubsection{Goto forward wrapped in an object}
+\subsubsection{Goto forward wrapped by object}
 
-After the conversion described in section 3.1.1, the simplest call of forward jump will be presented as:
+After the transformation described in section 3.1.1, the general case of calling forward jump will be presented as:
+
+\begin{equation}
+\begin{split}
+& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \sigma_1 (\sigma_2, \br
+& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2 ), \sigma_3) \rrbracket)\\
+\end{split}
+\end{equation}
+
+\begin{theorem}
+A goto object that contains an object or a chain of nested objects that wrap the \emph{.forward} attribute can be converted to a similar one, but without using the \emph{.forward} attribute.
+\end{theorem}
+
+In terms of $\varphi$-calculus, it can be represented as the following inference rule:
+
+\begin{equation*}
+\dfrac
+    {\begin{matrix}
+    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \sigma_1 (\sigma_2, \\
+    & \quad \quad \quad \quad \ff{if}.( \mu_1,     \ff{g}.\ff{forward}(\delta_1), \delta_2 ), \sigma_3) \rrbracket)\\
+    \end{matrix}}
+    {\begin{matrix}
+    & \sigma_1(\sigma_2, \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1), \\
+    & \quad \quad \ff{if.}(\mu_1.\ff{not}, \sigma_3, TRUE)) \\
+    \end{matrix}}
+    \jrule{1}
+\end{equation*}
+
+\begin{proof}
+To get rid of using ".forward" attribute, it is required to emulate work of jump itself.
+
+First of all, let's invert condition of jump, swap objects in "THEN"/"ELSE" brunches of if-statement and remove \emph{.forward} attribute:
 
@@
 & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+& \quad \quad \varphi \mapsto \sigma_1 ( \sigma_2,  \ff{if}.(\mu_1.not, \delta_2, \delta_1), \sigma_3) \rrbracket) \\
 \end{split}
@@
 
-The transformation under consideration involves the following steps:
+Since the jump does not execute all statements following the jump itself, we need to protect their execution by checking the jump condition for each of them:
 
@@
 & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \br
+& \quad \quad \varphi \mapsto \sigma_1(\sigma_2,  \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1), \br
+& \quad \quad \quad \ff{if.}(\mu_1.\ff{not}, \sigma_3, TRUE)) \rrbracket) \\
 \end{split}
@@
 
+Thus, all objects that would not have executed in the presence of the \emph{.forward} attribute will not be executed now.
+And objects that were returned in branches of the old if-statement will also be executed under the same condition.
+
+\end{proof}
+
+\begin{corollary}
+If there are no \emph{.forward} attributes inside the abstract object goto, no jumps will be performed and therefore it is possible to delete the abstract object goto itself without losing logic.
+\end{corollary}
+
 \begin{equation}
 \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \br
+& \sigma_1( \sigma_2, \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1), \br
+& \quad \quad \ff{if.}(\mu_1.\ff{not}, \sigma_3, TRUE)) \\
 \end{split}
@@
 
-\begin{equation}
-\begin{split}
-& \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1) \br
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 3 is semantically equivalent to expression 6:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket)
-    \end{matrix}}
-    {\ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1)}
-    \jrule{1}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
+Let's see, how this transformation will be presented in EO.
 
@@
 
-Now let's look at an example program with nested objects containing goto-forward:
+Now let's look at an example of transformation, if the code fragment \emph{X} is wrapped into an object:
 
@@
 
-\subsubsection{Goto backward wrapped in an object}
+\subsubsection{Goto backward wrapped by object}
 After the conversion described in Section 3.2.1, the simplest call of backward jump will be presented as:

### 2022-09-20 paper/skeleton.tex
upd paper

--- 2022-06-18 paper/skeleton.tex
@@
 \settopmatter{printfolios=false,printccs=false,printacmref=false}
-\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
+\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false,backend=biber]{biblatex}
+\usepackage{debate}
+\usepackage[T2A,T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{graphicx}
-\usepackage{xcolor}
+\usepackage[russian,english]{babel}
+\renewcommand\ttdefault{cmtt}
+\usepackage{csquotes}
 \usepackage{ffcode}
+\usepackage{CJKutf8}
+\usepackage{paralist}
+\usepackage{cancel} % to enable \cancel command
+\usepackage{anyfontsize} % To get rid of font not found warnings
+\usepackage{tabularx} % for special tables
 \usepackage{amsmath}
+\usepackage{to-be-determined}
+\usepackage{href-ul}
+\usepackage{amsthm}
+\usepackage{cleveref}
+\usepackage{tcolorbox} % for algorithm
+\tcbuselibrary{skins}
+\usepackage{fdsymbol} % for \mathbb
+\usepackage{algpseudocode} % for algorithms
+\usepackage{multicol} % for two cols in BNF
+\usepackage{pgffor} % to enable \foreach
+\usepackage{stmaryrd}
+\usepackage{mathtools}
+\newtheoremstyle{theorems}
+{} % Space above
+{} % Space below
+{} % Theorem body font % (default is "\upshape")
+{} % Indent amount
+{\scshape} % Theorem head font % (default is \mdseries)
+{.} % Punctuation after theorem head % default: no punctuation
+{ } % Space after theorem head
+{} % Theorem head spec
+\theoremstyle{theorems}
+\newtheorem{eodefinition}{Definition}
+\newtheorem{eotheorem}{Theorem}
 
-\newtheorem{definition}{Definition}[section]
+\addbibresource{refs.bib}
 
-\graphicspath{ {./images/} }
+\newcommand\br{\\[-4pt]}
+\newcounter{rule}
+\renewcommand\therule{R\arabic{rule}}
+\newcommand\rr{\smalltriangleright{}}
+\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
+\newcommand{\jrule}[1]{%
+    \refstepcounter{rule}\label{rule:#1}%
+    \text{\textbf{\rrule{#1}}}}
+
+\newcommand\sgm[1]{$\sigma_#1$}
+\newcommand\dlt[1]{$\delta_#1$}
+\newcommand\m[1]{$\mu_#1$}
 
@@
 
-\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}
-
     \section{Introduction}
-The problem is known both computer science and soft-
-ware engineering communities for a few decades and formulated by several scientists.
-
-Many of them have offered solutions to this problem. (Look at Related Work)
+    The problem of eliminating Jump-like statements is known for both computer science and software engineering communities for a few decades and formulated by several scientists, some of which have suggested solutions for this problem.
 
     The presence of jump statements in the source code makes it impossible to use the functional method of analysis.
+    Other program analysis methods, including those based on symbolic execution techniques, will also benefit from the removal of jump statements, which are well-known obstacles to the precision of analysis, as explained by \citet{baldoni2018survey}.
 
-There are an "object-flow" languages where we can control flow through an objects.
-An example of such language is EO (Elementary Objects language).
+    There are an "object-flow" languages where the execution flow is controlled by object composition.
+    An example of such a language is EO, which is based on $\varphi$-calculus introduced by \citet{bugayenko2021eolang} and formalized by \citet{kudasov2021}.
     This is a strictly object-oriented programming language in which any action is described by creating a new object, or decorating an existing one.
 
-We are trying to answer the following research question: "Is it possible for any program, written on "object-flow" language like EO and containing GOTO objects to find a semantically equivalent program, but without using them?"
+    We are trying to answer the following research question: "Is it possible for any program, written in 'object-flow' language like EO and containing GOTO objects, to find a semantically equivalent program, but without GOTO objects?"
 
     \section{Related work}
+    The problem was firstly formulated by \citet{dijkstra1968letters}: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages.
+    Even though a few years later \citet{knuth1974structured} showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements \citep{arsac1977construction}.
+
     To solve the problem of eliminating Jump statements in other programming languages, the following works were published:
-Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
-Ramshow proposed an algorithm for Pascal programs;
-Ceccato suggested how to eliminate GOTO during migration of legacy code to Java.
+    \Citet{williams1985restructuring} created a tool for restructuring Pascal code;
+    \Citet{jonsson1989next} was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements;
+    \Citet{erosa1994taming} suggested an algorithm for automatic elimination of GOTO statements in~C;
+    \Citet{zegour1994new} explained how GOTO elimination may work in any language, as long as it has jump statements and control structures;
+    \Citet{morris1997goto} suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
+    \Citet{ramshaw1988eliminating} proposed an algorithm for Pascal programs;
+    \Citet{ganapathi2008shim} introduced optimization method for SHIM IR;
+    \Citet{ceccato2008goto} suggested how to eliminate GOTO during migration of legacy code to Java.
 
-To our knowledge, there is still no method which enables automatic elimination of jump objects in programs written in such an object-flow languages.
+    However, to our knowledge, there is still no method available, which enables automatic elimination of jump objects in programs written in such an object-flow languages.
+
+    \section{Definitions and designations}
+    \begin{eodefinition}
+        \emph{Dataization} in $\varphi$-calculus is a process of retrieving data from an object.
+        The dataization of an object at the highest level of composition leads to the execution of a program.
+    \end{eodefinition}
+    \begin{eodefinition} \emph{Nesting} of the current object determines the number of objects that encapsulate current object via abstraction, application, or decoration directly or through other objects.
+
+    For example, here object $x$ has 3-rd level of nesting:
+    \begin{ffcode}
+        o1
+        o2
+        ...
+        o3
+        o4
+        x
+    \end{ffcode}
+    \end{eodefinition}
+    \begin{eodefinition}
+        \emph{Forwarding goto} denotes an object \ff{goto}, which encapsulate object \ff{forward} directly or through other objects:
+        \begin{ffcode}
+            goto
+            [o1]
+            ...
+            |$\leadsto$|o1.forward o2
+            ...
+        \end{ffcode}
+    \end{eodefinition}
+    \begin{eodefinition}
+        \emph{Backwarding goto} denotes an object \ff{goto}, which encapsulate object \ff{backward} directly or through other objects:
+        \begin{ffcode}
+            goto
+            [o1]
+            ...
+            |$\leadsto$|o1.backward
+            ...
+        \end{ffcode}
+    \end{eodefinition}
+    \emph{Designations:}
+    \begin{itemize}
+        \item "$>$" is used to name attributes of an object, where on the left side of ">" is attribute itself and its name on the right side,
+        \item "$[]$" is used for the specification of parameters of abstract objects,
+        \item "$@$" is used to denote the object being decorated,
+        \item "$\mapsto$" is used to denote an object, where free attributes stay in the parentheses on the left side and pairs, which represent bound attributes, stay on the right side, in double-square brackets,
+        \item "$\leadsto$" denotes an arbitrary \emph{nesting} of an object, i.e. it can be encapsulated by an arbitrary number of objects.
+    \end{itemize}
+
+    \section{Sample}
+    Let's consider the following example of code in EO, which uses GOTO object:
+
+    \begin{ffcode}
+        memory 0 > x
+        [] > func
+        goto > @
+        [g]
+        seq > @
+        x.write (x.plus 1)
+        if.
+        x.lt 10
+        g.backward
+        QQ.io.stdout "X >= 10!\n"
+        g.forward x
+    \end{ffcode}
+
+    \debate[Yegor]{Here I suggest we briefly explain the syntax of EO, since the language is not widely known.
+The reader will not understand what this code means and won't be able to digest it.
+Moreover, I would even suggest to also show a similar code in C++ language, so that the reader understand it better.
+
+    ----------------Done}
+
+    In this code snippet declares an \emph{atom}-object \ff{goto} with attribute \ff{g};
+    mutable object \ff{memory}, which allows to reinitialize the bound object \ff{x} via \ff{.write} attribute;
+    object \ff{eq}, which checks the equality of the objects passed to it;
+    object \ff{if}, implementing behavior of branching;
+    object \ff{seq}, which contains bound attributes as objects, which will be sequentially dataized;
+    objects \ff{backward} and \ff{forward}, which are implementing behaviour of jumps: first of them starts dataization of object \ff{g} again, while the second one dataizes an object, passed as an attribute, and terminates dataization of object \ff{g}.
+
+    Similar code snippet on C++ will be represented as:
+    \begin{ffcode}
+        int x = 0;
+        int func() {
+            l1:
+            x = x + 1;
+            if (x < 10)
+            goto l1;
+            else
+            cout << "X >= 10!\n";
+            return x;
+        }
+    \end{ffcode}
+
+    We provide four independent transformations that replace \ff{goto} objects with a semantically equivalent analogue. After transformations, this example will appear as:
+    \begin{ffcode}
+        memory 0 > fl_1
+        memory -1 > fl_2
+        memory 0 > x
+        [] > func
+        seq > @
+        fl_1.write 0
+        fl_2.write -1
+        while. > rem!
+        or.
+        fl_1.eq 0
+        fl_2.eq -1
+        [i]
+        seq > @
+        fl_1.write 1
+        fl_2.write 0
+        x.write (x.plus 1)
+        if.
+        x.lt 10
+        fl_1.write 0
+        QQ.io.stdout "X >= 10!\n"
+        if.
+        fl_1.eq 1
+        fl_2.write 1
+        TRUE
+        if.
+        fl_2.eq 1
+        x
+        rem
+    \end{ffcode}
+
+    Here, \ff{while} is an object, implementing behavior of loops: its first bound attribute implements condition of loop dataization and second one implies "body" of loop.
+
+    On C++, the code snippet above after transformation will presented as:
+    \begin{ffcode}
+        int fl_1 = 0;
+        int fl_2 = 0;
+        int x = 0;
+        int func() {
+            fl_1 = 0;
+            fl_2 = -1;
+            do {
+                fl_1 = 1;
+                fl_2 = 0;
+                x = x + 1;
+                if (x < 10)
+                fl_1 = 0;
+                else
+                cout << "X >= 10!\n";
+                if (fl_1 == 1)
+                fl_2 = 1;
+            } while (fl_1 == 0 || fl_2 == -1);
+            if (fl_2 == 1)
+            return x;
+        }
+    \end{ffcode}
+
+    Thus, the main purpose of our research is:
+    \begin{enumerate}
+        \item To formulate inference rules for the transformations that we propose,
+        \item proof that these 4 transformations are necessary and sufficient to solve the problem under consideration,
+        \item suggest a program tool, which
+        enables automatic elimination of jump objects in programs written in EO.
+    \end{enumerate}
 
@@
 
-Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called \emph{atoms}. 
-So all jump statements are implemented as a
-single \emph{atom}-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
+    Some objects in EO may need to be platform specific and can’t be composed from other existing objects — they are called \emph{atoms}.
+    All jump statements are implemented as a
+    single \emph{atom}-object \ff{goto}.
+    The implementation of \ff{goto} in EO implies two types of jumps - forward jump and backward jump.
+    It is required to cover all possible cases for both of them.
 
-Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can contain others.
+%%The proposed algorithm is a series of transformations that are performed depending on the type of "jump".
+    In total, we describe 4 types of transformations:
+    \begin{inparaenum}[1)]
+    \item \emph{Simple goto} (further \emph{SG}),
+    \item \emph{Goto forward/backward} (further \emph{GF}/\emph{GB}) and
+    \item \emph{Terminating the while object} (further \emph{TW}).
+
+    Transformations are independent and not sequential, and each one is executed in its own particular case.
+    For example, \emph{SG} is only a "preparation" for the actual replacement of the jump by a semantically equivalent analog and is executed if there is no condition before the jump itself.
+    \emph{GF}/\emph{GB} are the main transformations, as they contain the jump replacement itself and cover most possible cases of using forward and backward jumps.
+    \emph{TW} is an "addition" for \emph{GF} and \emph{GB} transformations, since the behavior of the \ff{while} object in EO is different from all other objects and dataization of jump inside the loop requires separate consideration.
+    \end{inparaenum}
+
+%%Thus, the algorithm itself consists of the following steps:
+%%\begin{inparaenum}[1)]
+%%\item Apply \emph{SF}/\emph{SB} transformation if necessary,
+%%\item Find all occurrences of forward/backward jump's calls,
+%%\item Apply \emph{GF}/\emph{GB} transformations to all of them,
+%%\item If there is a \emph{while.} object that wraps the jump call, apply the \emph{WF}/\emph{WB} transformation.
+%%\end{inparaenum}
+
+    The combination of all 4 transformations implies a complete algorithm for getting rid of the GOTO object, as they cover all possible cases of using GOTO and forward/backward jumps in the language.
+
+    Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can encapsulate others.
     It should be noted that each object in the program has its own level of \emph{nesting} relative to other objects.
 
-\begin{definition} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
-\end{definition}
+    \debate[Yegor]{If you give a definition, make sure it's followed by example. Now it's not really clear what it means.
 
-The solution we propose contains two types of transformations - forward jump and backward jump.
-The algorithm itself consists in applying these transformations to replace both types of jumps.
+    -----------------Done}
 
-\vspace{5mm}
-
-\emph{Designations:}
-
-\begin{itemize}
-\item $\sigma$ - Denotes either an object, a chain of nested objects or the absence of an object.
-
-\item $\delta$ - Denotes a not-empty object or a chain of nested objects that return a not-NULL value when accessed.
-
-\item $\mu$ - Denotes an object or a chain of nested objects that return a boolean value (TRUE/FALSE) when executed.
-\end{itemize}
-
-\newcommand\sgm[1]{$\sigma_#1$}
-\newcommand\dlt[1]{$\delta_#1$}
-\newcommand\m[1]{$\mu_#1$}
-
-We will also look at our transformations in the form of $\varphi$-calculus, on which EO is based.
-The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application, and decoration.
+    We will also consider our transformations in the form of $\varphi$-calculus, on which EO is based.
+    The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application and decoration.
     The calculus introduces a formal apparatus for manipulations with objects.
 
-$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
+    \subsection{Simple goto} \label{SG}
+    As mentioned above, this transformation is a "preparation" for \emph{GF}/\emph{GB} which are make the replacement of object \ff{goto} itself.
+    Since \emph{GF} and \emph{GB} only consider the use of the \ff{forward}/\ff{backward} objects when they are directly encapsulated in the \ff{if} object(\cref{GF}/\cref{GB}), it is required to add an additional \ff{if} when it is absent before the jump.
+    Thus, the transformation under consideration adds an additional fictitious condition $\emph{if (true)}$ if it necessary.
 
-\subsection{Forward jump}
-Goto forward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      g.forward |\dlt{1}|
-      stdout "Will never be printed"
-\end{ffcode}
-
-It consists of the goto atom-object, the abstract object \emph{g}, and the g.forward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.
-
-\subsubsection{Simple Forward}
-Consider the simplest example of using goto-forward:
-
+    Let's consider the case where the \ff{forward} is not directly encapsulated in the \ff{if} object:
     \begin{ffcode}
@@
         [g]
-    g.forward |\dlt{1}| > @
+        |$\leadsto$|x|$\label{ln:sf0}$|
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        g.forward y
+        |$\alpha_{n+1}$|
+        ...
+        |$\alpha_{m}$||$\label{ln:sf1}$|
+    \end{ffcode}
+    Here, $\alpha_{i}$, $x$ and $y$ defines any object in the language, excluding \ff{if}.
+
+    Applying the transformation, the example above maps to:
+    \begin{ffcode}
+        goto
+        [g]
+        |$\leadsto$|x|$\label{ln:tsf0}$|
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        if.
+        TRUE
+        g.forward y
+        TRUE
+        |$\alpha_{n+1}$|
+        ...
+        |$\alpha_{m}$||$\label{ln:tsf1}$|
     \end{ffcode}
 
-In terms of $\varphi$-calculus, this code will appear as:
-
+    Describing transformation in terms of $\varphi$-calculus, code at lines ~\ref{ln:sf0}---\ref{ln:sf1} will be represented as:
     \begin{equation}
         \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{forward} (\delta_1) \rrbracket ) \\
+            & x(\alpha_1,\,\ldots\,,\,\alpha_n, \br
+            & \quad \emph{g}.\ff{forward}( y ), \br
+            & \quad \alpha_{n+1},\,\ldots\,,\,\alpha_m) \\
+        \end{split}
+    \end{equation}
+    and code at lines ~\ref{ln:tsf0}---\ref{ln:tsf1} as:
+    \begin{equation}
+        \begin{split}
+            & x(\alpha_1,\,\ldots\,,\,\alpha_n, \br
+            & \quad \ff{TRUE}.\ff{if}(\emph{g}.\ff{forward}( y )), \br
+            & \quad \alpha_{n+1},\,\ldots\,,\,\alpha_m) \\
         \end{split}
@@
 
-Note that in this example, g.forward is simply an attribute of the abstract object \emph{g} and is executed as soon as the queue reaches it.
-Our transformation only considers the jumps that are made when a condition for it is fulfilled.
-In cases where there is unconditional jump, first of all we transform it into conditional jump by adding an additional if-statement - if (TRUE).
-This will not violate the program logic, because without the added if-statement, the jump would always be executed, and statements coming after this jump with a nesting not less that the nesting of the abstract object \emph{g} would never be executed:
+    \begin{eotheorem}
+        Any object is semantically equivalent to the same object encapsulated in \ff{TRUE}.\ff{if}:
+        \begin{equation*}
+            \forall x (x \equiv \ff{TRUE}.\ff{if}(x)).
+        \end{equation*}
+    \end{eotheorem}
 
+    \begin{proof}
+        By definition of the language, if there is any object \emph{Z}, then the following equivalence follows:
+        \begin{equation}
+            Z \equiv if(true,\,Z,\,true),
+        \end{equation}
+        where first argument in \emph{if} is condition itself, second argument dataizes when condition is \emph{true} and third argument dataizes when condition is \emph{false}.
+    \end{proof}
+
+    \begin{equation*}
+        \dfrac
+        {\begin{split}
+             & x(\alpha_1,\,\ldots\,,\,\alpha_n, \br
+             & \quad \emph{g}.\ff{forward}( y ), \br
+             & \quad \alpha_{n+1},\,\ldots\,,\,\alpha_m) \\
+        \end{split}}
+        {\begin{split}
+             & x(\alpha_1,\,\ldots\,,\,\alpha_n, \br
+             & \quad \ff{TRUE}.\ff{if}(\emph{g}.\ff{forward}( y )), \br
+             & \quad \alpha_{n+1},\,\ldots\,,\,\alpha_m) \\
+        \end{split}}
+        \jrule{1}
+    \end{equation*}
+
+%%Note that in this example, \ff{forward} is simply an attribute of the abstract object \emph{g} and is dataized as soon as the queue reaches it.
+    In such cases where there is an "unconditional" jump, first of all we transform it into "conditional" jump by encapsulating it in additional object \ff{if}---\emph{if (true)}.
+    This will not violate the program logic, since added condition will always be \emph{TRUE} and "THEN" brunch of if-statement with object \ff{forward} will always be dataized.
+
+    The same logic applies with the \ff{backward} object.
+
+    \subsection{Goto forward} \label{GF}
+    In this section, we discuss the transformation by replacing \emph{forwarding goto} with a semantic equivalent.
+    Based on the concept of transformation, only cases in which \ff{forward} is directly encapsulated in the object \ff{if} are considered.
+
+    The essence of the transformation is that we create an additional $flag$ object which will assign as "0" or "1" and will show whether the jump condition has been met.
+    Instead of dataization \ff{forward}, we will dataize the object passed to it as an argument and reinitialize the $flag$ object.
+    Moreover, it is necessary to protect from dataization all objects following the \ff{if} object containing the jump, and with \emph{nesting} not less than that of the goto object itself, since they should not be dataized when the jump condition is met.
+    This requires encapsulating each such object with an additional object \ff{if} to check the equality $flag$ to an object \ff{TRUE} - i.e. whether the jump condition has been met before or not.
+
+    Let's consider the following example:
+    \begin{ffcode}
+        goto
+        [g]
+        |$\leadsto$|x|$\label{ln:of0}$|
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        if.
+        k
+        g.forward y
+        |$\alpha_{n+1}$|
+        |$\alpha_{n+2}$|
+        ...
+        |$\alpha_{m}$|
+        |$\alpha_{m+1}$||$\label{ln:of1}$|
+        ...
+    \end{ffcode}
+    Here, $\alpha_i$, $x$ and $y$ defines any object in the language, $k$ defines an object, which when dataized equals to a data object \ff{TRUE}.
+
+    \debate[Yegor]{We don't have 'values' in EO. We only have objects. Moreover, we don't 'return' anything. The result of dataization may be equal to a data object 'TRUE'.}
+
+    Applying the transformation, the example above maps
+    to:
+    \begin{ffcode}
+        memory 0 > flag
+        goto
+        [g]
+        |$\leadsto$|x|$\label{ln:tof0}$|
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        if.
+        k
+        seq
+        y
+        flag.write 1
+        |$\alpha_{n+1}$|
+        if.
+        eq. (flag 0)
+        |$\alpha_{n+2}$|
+        TRUE
+        ...
+        if.
+        eq. (flag 0)
+        |$\alpha_{m}$|
+        TRUE
+        if.
+        eq. (flag 0)
+        |$\alpha_{m+1}$|
+        TRUE|$\label{ln:tof1}$|
+        ...
+    \end{ffcode}
+
+    In terms of $\varphi$-calculus lines ~\ref{ln:of0}--\ref{ln:of1} appears as:
     \begin{equation}
         \begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket) 
+            & x (\alpha_1,\,\ldots\,,\,\alpha_n, \br
+            & \quad k.\ff{if}(\,\emph{g}.\ff{forward}( y ),\,\alpha_{n+1}),\br
+            & \quad \alpha_{n+2},\,\ldots\,,\,\alpha_m), \\
+            & \alpha_{m+1} \\
+        \end{split}
+    \end{equation}
+    whereas the lines ~\ref{ln:tof0}--\ref{ln:tof1} will be represented as:
+    \begin{equation}
+        \begin{split}
+            & x (\alpha_1,\,\ldots\,,\,\alpha_n, \br
+            & \quad k.\ff{if}(\ff{seq}(y,\,flag.\ff{write}(1)),\,\alpha_{n+1}),\br
+            & \quad flag.\ff{eq}(0).\ff{if}(\alpha_{n+2}),\,\ldots\,,\br
+            & \quad flag.\ff{eq}(0).\ff{if}(\alpha_m)), \\
+            & flag.\ff{eq}(0).\ff{if}(\alpha_{m+1}) \\
         \end{split}
@@
 
-Same example on EO:
+    \begin{eotheorem}
+        \emph{Forwarding goto} maps to semantically equivalent analog without \ff{forward} objects:
+        \begin{equation*}
+            \begin{split}
+                & \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\,\varphi\,\leadsto\,x(\ldots,\,\leadsto g.\ff{forward}(y),\,\ldots)\rrbracket) \\
+                & \downarrow \\
+                & \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\,\varphi\,\leadsto\,x(\ldots,\,\leadsto y,\,\ldots)\rrbracket) \\
+            \end{split}
+        \end{equation*}
+    \end{eotheorem}
 
+    \begin{proof}
+        Let's introduce the following recursive function:
+        \begin{equation}
+            \begin{split}
+            (\forall x\,\in\,\emph{attr}(\emph{g})):\,\phi(x)\,&\rightarrow\,(\mu(x),\,\phi(x'\,\neq\,x)) \\
+            &\rightarrow\,(\mu(x),\,(\mu(x'),\,\phi(x''))) \\
+            &\ldots
+            \end{split}
+        \end{equation}
+        where \emph{attr}(\ldots) denotes all attributes of an object,
+        \begin{equation}
+            \begin{split}
+                & \mu(x)\,\rightarrow flag.\ff{eq}(0).\ff{if}(x) .\\
+            \end{split}
+        \end{equation}
+        Then the Ex. \ref{GFex1} maps to Ex. \ref{GFex2} according to the logic of dataization of \ff{goto} object with an attribute \ff{forward}.
+        \debate[Yegor]{The discussion flow is broken here. Why this expression is here? What it belongs to? You can't start a sentence with an expression.}
+        \begin{equation}\label{GFex1}
+        \begin{split}
+            & \ff{goto}(\llbracket\,\emph{g}\,\mapsto\,\varnothing,\br
+            & \quad \quad \varphi\,\leadsto\,x(\ldots,\br
+            & \quad \quad \quad k.\ff{if}(\emph{g}.\ff{forward}(y),\,z),\br
+            & \quad \quad \quad w,\,\ldots)\rrbracket) \\
+        \end{split}
+        \end{equation}
+        Here, $x$, $w$, $y$ and $z$ defines any object in the language, $k$ defines an object, which when dataized equals to a data object \ff{TRUE}.
+        \begin{equation}\label{GFex2}
+        \begin{split}
+            & \ff{goto}(\llbracket\,\emph{g}\,\mapsto\,\varnothing,\br
+            & \quad \quad \varphi\,\leadsto\,x(\ldots,\br
+            & \quad \quad \quad k.\ff{if}(\ff{seq}(y,\,flag.\ff{write}(1)),\,z),\br
+            & \quad \quad \quad \phi(w))\rrbracket) \\
+        \end{split}
+        \end{equation}
+        Indeed, depending on the jump condition, the same objects will be dataized as when dataization the \ff{forward} object itself.
+    \end{proof}
+
+    \begin{eotheorem} \label{delDef}
+    Object \ff{goto} without attributes \\
+    \ff{forward} and \ff{backward} inside is equivalent to object \ff{seq}.
+    \end{eotheorem}
+
+    \begin{proof}
+        By definition of the language, behavior of object \ff{goto} without attributes \ff{forward}/\ff{backward} inside is similar to behavior of an object \ff{seq}.
+        \begin{equation}
+            \begin{split}
+                & \ff{goto}(\llbracket \emph{g}\,\mapsto\,\varnothing,\,\varphi\,\mapsto\,x(\alpha_1,\,\ldots\,,\,\alpha_n)\rrbracket) \\
+                & \downarrow \\
+                & \ff{seq}(x(\alpha_1,\,\ldots\,,\,\alpha_n))
+            \end{split}
+        \end{equation}
+    \end{proof}
+
+    \begin{equation*}
+        \dfrac
+        {\begin{split}
+             & \ff{goto}(\llbracket\,\emph{g}\,\mapsto\,\varnothing,\br
+             & \quad \quad \quad \varphi\,\leadsto\,x(\ldots,\br
+             & \quad \quad \quad \quad k.\ff{if}(\emph{g}.\ff{forward}(y),\,z),\br
+             & \quad \quad \quad \quad w,\,\ldots)\rrbracket) \\
+        \end{split}}
+        {\begin{split}
+             & \ff{memory}(0)\,\mapsto\,flag, \\
+             & \ff{seq}(\leadsto x(\ldots,\br
+             & \quad \quad k.\ff{if}(\ff{seq}(y,\,flag.\ff{write}(1)),\,z),\br
+             & \quad \quad \phi(w))) \\
+        \end{split}}
+        \jrule{2}
+    \end{equation*}
+
+    It is not difficult to notice that objects which goto-forward "jumps through" will be dataized if the condition in the if-statement is not equal to \ff{TRUE}.
+    So before dataization such each object, that follows the jump, we can check condition of the jump.
+    It can be done via mutable object \ff{memory} and additional \ff{if} objects.
+    This is required so that all objects following the jump that are attributes of the abstract object $g$ straightforwardly or throw other objects are not dataized.
+    So, by encapsulating each object, following the jump and whose \emph{nesting} is at least that of the $g$ object, in this additional \ff{if} object with a $flag$ check, we make sure that these objects will not be dataized when the jump condition is met.
+
+    \subsection{Goto backward} \label{GB}
+    Here we describe how to replace \ff{goto} object which has an attribute \ff{backward} inside to a semantic equivalent.
+    Based on the concept of transformation, only cases in which attribute \ff{backward} is directly encapsulated in \ff{if} object are considered.
+
+    When dataized, the \ff{backward} object aborts the current dataization of the \ff{goto} object and starts it again.
+    In fact, such an implementation is equal to the DO-WHILE construct from other languages.
+    The essence of the transformation is that we "emulate" the work of this construct.
+    Since there is no such functionality in the language, we use the \ff{while} object and the mutable $flag$ object, from the result of dataization of which the loop will be dataized.
+
+    At the beginning, we assign $flag$ object to "0".
+The \ff{while} object condition checks that the \ff{flag} value is equal to "0".
+Then in the "body" of the loop, we change the value of $flag$ to "1".
+If the jump condition is \ff{TRUE}, then the \ff{flag} value is required back to "0".
+This is necessary for the condition of the loop to be fulfilled and the next "iteration" begins.
+
+    Same as at \ref{GF}, it is necessary to protect from dataization all objects following the \ff{if} object containing the jump, and with \emph{nesting} not less than that of the \ff{goto} object itself, since they should not be dataized when the jump condition is \ff{TRUE}.
+    This requires encapsulating each such object in object \ff{if} to check the value of $flag$---i.e. whether the jump condition has been fulfilled before or not.
+
+    Let's consider the following example of object \ff{goto} with \ff{backward} attribute:
     \begin{ffcode}
@@
         [g]
-    if. > @
+        |$\leadsto$|x|$\label{ln:GB0}$|
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        if.
+        k
+        g.backward
+        |$\alpha_{n+1}$|
+        |$\alpha_{n+2}$|
+        ...
+        |$\alpha_{m}$||$\label{ln:GB1}$|
+    \end{ffcode}
+    Applying transformation this example maps to:
+    \begin{ffcode}
+        memory 0 > fl|$\label{ln:TGB0}$|
+        while.
+        fl.eq 0
+        [i]
+        seq > @
+        fl.write 1
+        |$\leadsto$|x
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        if.
+        k
+        fl.write 0
+        |$\alpha_{n+1}$|
+        if.
+        fl.eq 1
+        |$\alpha_{n+2}$|
         TRUE
-      g.forward |\dlt{1}|
-      TRUE
+        ...
+        if.
+        fl.eq 1
+        |$\alpha_{m}$|
+        TRUE|$\label{ln:TGB1}$|
     \end{ffcode}
 
-\subsubsection{Goto forward wrapped in an object}
-
-After the conversion described in section 3.1.1, the simplest call of forward jump will be presented as:
-
+    In terms of $\varphi$-calculus, lines \ref{ln:GB0}-\ref{ln:GB1} appears as:
     \begin{equation}
         \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+            & x (\alpha_1,\,\ldots\,,\,\alpha_n, \br
+            & \quad k.\ff{if}(\emph{g}.\ff{backward},\,\alpha_{n+1}),\br
+            & \quad \alpha_{n+2},\,\ldots\,, \alpha_m), \\
+        \end{split}
+    \end{equation}
+    and lines \ref{ln:TGB0}-\ref{ln:TGB1} as:
+    \begin{equation}
+        \begin{split}
+            & \ff{memory}(0)\,\mapsto\,flag, \\
+            & flag.\ff{eq}(0).\ff{while}(, \br
+            & \quad \ff{seq}(flag.\ff{write}(1), \br
+            & \quad \quad \leadsto x (\alpha_1,\,\ldots\,,\,\alpha_n, \br
+            & \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(0),\,\alpha_{n+1}), \br
+            & \quad \quad \quad \quad flag.\ff{eq}(1).\ff{if}(\alpha_{n+2}),\,\ldots\,, \br
+            & \quad \quad \quad \quad flag.\ff{eq}(1).\ff{if}(\alpha_{m})))) \\
         \end{split}
@@
 
-The transformation under consideration involves the following steps:
+    \begin{eotheorem}
+        Object \ff{goto} with an attribute \ff{backward} inside maps to semantically equivalent analog with mutable object, object \ff{while} and additional \ff{if} objects.
+    \end{eotheorem}
 
+    \begin{proof}
+        Let's introduce the following recursive function:
         \begin{equation}
             \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
+            (\forall x\,\in \emph{attr}(\emph{g})):\,\phi'(x)\,&\rightarrow\,(\mu'(x),\,\phi'(x'\,\neq\,x)) \\
+            &\rightarrow\,(\mu'(x),\,(\mu'(x'),\,\phi'(x''))) \\
+            &\ldots
+            \end{split}
+        \end{equation}
+        where:
+        \begin{equation}
+            \begin{split}
+                & \mu'(x)\,\rightarrow flag.\ff{eq}(1).\ff{if}(x) \\
+            \end{split}
+        \end{equation}
+        Then the Ex. \ref{GBex1} maps to Ex. \ref{GBex2} according to the logic of dataization of \ff{goto} object with an attribute \ff{backward}.
+        \begin{equation}\label{GBex1}
+        \begin{split}
+            & \ff{goto}(\llbracket\,\emph{g}\,\mapsto\,\varnothing,\br
+            & \quad \quad \quad \varphi\,\leadsto\,x(\ldots,\br
+            & \quad \quad \quad \quad k.\ff{if}(\emph{g}.\ff{backward},\,z),\br
+            & \quad \quad \quad \quad w,\,\ldots)\rrbracket) \\
+        \end{split}
+        \end{equation}
+        where \emph{x}, \emph{w} and \emph{z} defines any object in the language, \emph{k} defines an object, which when dataized equals to a data object \ff{TRUE}.
+        \begin{equation}\label{GBex2}
+        \begin{split}
+            & \ff{goto}(\llbracket\,\emph{g}\,\mapsto\,\varnothing,\br
+            & \quad \quad \quad \varphi\,\mapsto\,flag.\ff{eq}(0).\ff{while}(\br
+            & \quad \quad \quad \quad \ff{seq}(flag.\ff{write}(1), \leadsto x(\ldots,\br
+            & \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(0),\,z),\br
+            & \quad \quad \quad \quad \quad \phi'(w))))\rrbracket) \\
+        \end{split}
+        \end{equation}
+        When the jump condition equals to \ff{TRUE}, all objects that should not be executed when the \ff{backward} object is executed will not be executed because of the added \ff{if} objects and since all attributes of object $g$ are encapsulated in object \ff{while}, all attributes of the object $g$ will start executing again.
+    \end{proof}
+
+    \begin{corollary}
+        After transformation \emph{GB}, \ff{goto} is required to be removed to not violate parent-relations between objects.
+    \end{corollary}
+
+    \begin{proof}
+        Relying on Theorem \ref{delDef}, \ff{goto} object maps to object \ff{seq}.
+        But during transformation \emph{GB}, object \ff{seq} would be already created inside the object \ff{while}.
+        So all bound attributes of object \ff{goto} are already inside this object \ff{seq}, and \ff{goto} now just adds two extra levels of encapsulating.
+
+        Thus, by definition of the language, \ff{goto} object is required to be removed.
+        \begin{equation}
+            \begin{split}
+                & \ff{goto}(\llbracket \emph{g}\,\mapsto\,\varnothing,\,\varphi\,\mapsto\,flag.\ff{eq}(0).\ff{while}(\br
+                & \quad \quad \quad \ff{seq}(flag.\ff{write}(1),\,\alpha_1,\,\ldots\,,\,\alpha_n))\rrbracket) \\
+                & \downarrow \\
+                & flag.\ff{eq}(0).\ff{while}(\br
+                & \quad \ff{seq}(flag.\ff{write}(1),\,\alpha_1,\,\ldots\,,\,\alpha_n)) \\
+            \end{split}
+        \end{equation}
+    \end{proof}
+
+    \begin{equation*}
+        \dfrac
+        {\begin{split}
+             & \ff{goto}(\llbracket\,\emph{g}\,\mapsto\,\varnothing,\br
+             & \quad \quad \varphi\,\leadsto\,x(\ldots,\br
+             & \quad \quad \quad k.\ff{if}(\emph{g}.\ff{backward},\,z),\br
+             & \quad \quad \quad w,\,\ldots)\rrbracket) \\
+        \end{split}}
+        {\begin{split}
+             & \ff{memory}(0)\,\mapsto\,flag, \\
+             & flag.\ff{eq}.(0).\ff{while}(\br
+             & \quad \ff{seq}(flag.\ff{write}(1),\br
+             & \quad \quad \leadsto x(\ldots,\,k.\ff{if}(flag.\ff{write}(0),\,z),\,\phi'(w)))) \\
+        \end{split}}
+        \jrule{3}
+    \end{equation*}
+
+    Goto-backward works the same as DO-WHILE construct in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
+    So, all objects that are attributes of object \ff{goto} and below the jump itself should be executed once, and all subsequent times were executed depending on the condition of the loop.
+
+    Since there is no direct implementation this construct in EO, but there is an implementation of the \emph{while} generator, we can resort to a little trick.
+    To emulate it, we can create an object \emph{flag} that will be a condition for \ff{while}, whose dataization condition will depend on this value.
+    The initial value of \emph{flag} is such that the condition for the dataization of \ff{while} is fulfilled.
+    Then, in the "body" of the loop, it is required to change the value of the \emph{flag} to the opposite.
+    If the jump condition is \emph{TRUE}, value of \emph{flag} changes again to original so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop dataization condition will be fulfilled.
+
+    In order to ensure that when the jump condition is \emph{TRUE}, all other objects below the jump are not executed, it is required to encapsulate them in object \ff{if}, in which will check whether the jump condition was previously been fulfilled.
+
+    \subsection{Terminating the while-object} \label{TW}
+    As mentioned above, the behavior of the \ff{while} object is different from all other objects.
+
+    In order to realize the functionality of loops in EO, generators are provided. A generator is a routine that can be used to control the iteration behaviour of a loop.
+    The language currently provides a \emph{while} generator, on which other generators are implemented.
+
+    This transformation is an "addition" for \emph{GF}/\emph{GB} transformations since it allows to terminate the \ff{while} objects where it is required.
+    It modifies the condition of executing the \ff{while} object, adding a condition so that if this condition fails, the \emph{while}-loop will be terminated.
+    This could be done by creating the \ff{and} object, which implements logical \emph{AND} between attributes, and adding the desired condition and the condition of executing the \ff{while} object to its attributes.
+
+    Consider the following code:
+    \begin{ffcode}
+        while.|$\label{ln:TW0}$|
+        e
+        x
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$||$\label{ln:TW1}$|
+    \end{ffcode}
+    where $\alpha_i$ and $x$ are any objects in language, $e$ is any object, which when dataized equals to a data object \ff{TRUE}.
+
+    Suppose you want to add the following condition, which if will not be fulfilled, the loop should be terminated:
+    \begin{equation}
+        Z\,\neq\,0
+    \end{equation}
+    Applying transformation we get:
+    \begin{ffcode}
+        while.|$\label{ln:TTW0}$|
+        and.
+        eq. (Z 0)
+        e
+        x
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$||$\label{ln:TTW1}$|
+    \end{ffcode}
+
+    Describing transformation in terms of $\varphi$-calculus, lines \ref{ln:TW0}-\ref{ln:TW1} appears as:
+    \begin{equation}
+        \begin{split}
+            & \emph{e}.\ff{while}(\emph{x}(\alpha_1,\,\ldots\,,\,\alpha_n)) \\
+        \end{split}
+    \end{equation}
+    and lines \ref{ln:TTW0}-\ref{ln:TTW1} as:
+    \begin{equation}
+        \begin{split}
+            & \emph{e}.\ff{and}(Z.\ff{eq}(0)).\ff{while}(\emph{x}(\alpha_1,\,\ldots\,,\,\alpha_n))
         \end{split}
@@
 
+    \begin{eotheorem}
+        The dataization of object \ff{while} can be changed using additional objects that implement logical operators.
+        For example, to add a condition, which if not executed, the loop will terminate, it is required to use an object \ff{and}.
+    \end{eotheorem}
+
+    \begin{proof}
+        By definition of the language.
+        If there is any object \emph{Z}, which returns boolean value when executed and an object \ff{while}, which dataization should stop, when this value is \emph{FALSE}, it is required to use logical operator \emph{AND} with this object:
         \begin{equation}
             \begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \\
+                & while(and(Z,\,cond_{while}),\,\ldots)\\
             \end{split}
         \end{equation}
+        where the first argument is the condition for the dataization of the loop, the second argument is the "body" of the loop.
+    \end{proof}
 
-\begin{equation}
-\begin{split}
-& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
-\end{split}
-\end{equation}
+    This is used in \emph{GF}/\emph{GB} to abort the dataization of the \ff{while} object depending on the value of \ff{flag}:
+    \begin{equation*}
+        \dfrac
+        {\begin{split}
+             & e.\ff{while}(x(\alpha_1,\,\ldots\,,\,\alpha_n)) \\
+        \end{split}}
+        {\begin{split}
+             & e.\ff{and}(flag.\ff{eq}(\emph{val})).\ff{while}(x(\alpha_1,\,\ldots\,,\,\alpha_n))
+        \end{split}}
+        \jrule{4}
+    \end{equation*}
+    where \emph{val} is a value "0" or "1", depending on type of transformation - \emph{GF}/\emph{GB}.
 
-\begin{theorem}
-Expression 3 is semantically equivalent to expression 6:
-\end{theorem}
+    It is also possible to use other objects in the language that implement logical operators such as \ff{or}, \ff{not}, \ff{xor}, etc with object \ff{while}.
 
-\begin{equation} \nonumber
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
-\end{split}
-\end{equation}
+%%\subsection{Final algorithm}
+%%To sum up, we can now fully describe the algorithm itself.
+The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
+The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if needs to make a replacement in the while loop, containing a jump - use transformations 3.1.3 and 3.2.3 accordingly.
+If needs to make a replacement for a simple object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
 
-\hline
+    \section{Experimental Results}
 
-\begin{equation} \nonumber
-\begin{split}
-& \ff{if.}(\mu_1.not, \delta_2, \delta_1) \\
-\end{split}
-\end{equation}
+    \tbd{Here we explain how we implemented an automated tool for applying all described transformations to EO code.}
 
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.
+    \tbd{Then, we explain how we conducted experiments with this tool, modifying many EO programs and then running them to check whether they return the same results as original ones.}
 
-Consider the following code:
+    \section{Discussion}
 
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret0}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.forward |\dlt{1}|
-        |\dlt{2}|
-      |\sgm{3}| |$\label{ln:ret1}$|
-\end{ffcode}
+    Our software will simplify programs in EO language and make them more readable without using GOTO objects.
 
-Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as X.
+    In addition, our proof makes it possible to remove all GOTO constructs from programs.
 
-It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
-Otherwise statements following the goto-object itself are executed.
-So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic.
-
-Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e.
-when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change.
-This is required so that all objects following the if-statement that are attributes of the abstract object g are not executed.
-So, by wrapping each object following the jump condition and whose nesting is at least that of the g object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
-
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example: the \m{1} object must be inverted with (\m{1}).not; in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object seq, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
-
-Thus, after transformation, the program converts to:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{1}||$\label{ln:ret2}$|
-  |\sgm{2}|
-  if.
-    |\m{1}|.not
-    |\dlt{2}|
-    seq
-      |\dlt{1}|
-      flag.write 1
-  if.
-    (eq. (flag 1)).not
-    |\sgm{3}|
-    TRUE|$\label{ln:ret3}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as X'.
-
-Now let's look at an example program with nested objects containing goto forward:
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @
-      X
-      |\sgm{4}|
-\end{ffcode}
-
-Applying the transformation, we get:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}|
-  X'
-  if.
-    (eq. (flag 1)).not
-    |\sgm{4}|
-    TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward inside the while-loop}
-In order to realize the functionality of cycles in EO, generators are provided. A generator is a routine that can be used to control the iteration behaviour of a loop.
-
-The language currently provides a while generator, on which other generators are implemented.
-
-The simplest way to call goto forward inside a while-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-%%\begin{equation}
-%%\begin{split}
-%%& \ff{memory}(flag), \\
-%%& flag.\ff{write}(0), \\
-%%& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} %%\mapsto \varnothing, \\
-%%& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-%%& \quad \ff{if}.(\mu_1, %%\ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-%%& \quad )\rrbracket) \\
-%%\end{split}
-%%\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
-& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{and}.( \\
-& \quad \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{and}.( \\
-& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) )\\
-& \quad ) \\
-& ) \\
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 7 is semantically equivalent to expression 10:
-\end{theorem}
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{and}.( \\
-& \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) \\
-& \quad )\\
-& ) \\
-\end{split}
-\end{equation}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto forward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @ |$\label{ln:ret4}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.forward |\dlt{1}|
-            |\dlt{2}|
-          |\sgm{3}||$\label{ln:ret5}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as Y.
-
-In this case, goto-forward is used to exit the body of the while loop. However, every iteration of a while loop checks its own condition if it is true.
-
-Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false.
-We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
-So by combining the jump condition and the while loop condition do not violate the program logic.
-But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
-So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
-Otherwise, all statements that came after the jump in the while loop will be executed.
-So the combined condition of the while loop will look like: while (!flag AND condOfWhile).
-
-Thus, the transformation is:
-
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}||$\label{ln:ret6}$|
-  while.
-    and.
-      (eq. (flag 1)).not
-      |\m{0}|
-    |\sgm{1}|
-      |\sgm{2}|
-      if.
-        |\m{1}|.not
-        |\dlt{2}|
-        seq
-          |\dlt{1}|
-          flag.write 1
-      if.
-        (eq. (flag 1)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret7}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as Y'.
-
-We create an additional \emph{flag} object that will be equal to 1 when the jump condition is triggered and add this condition to the loop body; modify if-statement as described in Section 3.1.2, except that in the 'ELSE' branch we are changing the flag value because the jump condition has been met and the next iteration of the loop should not be executed.
-
-It is worth noting that if goto-forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
-So, every while that has a nesting less than the original nesting and more than the nesting of the abstract object \emph{g} will end without performing the next iteration.
-
-For example, a program with nested while-loops may look like this:
-\begin{ffcode}
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Y
-        |\sgm{4}|
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-memory > flag
-flag.write 0
-while.
-  and.
-    (eq. (flag 1)).not
-    |\m{9}|
-  |\sgm{9}|
-    Y'
-    if.
-      (eq. (flag 1)).not
-      |\sgm{4}|
-      TRUE
-\end{ffcode}
-
-\subsection{Backward jump}
-Goto backward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      stdout "Will be printed forever"
-      g.backward
-\end{ffcode}
-
-Same as with goto forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
-
-\subsubsection{Simple Backward} The simplest example of using goto-backward:
-
-\begin{ffcode}
-goto
-  [g]
-    g.backward > @
-\end{ffcode}
-
-which in terms of $\varphi$-calculus appears as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{backward} \rrbracket ) \\
-\end{split}
-\end{equation}
-
-This is identical to that discussed in Section 3.1.1. In cases where the jump is performed without condition, you need to add an additional if-statement, similar to the example in Section 3.1.1:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \\
-\end{split}
-\end{equation}
-
-Same code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.backward
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto backward wrapped in an object}
-After the conversion described in Section 3.2.1, the simplest call of backward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad ) \\
-& ) \\
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 13 is semantically equivalent to expression 16:
-\end{theorem}
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
-\end{split}
-\end{equation}
-
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad ) \\
-& ) \\
-\end{split}
-\end{equation}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}||$\label{ln:ret8}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.backward
-        |\dlt{1}|
-      |\sgm{3}||$\label{ln:ret9}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as W.
-
-Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition is TRUE.
-So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.
-
-Since there is no direct implementation of the do-while construct in EO, but there is an implementation of the while generator, we can resort to a little trick.
-
-To create a do-while emission, we can create a flag globally that will be a condition for our outer loop, whose execution condition will depend on this value.
-The initial value of this flag will be such that the condition for the execution of the added while loop is fulfilled.
-Then, in the body of the loop, we change the value of the flag to the opposite.
-When the jump condition is met, we again change the value of the flag so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop execution condition will be met.
-
-In order to ensure that when the jump condition is met, all other objects in the body of the newly added while loop are not executed, we wrap them in an additional if-statement, in which we will check whether the jump condition was previously executed.
-
-So, after transformation, the program converts to:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{1}||$\label{ln:ret10}$|
-      |\sgm{2}|
-      if.
-        (|\m{1}|).not
-        |\dlt{1}|
-        flag.write 0
-      if.
-        (eq. (flag 0)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret11}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as W'.
-
-Let's look at an example of a chain of nested objects containing a goto backward:
-
-\begin{ffcode}
-
-goto
-  [g]
-    |\sgm{0}|
-      W
-      |\sgm{4}|
-
-\end{ffcode}
-
-Applying transformation, we get:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}|
-      W'
-      if.
-        (eq. (flag 0)).not
-        |\sgm{4}|
-        TRUE
-
-\end{ffcode}
-
-\subsubsection{Goto backward inside the while-loop}
-Goto backward also can be called inside a while-loop body.
-
-The simplest way to call goto-backward inside a while-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{while}.(\mu_0, \\
-& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \quad \ff{while}.( \\
-& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad \quad ) \\
-& \quad \quad ) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{while}.( \\
-& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad ) \\
-& \quad ) \\
-&  ) \\
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 17 is semantically equivalent to expression 20:
-\end{theorem}
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) \\
-& \quad ) \\
-& \rrbracket) \\
-\end{split}
-\end{equation}
-
-\hline
-
-\begin{equation} \nonumber
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \\
-& \quad \ff{seq}(flag.\ff{write}(1), \\
-& \quad \quad \ff{while}.( \\
-& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ) \\
-& \quad \quad ) \\
-& \quad ) \\
-&  ) \\
-\end{split}
-\end{equation}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto backward.
-
-As discussed in section 3.1.3, the behavior of while is different from other objects in the language. Therefore, the transformation will be slightly different from that described in section 3.2.2.
-
-To understand that the logic is not broken, let's look at a special case of calling goto backward inside a while-loop.
-
-Let's consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @|$\label{ln:ret12}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.backward
-            |\dlt{1}|
-          |\sgm{3}||$\label{ln:ret13}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as Z.
-
-As described in section 3.2.2, the program runs from top to bottom until it meets goto forward and if the jump condition is met, the abstract object g is executed again.
-Similar to what was said in section 3.2.2, all objects inside the abstract object g should be copied at the jump point.
-
-The only difference, when the jump itself frames a while loop, is that when the jump condition is met, we need to interrupt the execution of all the internal while loops inside the new while loop, which we replaced the jump with.
-
-In order to interrupt the execution of each of the internal while loops, we can add an additional condition to each of them, whether the jump condition is met or not.
-This can be done with an additional flag object that will signal for each inner while loop whether the jump condition has been met.
-
-So, all internal while loops will not be executed further if flag shows that the jump condition is met and the logic of the program is not violated.
-For all other objects inside our new while loop, we should apply the transformation described in section 3.2.2.
-
-The transformation will look like this:
-
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}||$\label{ln:ret14}$|
-      while.
-        and.
-          (eq. (flag 0)).not
-          |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|.not
-            |\dlt{1}|
-            flag.write 0
-          if.
-            (eq. (flag 0)).not
-            |\sgm{3}|
-            TRUE|$\label{ln:ret15}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as Z'.
-
-Let's take a look on a program with nested while-loops:
-\begin{ffcode}
-
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Z
-        |\sgm{4}|
-
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    while.
-      and.
-        (eq. (flag 0)).not
-        |\m{9}|
-      |\sgm{9}|
-        Z'
-        if.
-          (eq. (flag 0)).not
-          |\sgm{4}|
-          TRUE
-
-\end{ffcode}
-
-\subsection{Final algorithm}
-To sum up, we can now fully describe the algorithm itself.
-The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
-The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if you need to make a replacement in the while loop, containing a jump - we use transformations 3.1.3 and 3.2.3 accordingly.
-If you need to make a replacement for a normal object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
+    \subsection{Necessity and sufficiency}
+    In the above transformations, only three objects are affected - \ff{if}, \ff{while} and mutable object \ff{memory}.
+    We only consider these objects, since all other objects that could implement the behavior of such constructs as \emph{DO-WHILE}, \emph{FOR}, \emph{REPEAT-UNTIL}, \emph{IF-THEN-ELSE} and others can be implemented using this objects.
 
     \section{Conclusion}
-As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the \emph{atom} object GOTO.
-We also showed that the program at the output will contain the same logic as the program at the input.
 
-\section{Discussion}
-Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, our proof makes it possible to remove all GOTO constructs from programs.
+    As a result of our research, we suggested 4 transformations that automatically converts an input program to a semantically equivalent analog, but without using the \emph{atom} object \ff{goto}.
+    We also proved that the program at the output will contain the same logic as the program at the input.
 
+    \printbibliography %Prints bibliography
 \end{document}

### 2022-10-10 paper/main.tex
Create main.tex

--- 2022-05-09 paper/main.tex
@@
-\documentclass[two column]{article}
+\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
+\settopmatter{printfolios=false,printccs=false,printacmref=false}
+\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false,backend=biber]{biblatex}
+\usepackage{debate}
+\usepackage[T2A,T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{graphicx}
+\usepackage[russian,english]{babel}
+  \renewcommand\ttdefault{cmtt}
+\usepackage{csquotes}
+\usepackage{ffcode}
+\usepackage{CJKutf8}
+\usepackage{paralist}
+\usepackage{cancel} % to enable \cancel command
+\usepackage{anyfontsize} % To get rid of font not found warnings
+\usepackage{tabularx} % for special tables
+\usepackage{amsmath}
+\usepackage{to-be-determined}
+\usepackage{href-ul}
+\usepackage{amsthm}
+\usepackage{cleveref}
+\usepackage{tcolorbox} % for algorithm
+  \tcbuselibrary{skins}
+\usepackage{fdsymbol} % for \mathbb
+\usepackage{algpseudocode} % for algorithms
+\usepackage{multicol} % for two cols in BNF
+\usepackage{pgffor} % to enable \foreach
+\usepackage{stmaryrd}
+\usepackage{mathtools}
+\newtheoremstyle{theorems}
+  {} % Space above
+  {} % Space below
+  {} % Theorem body font % (default is "\upshape")
+  {} % Indent amount
+  {\scshape} % Theorem head font % (default is \mdseries)
+  {.} % Punctuation after theorem head % default: no punctuation
+  { } % Space after theorem head
+  {} % Theorem head spec
+\theoremstyle{theorems}
+\newtheorem{eodefinition}{Definition}
+\newtheorem{eotheorem}{Theorem}
 
-\graphicspath{ {./images/} }
+\addbibresource{refs.bib}
 
-% Keywords command
-\providecommand{\keywords}[1]
-{
-  \small
-  \textbf{\textit{Keywords:}} #1
-}
+\newcommand\br{\\[-4pt]}
+\newcounter{rule}
+\renewcommand\therule{R\arabic{rule}}
+\newcommand\rr{\smalltriangleright{}}
+\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
+\newcommand{\jrule}[1]{%
+  \refstepcounter{rule}\label{rule:#1}%
+  \text{\textbf{\rrule{#1}}}}
 
-\title{\textbf{Elimination Of Jump Statements}}
-\author{\textbf{author}}
-\date{May 2022}
+\newcommand\sgm[1]{$\sigma_#1$}
+\newcommand\dlt[1]{$\delta_#1$}
+\newcommand\m[1]{$\mu_#1$}
+
+\title{Elimination Of Jump Objects}
+\author{author}
 
@@
 
-\begin{abstract}
-In this article we raise the problem of the so-called Jump Statements.
-Getting rid of the use of operators such as \textbf{goto}, \textbf{return}, \textbf{continue}, \textbf{break}, and \textbf{throw} in code is the task of most modern programming languages, as the program becomes unreadable, poorly optimized and the probability of fixing errors in such a program is extremely high.
-We are trying to answer the following research question: “Is it possible to completely get rid of the \textbf{GOTO} operator in the code?”
+\section{Introduction}
+The problem of eliminating Jump-like statements is known for both computer science and software engineering communities for a few decades and formulated by several scientists, some of which have suggested solutions for this problem.
 
-\end{abstract}
+The presence of jump statements in the source code makes it impossible to use the functional method of analysis.
+Other program analysis methods, including those based on symbolic execution techniques, will also benefit from the removal of jump statements, which are well-known obstacles to the precision of analysis, as explained by \citet{baldoni2018survey}.
 
-\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}
+There are an "object-flow" languages where the execution flow is controlled by object composition.
+An example of such a language is EO, which is based on $\varphi$-calculus introduced by \citet{bugayenko2021eolang} and formalized by \citet{kudasov2021}.
+This is a strictly object-oriented programming language in which any action is described by creating a new object, or decorating an existing one.
 
-\section{Introduction}
-The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of \textbf{goto} has disastrous effect and proposed to remove it from all programming languages, Even though a few years later Knuth showed a manner for structuring programs with the \textbf{goto} statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating \textbf{goto} statements.
+We are trying to answer the following research question: "Is it possible for any program, written in 'object-flow' language like EO and containing GOTO objects, to find a semantically equivalent program, but without GOTO objects?"
 
-Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called \textbf{GOTO}-patches, which are design techniques for eliminating \textbf{goto} statements; Erosa suggested an algorithm fir automatic elimination of \textbf{goto} statements in C; Zegour explained how \textbf{goto} elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing \textbf{goto} with IF-THEN-ELSE constructs; Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate \textbf{goto} during migration of legacy code to Java,
+\section{Related work}
+The problem was firstly formulated by \citet{dijkstra1968letters}: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages.
+Even though a few years later \citet{knuth1974structured} showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements \citep{arsac1977construction}.
 
-To our knowledge, there is still no software tool available, which would implement any of the suggested methods and enable automatic elimination of jump statements in programs.
-However, the main reason for finding a solution to this problem for us is the development of EOLANG, an experimental \(\varphi\)-calculus-based object-oriented programming language, which is used as an Intermediate Representation (IR) in Polystat, a new polyglot static analyzer.
-The method of program analysis used in Polystat is functional: we find bugs by 1) transforming source code to formulas of \(\varphi\)-calculus, 2) mapping them to \(\lambda\)-terms, and 3) reasoning on terms using their inverses.
+To solve the problem of eliminating Jump-like statements in other programming languages, the following works were published:
+\Citet{williams1985restructuring} created a tool for restructuring Pascal code;
+\Citet{jonsson1989next} was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements;
+\Citet{erosa1994taming} suggested an algorithm for automatic elimination of GOTO statements in~C;
+\Citet{zegour1994new} explained how GOTO elimination may work in any language, as long as it has jump statements and control structures;
+\Citet{morris1997goto} suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
+\Citet{ramshaw1988eliminating} proposed an algorithm for Pascal programs;
+\Citet{ganapathi2008shim} introduced optimization method for SHIM IR;
+\Citet{ceccato2008goto} suggested how to eliminate GOTO during migration of legacy code to Java.
 
-Such an analysis works well with statements which are easy to map to functions, for example if and switch.
-Jump statements, on the other hand, can't be easily mapped to functions, The presence of jump statements in the source code makes it impossible to use the functional method of analysis just explained.
+However, to our knowledge, there is still no method available, which enables automatic elimination of jump objects in programs written in such an object-flow languages.
 
-The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing \textbf{GOTO} objects into a semantically similar one, but without using them.
-We propose an algorithm that replaces code fragments using the GOTO object with similar fragments, but without using it.
-We claim that two algorithms are semantically equivalent if with the same set of input arguments they return the same results.
+\section{Definitions and designations}
+\begin{eodefinition}
+\emph{Dataization} in $\varphi$-calculus is a process of retrieving data from an object.
+The dataization of an object at the highest level of composition is similar to the execution of a program in other languages.
+\end{eodefinition}
+\begin{eodefinition} \emph{Nesting} of the current object determines the number of objects that encapsulate current object via abstraction, application, or decoration directly or through other objects.
+For example, here object $x$ has 3-rd level of nesting:
+\begin{ffcode}
+o1
+  o2
+  ...
+  o3
+    o4
+      x
+\end{ffcode}
+\end{eodefinition}
+\begin{eodefinition}
+\emph{Forwarding goto} denotes an object \ff{goto}, which encapsulate object \ff{forward} directly or through other objects:
+\begin{ffcode}
+goto
+  [o1]
+  |$\leadsto$|o1.forward o
+\end{ffcode}
+\end{eodefinition}
+\begin{eodefinition}
+\emph{Backwarding goto} denotes an object \ff{goto}, which encapsulate object \ff{backward} directly or through other objects:
+\begin{ffcode}
+goto
+  [o1]
+  |$\leadsto$|o1.backward
+\end{ffcode}
+\end{eodefinition}
 
-\section{Methods}
-In EOLANG, all jump statements are implemented as a single \textbf{GOTO}-object.
-The \textbf{GOTO}-object represents two types of jumps: \textit{forward jump} and \textit{backward jump}.
-Operators such as \textbf{break}, \textbf{return} and \textbf{goto forward} are implemented via \textit{forward jump}; \textbf{continue} and \textbf{goto backward} are implemented via \textit{backward jump}.
+Let's look at an EO code example that demonstrates the general syntax of the language:
+\begin{ffcode}
+memory 0 > x
+[] > app
+  [a b] > max
+    goto > @
+      [g]
+        if. > @
+          a.gt b
+          g.forward a
+          b
+  [x] > run
+    while. > @!
+      and.
+        x.lt 10
+        (x.mod 1).eq 0
+      [i]
+        x.write > @
+          (x.plus 1)
+\end{ffcode}
+In this code snippet, \ff{goto} is an \emph{atom}-object with attribute \ff{g}, which dataizes similar to \ff{seq} object;
+\ff{memory} is mutable object, which allows to reinitialize the bound object \ff{x} via \ff{.write} attribute;
+\ff{eq} is an object, which checks the equality of the objects passed to it;
+\ff{if} is an object, which implements behavior of branching;
+\ff{seq} is an object that sequentially dataizes all objects within it;
+\ff{while} is an object, implementing behavior of loops: its first bound attribute implements condition of loop dataization and second one implies "body" of loop;
+\ff{backward} and \ff{forward} are objects, which implements behaviour of jumps: first of them starts dataization of object \ff{g} again, while the second one returns the object passed to it as a parameter and terminates the dataization of the \ff{goto} object.
 
-For each of them, a semantically identical replacement is required so that the algorithm returns the same output with the same input parameters.
+In terms of $\varphi$-calculus, code snipped above will be presented as:
+\begin{equation}
+\begin{split}
+& app \mapsto \llbracket \br
+& \quad max(a, b) \mapsto \llbracket \br
+& \quad \quad \varphi \mapsto \ff{goto}(\llbracket\,g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \varphi \mapsto a.\ff{gt}(b).\ff{if}(g.\ff{forward}(a), b) \br
+& \quad \quad \rrbracket) \br
+& \quad \rrbracket \br
+& \quad run(x) \mapsto \llbracket \br
+& \quad \quad \varphi\ff{!} \mapsto x.\ff{lt}(10).\ff{and}(x.\ff{mod}(1).\ff{eq}(0)) \br
+& \quad \quad \quad \quad .\ff{while}(\llbracket i \mapsto \varnothing, \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \varphi \mapsto x.\ff{write}(x.\ff{plus}(1)) \br
+& \quad \quad \quad \quad \quad \rrbracket) \br
+& \quad \rrbracket \br
+& \rrbracket \\
+\end{split}
+\end{equation}
 
-\subsection{forward jump}
-\textbf{\textit{Goto forward}} is implemented in the language as:
-\begin{lstlisting}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
+\emph{Designations:}
+\begin{itemize}
+\item "$>$" is used to name objects, where on the left side of ">" is object itself and its name on the right side,
+\item "$[]$" is used to specify object parameters,
+\item "$@$" is used to denote the object being decorated,
+\item "$!$" is used to declare the object as a constant,
+\item "$\mapsto$" is used to denote an object, where free attributes stay in the parentheses on the left side and pairs, which represent bound attributes, stay on the right side, in double-square brackets,
+\item "$\leadsto$" denotes an arbitrary \emph{nesting} of an object, i.e. it can be encapsulated by other objects directly or via chain of objects.
+\end{itemize}
 
+\section{Sample}
+Let's consider the following example of C++ code, which uses goto:
+\begin{ffcode}
+int x = 0;|$\label{ln:cpp0}$|
+int func() {
+l1:
+  x = x + 1;
+  if (x < 10)
+    goto l1;
+  else
+    cout << "X >= 10!\n";
+  return x;
+}|$\label{ln:cpp1}$|
+\end{ffcode}
+
+We provide four independent transformations that replace \ff{goto} with a semantically equivalent analogue.
+After applying them, example above respresents as:
+\begin{ffcode}
+int fl_1 = 0;|$\label{ln:tcpp0}$|
+int fl_2 = -1;
+int x = 0;
+int func() {
+  fl_1 = 0;
+  fl_2 = -1;
+  do {
+    fl_1 = 1;
+    fl_2 = 0;
+    x = x + 1;
+    if (x < 10)
+      fl_1 = 0;
+    else
+      cout << "X >= 10!\n";
+    if (fl_1 == 1)
+      fl_2 = 1;
+  } while (fl_1 == 0 |$\vert$||$\vert$| fl_2 == -1);
+  if (fl_2 == 1)
+    return x;
+}|$\label{ln:tcpp1}$|
+\end{ffcode}
+
+Since we consider the problem of eliminating Jump-like statements on the example of a strictly object-oriented language EO, lines ~\ref{ln:cpp0}--~\ref{ln:cpp1} will be represented as:
+\begin{ffcode}
+memory 0 > x
+[] > func
+  goto > @
+    [g]
+      seq > @
+        x.write (x.plus 1)
+        if.
+          x.lt 10
+          g.backward
+          QQ.io.stdout "X >= 10!\n"
+        g.forward x
+\end{ffcode}
+
+While this code after transformations will appear as:
+\begin{ffcode}
+memory 0 > fl_1
+memory -1 > fl_2
+memory 0 > x
+[] > func
+  seq > @
+    fl_1.write 0
+    fl_2.write -1
+    while. > rem!
+      or.
+        fl_1.eq 0
+        fl_2.eq -1
+      [i]
+        seq > @
+          fl_1.write 1
+          fl_2.write 0
+          x.write (x.plus 1)
+          if.
+            x.lt 10
+            fl_1.write 0
+            QQ.io.stdout "X >= 10!\n"
+          if.
+            fl_1.eq 1
+            fl_2.write 1
+            TRUE
+    if.
+      fl_2.eq 1
+      x
+      rem
+\end{ffcode}
+
+Thus, the main purpose of our research is:
+\begin{enumerate}
+    \item To formulate inference rules for the transformations that we propose,
+    \item proof that these 4 transformations are necessary and sufficient to solve the problem under consideration,
+    \item suggest a program tool, which
+    enables automatic elimination of jump objects in programs written in EO.
+\end{enumerate}
+
+\section{Method}
+In this article, we will describe an algorithm that will convert an EO program in such a way that the output returns a semantically equivalent program, but without using the GOTO object.
+
+Some objects in EO may need to be platform specific and can’t be composed from other existing objects — they are called \emph{atoms}. 
+All jump statements are implemented as a
+single \emph{atom}-object \ff{goto}.
+The implementation of \ff{goto} in EO implies two types of jumps - forward jump and backward jump.
+It is required to cover all possible cases for both of them.
+
+%%The proposed algorithm is a series of transformations that are performed depending on the type of "jump".
+In total, we describe 4 types of transformations:
+\begin{inparaenum}[1)]
+\item \emph{Simple goto} (further $SG$),
+\item \emph{Goto to While} (further $GTW$) and
+\item \emph{Goto forward/backward} (further $GF$/$GB$).
+\end{inparaenum}
+Transformations are independent and not sequential, and each one is executed in its own particular case.
+For example, $SG$ and $GTW$ are only a "preparation" for the actual replacement of the jump by a semantically equivalent analog.
+First one is executed if there is no condition before the jump itself, while second one transforms object \ff{goto} into object \ff{while}.
+$GF$/$GB$ are the main transformations, as they contain the jump replacement itself and cover most possible cases of using forward and backward jumps.
+%%\emph{TW} is an "addition" for $GF$ and $GB$ transformations, since the behavior of the \ff{while} object in EO is different from all other objects and dataization of jump inside the loop requires separate consideration.
+
+%%Thus, the algorithm itself consists of the following steps: 
+%%\begin{inparaenum}[1)]
+%%\item Apply \emph{SF}/\emph{SB} transformation if necessary,
+%%\item Find all occurrences of forward/backward jump's calls,
+%%\item Apply $GF$/$GB$ transformations to all of them,
+%%\item If there is a \emph{while.} object that wraps the jump call, apply the \emph{WF}/\emph{WB} transformation.
+%%\end{inparaenum}
+
+The combination of all 4 transformations implies a complete algorithm for getting rid of the GOTO object, as they cover all possible cases of using GOTO and forward/backward jumps in the language.
+
+Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can encapsulate others.
+It should be noted that each object in the program has its own level of \emph{nesting} relative to other objects.
+
+We will also consider our transformations in the form of $\varphi$-calculus, on which EO is based.
+The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application and decoration.
+The calculus introduces a formal apparatus for manipulations with objects.
+
+\subsection{Simple goto} \label{SG}
+As mentioned above, this transformation is a "preparation" for $GF$/$GB$ which are make the replacement of object \ff{goto} itself.
+Since $GF$/$GB$ only consider the use of the \ff{forward}/\ff{backward} objects when they are directly encapsulated in the \ff{if} object(\cref{GF}/\cref{GB}), it is required to add an additional \ff{if} when it is absent before the jump.
+Thus, the transformation under consideration adds an additional fictitious condition $\emph{if (true)}$ if it necessary.
+
+Let's consider the case where the \ff{forward} is not directly encapsulated in the \ff{if} object:
+\begin{ffcode}
 goto
   [g]
-  seq
-   g.forward TRUE
-   stdout "Will never be printed"
-\end{lstlisting}
+   |$\leadsto$|g.forward y|$\label{ln:sf1}$|
+\end{ffcode}
+Here, $\alpha_{i}$, $x$ and $y$ defines any object in the language, excluding \ff{if}.
 
-In a program \textit{forward jump} can be used within the body of \textbf{if}-statement. In this case program will look like this:
+Applying the transformation, the example above maps to:
+\begin{ffcode}
+goto
+  [g]
+   |$\leadsto$|if.|$\label{ln:tsf0}$|
+      TRUE
+      g.forward y
+      TRUE|$\label{ln:tsf1}$|
+\end{ffcode}
 
-\includegraphics{forward1}
+Describing transformation in terms of $\varphi$-calculus, code at line ~\ref{ln:sf1} will be represented as:
+\begin{equation}
+\begin{split}
+& g.\ff{forward}( y ) \\
+\end{split}
+\end{equation}
+and code at lines ~\ref{ln:tsf0}---\ref{ln:tsf1} as:
+\begin{equation}
+\begin{split}
+& \ff{TRUE}.\ff{if}(g.\ff{forward}( y )) \\
+\end{split}
+\end{equation}
 
-Let's look at the following code on EOLANG:
-\begin{lstlisting}
-[x] > f
- memory > r
+\begin{eotheorem}
+Any object is semantically equivalent to the same object encapsulated in \ff{TRUE}.\ff{if}:
+\begin{equation*}
+\forall x (x \equiv \ff{TRUE}.\ff{if}(x)).
+\end{equation*}
+\end{eotheorem}
+
+\begin{proof}
+By definition of the language, if there is any object \emph{Z}, then the following equivalence follows:
+\begin{equation}
+Z \equiv if(true,\,Z,\,true),
+\end{equation}
+where first argument in \emph{if} is condition itself, second argument dataizes when condition is \emph{true} and third argument dataizes when condition is \emph{false}.
+\end{proof}
+
+\begin{equation*}
+\dfrac
+    {\begin{split}
+    & g.\ff{forward}( y ) \\
+    \end{split}}
+    {\begin{split}
+    & \ff{TRUE}.\ff{if}(g.\ff{forward}( y )) \\
+    \end{split}}
+    \jrule{1}
+\end{equation*}
+
+%%Note that in this example, \ff{forward} is simply an attribute of the abstract object \emph{g} and is dataized as soon as the queue reaches it.
+In such cases where there is an "unconditional" jump, first of all we transform it into "conditional" jump by encapsulating it in additional object \ff{if}---\emph{if (true)}.
+This will not violate the program logic, since added condition will always be \emph{TRUE} and "THEN" brunch of if-statement with object \ff{forward} will always be dataized.
+
+The same logic applies with the \ff{backward} object.
+
+\subsection{Goto forward} \label{GF}
+In this section, we discuss the transformation by replacing \emph{forwarding goto} with a semantic equivalent.
+Based on the concept of transformation, only cases in which \ff{forward} is directly encapsulated in the object \ff{if} are considered.
+
+The essence of the transformation is that we create an additional $flag$ object which will assign as "0" or "1" and will show whether the jump condition has been met.
+Instead of dataization \ff{forward}, we just reinitialize the $flag$ object with another value of data object \ff{Int}.
+Moreover, it is necessary to protect from dataization all objects inside \ff{goto} that follows the jump, since they should not be dataized when the jump condition is \ff{TRUE}.
+This requires encapsulating each such object with an additional object \ff{if} to check the equality $flag$ to an object "1"---i.e. whether the jump condition has been met before or not.
+
+Let's consider the following example:
+\begin{ffcode}
+goto|$\label{ln:of0}$|
+  [g]
+   |$\leadsto$|if.
+      k
+      g.forward y
+      |$\alpha_{n}$||$\label{ln:of1}$|
+\end{ffcode}
+Here, $\alpha_i$, $x$ and $y$ defines any object in the language; $k$ defines an object, which when dataized equals to a data object \ff{TRUE}/\ff{FALSE}.
+
+Applying the transformation, the example above maps
+to:
+\begin{ffcode}
+memory -1 > flag
+seq|$\label{ln:tof0}$|
+  goto > rem!
+    [g]
+     |$\leadsto$|if.
+        k
+        flag.write 1
+        |$\alpha_{n+1}$|
+  if.
+    flag.eq 1
+    y
+    rem|$\label{ln:tof1}$|
+\end{ffcode}
+
+In terms of $\varphi$-calculus lines ~\ref{ln:of0}--\ref{ln:of1} appears as:
+\begin{equation}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \varphi\,\mapsto\,(\,\leadsto k.\ff{if}(g.\ff{forward}(y), \alpha_{n+1}), \br
+& \quad \quad \quad \rrbracket) \\
+\end{split}
+\end{equation}
+Lines ~\ref{ln:tof0}--\ref{ln:tof1} will be represented as:
+\begin{equation}
+\begin{split}
+& \ff{seq}(\ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\,\leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+& \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(1),\,\alpha_{n+1}), \br
+& \quad \quad \quad \quad \quad \quad \quad \Theta(\alpha_{n+2}),\,\ldots\,,\,\Theta(\alpha_m)),\ldots\Theta(\alpha_{m+1})) \br
+& \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+& \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+\end{split}
+\end{equation}
+Here,
+\begin{equation}
+\Theta(X) \equiv flag.\ff{eq}(0).\ff{if}(X,\,\ff{TRUE})
+\end{equation}
+
+\begin{eotheorem}
+\emph{Forwarding goto} maps to semantically equivalent analog without \ff{forward} objects:
+\begin{equation*}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\,\varphi\,\leadsto\,x(\ldots,\,\leadsto g.\ff{forward}(y),\,\ldots)\rrbracket) \\
+& \downarrow \\
+& \ff{seq}( \br
+& \quad \quad \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \quad \quad \varphi\,\leadsto\,x(\ldots,\,\leadsto flag.\ff{write}(1),\,\ldots)\br
+& \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+& \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+\end{split}
+\end{equation*}
+\end{eotheorem}
+
+\begin{proof}
+Let's introduce the following recursive function:
+\begin{equation}
+\begin{split}
+(\forall x\,\in\,\emph{attr}(\emph{g})):\,\mu(x)\,&\rightarrow\,(\Theta(x),\,\mu(x'\,\neq\,x)) \\
+        &\rightarrow\,(\Theta(x),\,(\Theta(x'),\,\mu(x''))) \\
+        &\ldots
+\end{split}
+\end{equation}
+Here, $attr(X)$ denotes all attributes of an object $X$.
+
+Since the object \ff{goto} without \ff{forward} inside dataizes similar to the object \ff{seq}, then it follows that the following expression is valid:
+\begin{equation}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \varphi\,\leadsto\,x(\alpha_1,\,\ldots\,,\alpha_n)\rrbracket) \equiv \\
+& \ff{seq}(\ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \varphi\,\leadsto\,x(\alpha_1,\,\ldots\,,\alpha_n)\rrbracket)),\\
+\end{split}
+\end{equation}
+Here, $alpha_n$ defines any object in the language, excluding object \ff{forward}.
+
+When the outer \ff{seq} dataizes object \ff{goto} and the jump condition is \ff{TRUE}, it must return as a result of dataization the attribute of an object \ff{forward}.
+It can be done by the \ff{if} object, that follows object \ff{goto} and checks equality of $flag$ object to "1".
+
+According to the logic of dataization and definition of the language, both cases of dataization object \ff{forward} are considered via added \ff{if} objects.
+\debate[Mikhail]{Need a STRONG proof!}
+\end{proof}
+
+\begin{equation*}
+\dfrac
+    {\begin{split}
+    & \ff{goto}(\llbracket\,g\,\mapsto\,\varnothing,\br
+    & \quad \quad \quad \varphi\,\leadsto\,x(\ldots,\,k.\ff{if}(g.\ff{forward}(y),\,z),\br
+    & \quad \quad \quad w,\,\ldots)\rrbracket) \\
+    \end{split}}
+    {\begin{split}
+    & \ff{seq}(\ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+    & \quad \quad \quad \quad \quad \varphi\,\leadsto\,x(\ldots,\,k.\ff{if}(flag.\ff{write}(1),\,z), \br
+    & \quad \quad \quad \quad \quad \quad \quad \mu(w),\,\ldots\,) \br
+    & \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+    & \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+    \end{split}}
+    \jrule{2}
+\end{equation*}
+Here, $x$, $w$, $y$ and $z$ defines any object in the language, $k$ defines an object, which when dataized equals to a data object \ff{TRUE}.
+
+Indeed, depending on the jump condition, the same objects will be dataized as when dataization the \ff{forward} object itself.
+
+It is not difficult to notice that objects which goto-forward "jumps through" will be dataized if the condition in the if-statement is not equal to \ff{TRUE}.
+So before dataization such each object, that follows the jump, we can check condition of the jump.
+It can be done via mutable object \ff{memory} and additional \ff{if} objects.
+This is required so that all objects following the jump that are attributes of the abstract object $g$ straightforwardly or throw other objects are not dataized.
+So, by encapsulating each object, following the jump and whose \emph{nesting} is at least that of the $g$ object, in this additional \ff{if} object with a $flag$ check, we make sure that these objects will not be dataized when the jump condition is met.
+
+\subsection{Goto to While} \label{GTW}
+As mentioned above, all transformations are sequential.
+A necessary condition for the $GTW$ transformation is the absence of \ff{forward}/\ff{backward} objects inside the \ff{goto} object.
+In other words, this transformation is applied directly along with $GF$ and $GB$, since they imply the replacement of \ff{forward} and \ff{backward} objects.
+The essence of the transformation is that the object \ff{goto} maps to a control-flow object \ff{while}.
+
+Let's consider an example where inside the \ff{goto} object, the \ff{forward}/\ff{backward} objects are replaced with a semantic equivalent:
+\begin{ffcode}
+memory -1 > flag
+seq|$\label{ln:gtw0}$|
+  goto > rem!
+    [g]
+     |$\leadsto$|x
+        |$\alpha_1$|
+        ...
+        |$\alpha_n$|
+        if.
+          k
+          flag.write 1
+          |$\alpha_{n+1}$|
+        if.
+          flag.eq 0
+          |$\alpha_{n+2}$|
+          TRUE
+        ...
+        if.
+          flag.eq 0
+          |$\alpha_{m}$|
+          TRUE
+  if.
+    flag.eq 1
+    y
+    rem|$\label{ln:gtw1}$|
+\end{ffcode}
+Here, $\alpha_{i}$, $y$ and $x$ defines any object in the language, excluding \ff{forward}/\ff{backward};
+$k$ defines an object, which when dataized equals to a data object \ff{TRUE}/\ff{FALSE}.
+
+Applying the transformation, the example above maps
+to:
+\begin{ffcode}
+memory -1 > flag
+seq|$\label{ln:tgtw0}$|
+  while. > rem!
+    flag.eq -1
+    [i]
       seq > @
-  r.write 0
+        flag.write 0
+        |$\leadsto$|x
+          |$\alpha_1$|
+          ...
+          |$\alpha_n$|
+          if.
+            k
+            flag.write 1
+            |$\alpha_{n+1}$|
+          if.
+            flag.eq 0
+            |$\alpha_{n+2}$|
+            TRUE
+          ...
+          if.
+            flag.eq 0
+            |$\alpha_{m}$|
+            TRUE
+  if.
+    flag.eq 1
+    y
+    rem|$\label{ln:tgtw1}$|
+\end{ffcode}
+
+In terms of $\varphi$-calculus lines ~\ref{ln:gtw0}--\ref{ln:gtw1} appears as:
+\begin{equation}
+\begin{split}
+& \ff{seq}(\ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\,\leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+& \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(1),\,\alpha_{n+1}), \br
+& \quad \quad \quad \quad \quad \quad \quad \Theta(\alpha_{n+2}),\,\ldots\,,\,\Theta(\alpha_m))) \br
+& \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+& \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+\end{split}
+\end{equation}
+Here, $alpha_n$ defines any object in the language, excluding objects \ff{forward} and \ff{backward}.
+
+Lines ~\ref{ln:tgtw0}--\ref{ln:tgtw1} will be represented as:
+\begin{equation}
+\begin{split}
+& \ff{seq}(flag.\ff{eq}(-1).\ff{while}(\llbracket i\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\ff{seq}(flag.\ff{write}(0), \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \quad \leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(1),\,\alpha_{n+1}), \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \Theta(\alpha_{n+2}),\,\ldots\,,\,\Theta(\alpha_m)))) \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+& \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+\end{split}
+\end{equation}
+
+\begin{eotheorem}
+Object \ff{goto} maps to object \ff{while} if there are no \ff{forward}/\ff{backward} objects inside of it:
+\begin{equation*}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\,\varphi\,\leadsto\,x(\alpha_1,\,\ldots\,,\alpha_n)\rrbracket) \\
+& \downarrow \\
+& Z.\ff{while}(\llbracket i\,\mapsto\,\varnothing,\,\varphi\,\mapsto(\leadsto\,x(\alpha_1,\,\ldots\,,\alpha_n))\rrbracket) \\
+\end{split}
+\end{equation*}
+\end{eotheorem}
+Here, $Z$ is an object, which, when dataized, will be equal to a data object \ff{TRUE} only once.
+
+\begin{proof}
+By definition of the language, if there are no \ff{forward} and \ff{backward} objects inside object \ff{goto}, it dataizes similar to object \ff{seq}.
+It follows that the \ff{goto} object can be mapped to object \ff{while} with a condition, that will be equal to a data object \ff{TRUE} once, without violating the program logic.
+\end{proof}
+
+\begin{equation*}
+\dfrac
+    {\begin{split}
+    & \ff{seq}(\ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+    & \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\,\leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+    & \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(1),\,\alpha_{n+1}), \br
+    & \quad \quad \quad \quad \quad \quad \quad \Theta(\alpha_{n+2}),\,\ldots\,,\,\Theta(\alpha_m))) \br
+    & \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+    & \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+    \end{split}}
+    {\begin{split}
+    & \ff{seq}(flag.\ff{eq}(-1).\ff{while}(\llbracket i\,\mapsto\,\varnothing,\br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\ff{seq}(flag.\ff{write}(0), \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \quad \leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(1),\,\alpha_{n+1}), \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \Theta(\alpha_{n+2}),\,\ldots\,,\,\Theta(\alpha_m)))) \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+    & \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+    \end{split}}
+    \jrule{3}
+\end{equation*}
+
+The transformation does not violate the logic of the program, however, it gives the opportunity to dataize the "body" of the \ff{while} object loop again, if necessary.
+This trick is used in the $GB$ transformation.
+
+\subsection{Goto backward} \label{GB}
+Here we describe how to replace \ff{goto} object which has an object \ff{backward} inside to a semantic equivalent.
+Based on the concept of transformation, only cases in which attribute \ff{backward} is directly encapsulated in \ff{if} object are considered and this transformation is applied directly with $GTW$.
+
+When dataized, the \ff{backward} object aborts the current dataization of the \ff{goto} object and starts it again.
+In fact, such an implementation is equal to the DO-WHILE construct from other languages.
+The essence of the transformation is that we "emulate" the work of this construct.
+Since there is no such functionality in the language, we use the \ff{while} object and the mutable $flag$ object, from the result of dataization of which the loop will be dataized.
+
+At the beginning, we assign $flag$ object to a data object \ff{Int} equal to "0".
+The \ff{while} object condition checks that the \ff{flag} value is equal to "0" of data object \ff{Int}.
+Then in the "body" of the loop, we change $flag$ to "1".
+If the jump condition is \ff{TRUE}, then the \ff{flag} is required back to "0".
+This is necessary for the condition of the loop to be fulfilled and the next "iteration" begins.
+
+Same as at \ref{GF}, it is necessary to protect from dataization all objects inside \ff{goto} that follows the jump, since they should not be dataized when the jump condition is \ff{TRUE}.
+This requires encapsulating each such object in object \ff{if} to check $flag$---i.e. whether the jump condition was \ff{TRUE} before or not.
+
+Let's consider the following example of object \ff{goto} with \ff{backward} inside:
+\begin{ffcode}
+goto|$\label{ln:GB0}$|
+  [g]
+   |$\leadsto$|x
+      |$\alpha_1$|
+      ...
+      |$\alpha_n$|
+      if.
+        k
+        g.backward
+        |$\alpha_{n+1}$|
+      |$\alpha_{n+2}$|
+      ...
+      |$\alpha_{m}$||$\label{ln:GB1}$|
+\end{ffcode}
+Applying transformation $GB$ with $GTW$ this example maps to:
+\begin{ffcode}
+memory 0 > flag
+while.|$\label{ln:TGB0}$|
+  flag.eq 0
+  [i]
+    seq > @
+      flag.write 1
+       |$\leadsto$|if.
+          k
+          flag.write 0
+          |$\alpha_{n}$||$\label{ln:TGB1}$|
+\end{ffcode}
+
+In terms of $\varphi$-calculus, lines \ref{ln:GB0}--\ref{ln:GB1} appears as:
+\begin{equation}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \varphi\,\mapsto\,(\,\leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+& \quad \quad \quad \quad \quad k.\ff{if}(g.\ff{backward}, \alpha_{n+1}), \br
+& \quad \quad \quad \quad \quad \alpha_{n+2},\,\ldots\,,\,\alpha_m))\rrbracket) \\
+\end{split}
+\end{equation}
+Lines \ref{ln:TGB0}--\ref{ln:TGB1} as:
+\begin{equation}
+\begin{split}
+& \ff{seq}(flag.\ff{eq}(0).\ff{while}(\llbracket i\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\ff{seq}(flag.\ff{write}(1), \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \quad \leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(0),\,\alpha_{n+1}), \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \Upsilon(\alpha_{n+2}),\,\ldots\,,\,\Upsilon(\alpha_m)))) \br
+& \quad \quad \quad \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+& \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+\end{split}
+\end{equation}
+Here,
+\begin{equation}
+\Upsilon(X) \equiv flag.\ff{eq}(1).\ff{if}(X,\,\ff{TRUE})
+\end{equation}
+
+\begin{eotheorem}
+\emph{Backwarding goto} maps to semantically equivalent analog without \ff{backward} objects:
+\begin{equation*}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\,\varphi\,\leadsto\,x(\ldots,\,\leadsto g.\ff{backward},\,\ldots)\rrbracket) \\
+& \downarrow \\
+& \ff{seq}( \br
+& \quad \quad flag.\ff{eq}(0).\ff{while}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \quad \quad \quad \varphi\,\leadsto\,x(\ldots,\,\leadsto flag.\ff{write}(1),\,\ldots)\br
+& \quad \quad \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+& \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem)) \\
+\end{split}
+\end{equation*}
+\end{eotheorem}
+
+\begin{proof}
+Let's introduce the following recursive function:
+\begin{equation}
+\begin{split}
+(\forall x\,\in\,\emph{attr}(\emph{g})):\,\mu'(x)\,&\rightarrow\,(\Upsilon(x),\,\mu'(x'\,\neq\,x)) \\
+        &\rightarrow\,(\Upsilon(x),\,(\Upsilon(x'),\,\mu'(x''))) \\
+        &\ldots
+\end{split}
+\end{equation}
+
+Since this transformation is applied directly with $GTW$, then \ff{goto} object is already mapped to object \ff{while}.
+Based on logic of dataization of an object \\
+\ff{backward}, it is required to emulate dataization of object again.
+This can easily be done via the \ff{while} loop added to the $GTW$ transformation by changing its dataization condition:
+\begin{equation}
+\begin{split}
+& \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+& \quad \quad \varphi\,\leadsto\,x(\alpha_1,\,\ldots\,g.\ff{backward},\,\ldots\,,\alpha_n)\rrbracket) \equiv \\
+& \ff{seq}(flag.\ff{eq}(0).\ff{while}(\llbracket i\,\mapsto\,\varnothing,\br
+& \quad \quad \varphi\,\leadsto\,x(\alpha_1,\,\ldots\,,flag.\ff{write}(1),\,\ldots\,,\Upsilon(\alpha_n))\rrbracket)),\\
+\end{split}
+\end{equation}
+Here, $alpha_n$ defines any object in the language, excluding object \ff{forward}.
+
+Based on the $GF$ and $GTW$ transformations, this transformation is valid by the definition of the language.
+\debate[Mikhail]{Need a STRONG proof!}
+\end{proof}
+
+\begin{equation*}
+\dfrac
+    {\begin{split}
+    & \ff{goto}(\llbracket g\,\mapsto\,\varnothing,\br
+    & \quad \quad \quad \varphi\,\mapsto\,(\,\leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+    & \quad \quad \quad \quad \quad k.\ff{if}(g.\ff{backward},\,\alpha_{n+1}), \br
+    & \quad \quad \quad \quad \quad \Upsilon(\alpha_{n+2}),\,\ldots\,,\,\Upsilon(\alpha_m))) \br
+    & \quad \quad \quad \rrbracket)\mapsto rem\ff{!}, \br
+    & \quad \quad flag.\ff{eq}(1).\ff{if}(y,\,rem) \\
+    \end{split}}
+    {\begin{split}
+    & \ff{seq}(flag.\ff{eq}(0).\ff{while}(\llbracket i\,\mapsto\,\varnothing,\br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \varphi\,\mapsto\,(\ff{seq}(flag.\ff{write}(1), \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \quad \leadsto x(\alpha_1\,\ldots\,\alpha_n, \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad k.\ff{if}(flag.\ff{write}(0),\,\alpha_{n+1}), \br
+    & \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \Upsilon(\alpha_{n+2}),\,\ldots\,,\,\Upsilon(\alpha_m)))) \br
+    & \quad \quad \quad \quad  \quad \quad \quad \quad \quad \quad \rrbracket)) \\
+    \end{split}}
+    \jrule{4}
+\end{equation*}
+
+Goto-backward works the same as DO-WHILE construct in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
+So, all objects that inside of object \ff{goto} and below the jump itself should be executed once, and all subsequent times were executed depending on the condition of the loop.
+
+Since there is no direct implementation this construct in EO, but there is an implementation of the \emph{while} generator, we can resort to a little trick.
+To emulate it, we can create an object $flag$ that will be a condition for \ff{while}, whose dataization condition will depend on this object.
+We initialize $flag$ is such that the condition for the dataization of \ff{while} is fulfilled.
+Then, in the "body" of the loop, it is required to change $flag$ to the opposite.
+If the jump condition is \ff{TRUE}, $flag$ changes again to original so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop dataization condition will be \ff{TRUE}.
+
+In order to ensure that when the jump condition is \ff{TRUE}, all other objects below the jump are not executed, it is required to encapsulate them in object \ff{if}, in which will check whether the jump condition was previously been \ff{TRUE}.
+
+\section{Restrictions}
+Based on the concept of strictly object-oriented programming languages like EO, it is not possible to get rid of \ff{forward}/\ff{backward} objects in all cases.
+In such languages, some constructs are impossible to be exactly converted into code in functional languages such as Java, C++, Python, and others.
+
+Let's consider the following example of using \ff{goto} object:
+\begin{ffcode}
 goto
@@
     seq > @
-     if.
-      x.eq 0
-      g.forward
-      TRUE
-     r.write (42.div x)
-  r
-\end{lstlisting}
+      foo g
+[x] > foo
+  x.forward 25
+\end{ffcode}
+In this case, the object $g$, from which the \ff{forward}/\ff{backward} objects are called, is passed as an argument to another object, and the \ff{forward} object is already will be dataized inside object $foo$.
 
-In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within \textbf{if}-statement is TRUE.
-By inverting the condition in \textbf{if}-statement, you can write the code block between the \textbf{goto} call and its label into a separate \textbf{if}-statement:
-
-\includegraphics{forward2}
-
-Modified code:
-\begin{lstlisting}
-[x] > f
- memory > r
- seq > @
-  r.write 0
-  if.
-   not. (eq. (x 0))
-   r.write (42.div x)
-   TRUE
-  r
-\end{lstlisting}
-
-If the program encountered unconditional \textit{forward jump}, we need to transform it as \textbf{goto} with an additional condition: \textbf{if (true) goto forward}.
-Then the replacement occurs just as if the condition exists.
-
-\subsubsection{return}
-As mentioned above, return statement is also implemented via \textit{goto forward} object. Consider the following code:
-\begin{lstlisting}
-[a b] > max
- goto > @
-  [g]
-   seq > @
-    if.
-     a.greater b
-     g.forward a
-     TRUE
-    b
-\end{lstlisting}
-When using goto as \textit{return} statement, an additional attribute is added to the \textbf{goto}-object, similar to the return value of a procedure.
-In this case, it can easily be transformed into an \textbf{if}-statement as shown in the paragraph above:
-\begin{lstlisting}
-[a b] > max
- if.
-  a.greater b
-  a
-  TRUE
- b
-\end{lstlisting}
-
-\subsubsection{break}
-Break is a control-flow statement which could also be implemented using \textbf{goto forward}.
-Since the break statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
-In this case, we need to invert the \textit{if}-condition and add it to the condition of the loop with the logical operator \textit{AND}.
-After that, we easily get rid of the \textit{if}-condition itself.
-
-Let's look at the example:
-\begin{lstlisting}
-[]
- memory > i
- goto > @
-  [g]
-   seq > @
-    while.
-     i.less 10
-     seq
-      i.write (i.add 1)
-      if.
-       eq. (i.mod 5 0)
-       g.forward
-       TRUE
-\end{lstlisting}
-
-We invert \textit{condition} and add it to \textbf{while}-condition:
-\begin{lstlisting}
-[]
- memory > i
- seq > @
-  while.
-   and.
-    i.less 10
-    not. (eq. (i.mod 5 0))
-   seq
-    i.write (i.add 1)
-\end{lstlisting}
-
-\subsection{backward jumps}
-Backward jump is usually used similarly to a while loop and can be easily replaced by it (considering programs that are compiled and executed).
-Substitution will look like \textbf{do-while} construction.
-
-\includegraphics{backward1}
-
-Consider the following code:
-\begin{lstlisting}
-[] > f
- memory > i
- seq > @
-  i.write 1
+Similarly, if the \ff{forward}/\ff{backward} objects encapsulate third-party objects whose logic is not known to us, we cannot do the correct jump transformation:
+\begin{ffcode}
 goto
   [g]
-    seq > @
-     i.write (i.add 1)
-     if.
-      i.less 10
-      g.backward
-      TRUE
- stdout "Finished!"
-\end{lstlisting}
+    foreign_obj > @
+      QQ.io.stdout
+        "We don't know the logic\n"
+      g.forward TRUE
+\end{ffcode}
 
-In this case we could easily replace construction using \textbf{goto} with the \textbf{while}:
+Thus, we can guarantee transformations of \ff{forward} and \ff{backward} objects only if these objects encapsulate objects whose logic is known to us and these \ff{forward} and \ff{backward} objects are inside the \ff{goto} object.
 
-\includegraphics{backward2}
+\section{Toolkit}
+\tbd{TODO}
 
-\begin{lstlisting}
-[] > f
- memory > i
- seq > @
-  i.write 1
-  i.write (i.add 1)
-  while.
-   i.less 10
-   seq
-    i.write (i.add 1)
- stdout "Finished!"
-\end{lstlisting}
+Here we explain how we implemented an automated tool for applying all described transformations to EO code.
 
-\subsubsection{continue}
-Continue is also a control-flow statement, which occurs in loops and is implemented through the EO object \textbf{GOTO}.
-In order to replace it, we need to invert the \textit{if}-condition in the loop and all the statements that occur after \textbf{goto} are put in the \textit{if} body with the inverted condition.
+Then, we explain how we conducted experiments with this tool, modifying many EO programs and then running them to check whether they return the same results as original ones.
 
-Example of using \textit{continue} via \textbf{goto backward}:
-\begin{lstlisting}
-[]
- memory > i
- goto > @
-  [g]
-   seq > @
-    while.
-     i.less 10
-     seq
-      i.write (i.add 1)
-      if.
-       eq. (i.mod 5 0)
-       g.backward
-       TRUE
-      stdout "Not divisible by 5!\n"
-\end{lstlisting}
+\section{Discussion}
+\tbd{TODO}
 
-Replace the GOTO object with the described method:
-\begin{lstlisting}
-[]
- memory > i
- seq > @
- while.
-  i.less 10
-  seq
-   i.write (i.add 1)
-   if.
-    not. (eq. (i.mod 5 0))
-    stdout "Not divisible by 5!\n"
-    TRUE
-\end{lstlisting}
+Our software will simplify programs in EO language and make them more readable without using GOTO objects.
 
-\subsection{Complex cases}
-??? when forward and then backward jump
-??? and mb add throw ???
+\subsection{Necessity and sufficiency}
+\debate[Mikhail]{ Is it Necessary? We already have section Restrictions}
 
-\subsection{Final algorithm}
-Knowing how to replace a goto-forward statement and a goto-backward statement, we can present a final algorithm to get rid of all the GOTO objects in the EOlang code.
+In the above transformations, only three objects are affected - \ff{if}, \ff{while} and mutable object \ff{memory}.
+We only consider these objects, since all other objects that could implement the behavior of such constructs as \emph{DO-WHILE}, \emph{FOR}, \emph{REPEAT-UNTIL}, \emph{IF-THEN-ELSE} and others can be implemented using this objects.
 
+\section{Conclusion}
+\tbd{TODO}
+
+As a result of our research, we suggested 4 transformations that automatically converts an input program to a semantically equivalent analog, but without using the \emph{atom} object \ff{goto}.
+We also proved that the program at the output will contain the same logic as the program at the input.
+
+\printbibliography %Prints bibliography
 \end{document}

### 2022-10-12 paper/main.tex
Update main.tex

--- 2022-05-10 paper/main.tex
@@
-\documentclass[two column]{article}
+\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
+\settopmatter{printfolios=false,printccs=false,printacmref=false}
+\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false,backend=biber]{biblatex}
+\usepackage{debate}
+\usepackage[T2A,T1]{fontenc}
 \usepackage[utf8]{inputenc}
-\usepackage{listings}
-\usepackage{graphicx}
-\usepackage{xcolor}
+\usepackage[russian,english]{babel}
+  \renewcommand\ttdefault{cmtt}
+\usepackage{csquotes}
+\usepackage{ffcode}
+\usepackage{CJKutf8}
+\usepackage{paralist}
+\usepackage{cancel} % to enable \cancel command
+\usepackage{anyfontsize} % To get rid of font not found warnings
+\usepackage{tabularx} % for special tables
+\usepackage{amsmath}
+\usepackage{to-be-determined}
+\usepackage{href-ul}
+\usepackage{amsthm}
+\usepackage{cleveref}
+\usepackage{tcolorbox} % for algorithm
+  \tcbuselibrary{skins}
+\usepackage{fdsymbol} % for \mathbb
+\usepackage{algpseudocode} % for algorithms
+\usepackage{multicol} % for two cols in BNF
+\usepackage{pgffor} % to enable \foreach
+\usepackage{stmaryrd}
+\usepackage{mathtools}
+\newtheoremstyle{theorems}
+  {} % Space above
+  {} % Space below
+  {} % Theorem body font % (default is "\upshape")
+  {} % Indent amount
+  {\scshape} % Theorem head font % (default is \mdseries)
+  {.} % Punctuation after theorem head % default: no punctuation
+  { } % Space after theorem head
+  {} % Theorem head spec
+\theoremstyle{theorems}
+\newtheorem{eodefinition}{Definition}
+\newtheorem{eotheorem}{Theorem}
 
-\graphicspath{ {./images/} }
+\newcommand\nospell[1]{#1}
+\newcommand\br{\\[-4pt]}
+\newcommand\sgm[1]{$\sigma_#1$}
+\newcommand\dlt[1]{$\delta_#1$}
+\newcommand\m[1]{$\mu_#1$}
+\newcommand\figcap[1]{\caption{#1}\Description{#1}}
+\newcommand\phic{$\varphi$-calculus}
+\newcommand\eo{{\sffamily EO}}
+\newcommand\XMIR{{\sffamily XMIR}}
+\newcommand\lref[1]{the line no.~\ref{ln:#1}}
+\newcommand\lrefs[2]{the lines~\ref{ln:#1}--\ref{ln:#2}}
+\newcounter{rule}
+\renewcommand\therule{R\arabic{rule}}
+\newcommand\rr{\smalltriangleright{}}
+\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
+\newcommand{\jrule}[1]{%
+  \refstepcounter{rule}\label{rule:#1}%
+  \text{\textbf{\rrule{#1}}}}
+\newenvironment{algo}
+  {\newcommand\kw[1]{{\bfseries\sffamily ##1}}
+  \newcommand\tab{{\hspace*{1em}}}
+  \noindent}
+  {}
 
-% Keywords command
-\providecommand{\keywords}[1]
-{
-  \small
-  \textbf{\textit{Keywords:}} #1
-}
+\addbibresource{refs.bib}
 
-\definecolor{codegray}{rgb}{0.5,0.5,0.5}
+\title{Elimination Of Jump Objects}
+\author{author}
 
-\lstdefinestyle{mystyle}{
-  %%backgroundcolor=\color{backcolour}, commentstyle=\color{codegreen},
-  %%keywordstyle=\color{magenta},
-  numberstyle=\tiny\color{codegray},
-  %%stringstyle=\color{codepurple},
-  basicstyle=\ttfamily\footnotesize,
-  breakatwhitespace=false,         
-  breaklines=true,
-  frame=leftline,
-  captionpos=b,                    
-  keepspaces=true,                 
-  numbers=left,                    
-  numbersep=5pt,                  
-  showspaces=false,                
-  showstringspaces=false,
-  showtabs=false,                  
-  tabsize=2
-}
-
-\title{\textbf{Elimination Of Jump Statements}}
-\author{\textbf{author}}
-\date{May 2022}
-
-\lstset{style=mystyle}
 \begin{document}
@@
 
-\begin{abstract}
-In this article we raise the problem of the so-called Jump Statements.
-Getting rid of the use of operators such as \textbf{goto}, \textbf{return}, \textbf{continue}, \textbf{break}, and \textbf{throw} in code is the task of most modern programming languages, as the program becomes unreadable, poorly optimized and the probability of fixing errors in such a program is extremely high.
-We are trying to answer the following research question: “Is it possible to completely get rid of the \textbf{GOTO} operator in the code?”
+\section{Introduction}
+\label{sec:intro}
+\input{sections/intro}
 
-\end{abstract}
+\section{Related work}
+\label{sec:related}
+\input{sections/related}
 
-\keywords{Object-Oriented Programming, software engineering, algorithms, computer science}
+\section{Definitions and Designations}
+\label{sec:defs}
+\input{sections/defs}
 
-\section{Introduction}
-The problem is known both computer science and software engineering communities for a few decades already, while it was firstly formulated by Dijkstra in 1968: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages, Even though a few years later Knuth showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements.
+\section{Sample}
+\label{sec:sample}
+\input{sections/sample}
 
-Williams created a tool for restructuring Pascal code; Jonsson was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements; Erosa suggested an algorithm fir automatic elimination of GOTO statements in C; Zegour explained how GOTO elimination may work in any language, as long as it has jump statements and control structures; Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs; Ramshow proposed an algorithm for Pascal programs; Ganapathi introduced optimisation method for SHIM IR; Ceccato suggested how to eliminate GOTO during migration of legacy code to Java,
+\section{Method}
+\label{sec:method}
+\input{sections/method}
 
-To our knowledge, there is still no software tool available, which would implement any of the suggested methods and enable automatic elimination of jump statements in programs.
-However, the main reason for finding a solution to this problem for us is the development of EOLANG, an experimental \(\varphi\)-calculus-based object-oriented programming language, which is used as an Intermediate Representation (IR) in Polystat, a new polyglot static analyzer.
-The method of program analysis used in Polystat is functional: we find bugs by 1) transforming source code to formulas of \(\varphi\)-calculus, 2) mapping them to \(\lambda\)-terms, and 3) reasoning on terms using their inverses.
+\section{Restrictions}
+\label{sec:rest}
+\input{sections/restrictions}
 
-Such an analysis works well with statements which are easy to map to functions, for example if and switch.
-Jump statements, on the other hand, can't be easily mapped to functions, The presence of jump statements in the source code makes it impossible to use the functional method of analysis just explained.
+\section{Toolkit}
+\label{sec:tool}
+\input{sections/toolkit}
 
-The result of our research is an algorithm that allows converting a program in EO (Elementary Objects) language containing GOTO objects into a semantically similar one, but without using them.
-We propose an algorithm that replaces code fragments using the GOTO object with similar fragments, but without using it.
-We claim that two algorithms are semantically equivalent if with the same set of input arguments they return the same results.
+\section{Discussion}
+\label{sec:discus}
+\input{sections/discussion}
 
-\section{Methods}
-In EOLANG, all jump statements are implemented as a single \textbf{goto}-object.
-The \textbf{goto}-object represents two types of jumps: \textit{forward jump} and \textit{backward jump}.
-Operators such as \textbf{break}, \textbf{return} and \textbf{goto forward} are implemented via \textit{forward jump}; \textbf{continue} and \textbf{goto backward} are implemented via \textit{backward jump}.
+\section{Conclusion}
+\label{sec:conclusion}
+\input{sections/conclusion}
 
-We need to find a solution for both, how to replace them in different situations.
-For each of them, a semantically identical replacement is required so that the algorithm returns the same output with the same input parameters.
+\printbibliography
 
-\subsection{forward jump}
-\textbf{Goto forward} is implemented in EOLANG as:
-\begin{lstlisting}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
- [g]
-  seq
-   g.forward TRUE
-   stdout "Will never be printed"
-\end{lstlisting}
-
-In a program \textit{forward jump} can be used within the body of \textit{if-statement}.
-Structure of an algorithm can be represented by a scheme on Figure 1.
-Inside \textit{if-statement} are located some statements (stmt1), after that \textbf{goto-forward}, some other statements (stmt2) and the label of \textbf{goto}, where the program will continue to work if the condition in \textit{if-statement} was equal to \textit{TRUE}.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics{forward1}
-    \caption{\textit{forward jump} scheme}
-    \label{fig:my_label}
-\end{figure}
-
-Let's look at the following code:
-\begin{lstlisting}
-[x] > f
- memory > r
- seq > @
-  r.write 0
-  goto
-   [g]
-    seq > @
-     if.
-      x.eq 0
-      g.forward
-      TRUE
-     r.write (42.div x)
-  r
-\end{lstlisting}
-
-In this example we can see that the use of "forward jump" is unnecessary because it is called when condition within \textit{if-statement} is TRUE.
-By inverting the condition, you can write the code block between the \textbf{goto} call and its label into a separate \textit{if-statement}.
-This approach is illustrated in Figure 2.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics{forward2}
-    \caption{\textit{forward jump} elimination}
-    \label{fig:my_label}
-\end{figure}
-
-Modified code:
-\begin{lstlisting}
-[x] > f
- memory > r
- seq > @
-  r.write 0
-  if.
-   not. (eq. (x 0))
-   r.write (42.div x)
-   TRUE
-  r
-\end{lstlisting}
-
-If the program encountered unconditional \textit{forward jump}, we need to transform it as \textbf{goto} with an additional condition: \textbf{if (true) goto forward}.
-Then the replacement occurs just as if the condition exists.
-
-\subsubsection{return}
-As mentioned above, \textbf{return} statement is also implemented via \textit{goto forward} object. Consider the following code:
-\begin{lstlisting}
-[a b] > max
- goto > @
-  [g]
-   seq > @
-    if.
-     a.greater b
-     g.forward a
-     TRUE
-    b
-\end{lstlisting}
-When using goto as \textit{return} statement, an additional attribute is added to the \textbf{goto}-object, similar to the return value of a procedure.
-In this case, it can easily be transformed into an \textbf{if}-statement as shown in the paragraph above:
-\begin{lstlisting}
-[a b] > max
- if.
-  a.greater b
-  a
-  TRUE
- b
-\end{lstlisting}
-
-\subsubsection{break}
-\textit{Break} is a control-flow statement which could also be implemented using \textbf{goto forward}.
-Since the \textit{break} statement can only be found inside the generator (in EOlang Generator is a routine that can be used to control iteration behaviour of a loop) Its replacement is slightly different from the one presented in the paragraph above.
-In this case, we need to invert the \textit{if}-condition and add it to the condition of the loop with the logical operator \textit{AND}.
-After that, we easily get rid of the \textit{if}-condition itself.
-
-Let's look at the example:
-\begin{lstlisting}
-[]
- memory > i
- goto > @
-  [g]
-   seq > @
-    while.
-     i.less 10
-     seq
-      i.write (i.add 1)
-      if.
-       eq. (i.mod 5 0)
-       g.forward
-       TRUE
-\end{lstlisting}
-
-We invert \textit{condition} and add it to \textbf{while}-condition:
-\begin{lstlisting}
-[]
- memory > i
- seq > @
-  while.
-   and.
-    i.less 10
-    not. (eq. (i.mod 5 0))
-   seq
-    i.write (i.add 1)
-\end{lstlisting}
-
-Thus, at each iteration of the \textit{while} loop, the added condition will be checked, and as soon as it becomes \textit{FALSE}, the loop will be terminated because of the \textit{AND} statement.
-
-\subsection{backward jump}
-\textit{Backward jump} is usually used similarly to a while loop and can be easily replaced by it (considering programs that are compiled and executed).
-Substitution will look like \textbf{do-while} construction.
-
-\begin{figure}[h]
-    \centering
-    \includegraphics{backward1}
-    \caption{\textit{backward jump} scheme}
-    \label{fig:my_label}
-\end{figure}
-
-Consider the following code:
-\begin{lstlisting}
-[] > f
- memory > i
- seq > @
-  i.write 1
-  goto
-   [g]
-    seq > @
-     i.write (i.add 1)
-     if.
-      i.less 10
-      g.backward
-      TRUE
- stdout "Finished!"
-\end{lstlisting}
-
-\textbf{Goto backward} will work as long as the condition in if-statement is TRUE. In this case we could easily replace construction using \textbf{goto} with the \textit{while}:
-
-\begin{figure}[h]
-    \centering
-    \includegraphics{backward2}
-    \caption{\textit{backward jump} elimination}
-    \label{fig:my_label}
-\end{figure}
-
-\begin{lstlisting}
-[] > f
- memory > i
- seq > @
-  i.write 1
-  i.write (i.add 1)
-  while.
-   i.less 10
-   seq
-    i.write (i.add 1)
- stdout "Finished!"
-\end{lstlisting}
-
-The first iteration will always work, and all subsequent ones only as long as the condition in the loop is \textit{TRUE}.
-
-\subsubsection{continue}
-\textit{Continue} is also a control-flow statement, which occurs in loops and is implemented through the EO object \textbf{GOTO}.
-In order to replace it, we need to invert the \textit{if}-condition in the loop and all the statements that occur after \textbf{goto} are put in the \textit{if} body with the inverted condition.
-
-Example of using \textit{continue} via \textbf{goto backward}:
-\begin{lstlisting}
-[]
- memory > i
- goto > @
-  [g]
-   seq > @
-    while.
-     i.less 10
-     seq
-      i.write (i.add 1)
-      if.
-       eq. (i.mod 5 0)
-       g.backward
-       TRUE
-      stdout "Not divisible by 5!\n"
-\end{lstlisting}
-
-Since the \textbf{while} loop is an attribute of the \textbf{goto} object, \textit{if-condition} is executed a "jump up" that emulates the \textit{continue} statement.
-To get rid of this "jump" we should replace the GOTO object with the method described above:
-\begin{lstlisting}
-[]
- memory > i
- seq > @
- while.
-  i.less 10
-  seq
-   i.write (i.add 1)
-   if.
-    not. (eq. (i.mod 5 0))
-    stdout "Not divisible by 5!\n"
-    TRUE
-\end{lstlisting}
-
-\subsection{Complex cases}
-??? when forward and then backward jump
-??? and mb add throw ???
-
-\subsection{Final algorithm}
-Knowing how to replace a goto-forward statement and a goto-backward statement, we can present a final algorithm to get rid of all the GOTO objects in the EOlang code.
+\clearpage
 
 \end{document}
-\endinput

### 2022-10-12 paper/section/sample.tex
Create sample.tex

--- 2022-06-29 paper/skeleton.tex
@@
-\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
-\settopmatter{printfolios=false,printccs=false,printacmref=false}
-\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
-\usepackage{listings}
-\usepackage{graphicx}
-\usepackage{xcolor}
-
-\usepackage[T2A,T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[russian,english]{babel}
-  \renewcommand\ttdefault{cmtt}
-\usepackage{csquotes}
-\usepackage{ffcode}
-\usepackage{CJKutf8}
-\usepackage{paralist}
-\usepackage{cancel} % to enable \cancel command
-\usepackage{anyfontsize} % To get rid of font not found warnings
-\usepackage{tabularx} % for special tables
-\usepackage{amsmath}
-\usepackage{to-be-determined}
-\usepackage{href-ul}
-\usepackage{amsthm}
-\usepackage{tcolorbox} % for algorithm
-  \tcbuselibrary{skins}
-\usepackage{fdsymbol} % for \mathbb
-\usepackage{algpseudocode} % for algorithms
-\usepackage{multicol} % for two cols in BNF
-\usepackage{pgffor} % to enable \foreach
-\usepackage{stmaryrd}
-\usepackage{mathtools}
-
-\newcommand\br{\\[-4pt]}
-\newcounter{rule}
-\renewcommand\therule{R\arabic{rule}}
-\newcommand\rr{\smalltriangleright{}}
-\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
-\newcommand{\jrule}[1]{%
-  \refstepcounter{rule}\label{rule:#1}%
-  \text{\textbf{\rrule{#1}}}}
-
-\newtheorem{definition}{Definition}[section]
-
-\graphicspath{ {./images/} }
-
-\title{Elimination Of Jump Objects}
-\author{author}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-The problem is known both computer science and soft-
-ware engineering communities for a few decades and formulated by several scientists.
-
-Many of them have offered solutions to this problem. (Look at Related Work)
-
-The presence of jump statements in the source code makes it impossible to use the functional method of analysis.
-
-There are an "object-flow" languages where we can control flow through an objects.
-An example of such language is EO (Elementary Objects language).
-This is a strictly object-oriented programming language in which any action is described by creating a new object, or decorating an existing one.
-
-We are trying to answer the following research question: "Is it possible for any program, written on "object-flow" language like EO and containing GOTO objects to find a semantically equivalent program, but without using them?"
-
-\section{Related work}
-To solve the problem of eliminating Jump statements in other programming languages, the following works were published:
-Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
-Ramshow proposed an algorithm for Pascal programs;
-Ceccato suggested how to eliminate GOTO during migration of legacy code to Java.
-
-To our knowledge, there is still no method which enables automatic elimination of jump objects in programs written in such an object-flow languages.
-
-\section{Method}
-In this article, we will describe an algorithm that will convert an EO program in such a way that the output returns a semantically equivalent program, but without using the GOTO object.
-
-Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called \emph{atoms}. 
-So all jump statements are implemented as a
-single \emph{atom}-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
-
-Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can contain others.
-It should be noted that each object in the program has its own level of \emph{nesting} relative to other objects.
-
-\begin{definition} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
-\end{definition}
-
-The solution we propose contains two types of transformations - forward jump and backward jump.
-The algorithm itself consists in applying these transformations to replace both types of jumps.
-
-\vspace{5mm}
-
-\emph{Designations:}
-
-\begin{itemize}
-\item $\sigma$ - Denotes either an object, a chain of nested objects or the absence of an object.
-
-\item $\delta$ - Denotes a not-empty object or a chain of nested objects that return a not-NULL value when accessed.
-
-\item $\mu$ - Denotes an object or a chain of nested objects that return a boolean value (TRUE/FALSE) when executed.
-\end{itemize}
-
-\newcommand\sgm[1]{$\sigma_#1$}
-\newcommand\dlt[1]{$\delta_#1$}
-\newcommand\m[1]{$\mu_#1$}
-
-We will also look at our transformations in the form of $\varphi$-calculus, on which EO is based.
-The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application, and decoration.
-The calculus introduces a formal apparatus for manipulations with objects.
-
-$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
-
-\subsection{Forward jump}
-Goto forward in EO is implemented as:
-
+Let's consider the following example of C++ code, which uses goto:
 \begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      g.forward |\dlt{1}|
-      stdout "Will never be printed"
+int x = 0;|$\label{ln:cpp0}$|
+int func() {
+l1:
+  x = x + 1;
+  if (x < 10)
+    goto l1;
+  else
+    cout << "X >= 10!\n";
+  return x;
+}|$\label{ln:cpp1}$|
+\end{ffcode}
+Applying the method described by ~\citet{erosa1994taming}, we get the following code:
+\begin{ffcode}
+int goto_l1 = 0;|$\label{ln:tcpp0}$|
+int x = 0;
+int func() {
+  do {
+    goto_l1 = 0;
+    x = x + 1;
+    if (x < 10)
+      goto_l1 = 1;
+    else
+      cout << "X >= 10!\n";
+  } while (goto_l1);
+  return x;
+}|$\label{ln:tcpp1}$|
 \end{ffcode}
 
-It consists of the goto \emph{atom}-object, the abstract object \emph{g}, and the g.forward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.
-
-\subsubsection{Simple Forward}
-Consider the simplest example of using goto-forward:
-
+Since we consider the problem of eliminating Jump-like statements on the example of a strictly object-oriented language EO, \lrefs{cpp0}{cpp1} will be represented as:
 \begin{ffcode}
-goto
+memory 0 > x
+[] > func
+  goto > @
     [g]
-    g.forward |\dlt{1}| > @
+      seq > @
+        x.write (x.plus 1)
+        if.
+          x.lt 10
+          g.backward
+          QQ.io.stdout "X >= 10!\n"
+        g.forward x
+\end{ffcode}
+After the transformations that we propose, the code above is transformed into:
+\begin{ffcode}
+memory 0 > fl_1
+memory -1 > fl_2
+memory 0 > x
+[] > func
+  seq > @
+    fl_1.write 0
+    fl_2.write -1
+    while. > rem!
+      or.
+        fl_1.eq 0
+        fl_2.eq -1
+      [i]
+        seq > @
+          fl_1.write 1
+          fl_2.write 0
+          x.write (x.plus 1)
+          if.
+            x.lt 10
+            fl_1.write 0
+            QQ.io.stdout "X >= 10!\n"
+          if.
+            fl_1.eq 1
+            fl_2.write 1
+            TRUE
+    if.
+      fl_2.eq 1
+      x
+      rem
 \end{ffcode}
 
-In terms of $\varphi$-calculus, this code will appear as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{forward} (\delta_1) \rrbracket ) \\
-\end{split}
-\end{equation}
-
-Note that in this example, g.forward is simply an attribute of the abstract object \emph{g} and is executed as soon as the queue reaches it.
-Our transformation only considers the jumps that are made when a condition for it is fulfilled.
-In cases where there is unconditional jump, first of all we transform it into conditional jump by adding an additional if-statement - if (TRUE).
-This will not violate the program logic, because without the added if-statement, the jump would always be executed, and statements coming after this jump with a nesting not less that the nesting of the abstract object \emph{g} would never be executed:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing,\br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket)\\
-\end{split}
-\end{equation}
-
-Same example on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.forward |\dlt{1}|
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward wrapped in an object}
-
-After the conversion described in section 3.1.1, the simplest call of forward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \br
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \br
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1) \br
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 3 is semantically equivalent to expression 6:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket)
-    \end{matrix}}
-    {\ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1)}
-    \jrule{1}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
-
-Consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret0}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.forward |\dlt{1}|
-        |\dlt{2}|
-      |\sgm{3}| |$\label{ln:ret1}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as $X$.
-
-It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
-Otherwise statements following the goto-object itself are executed.
-So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic.
-
-Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e.
-when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change.
-This is required so that all objects following the if-statement that are attributes of the abstract object \emph{g} are not executed.
-So, by wrapping each object following the jump condition and whose nesting is at least that of the \emph{g} object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
-
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
-the \m{1} object must be inverted with (\m{1}).not;
-in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object \emph{seq}, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
-
-Thus, after transformation, the program converts to:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{1}||$\label{ln:ret2}$|
-  |\sgm{2}|
-  if.
-    |\m{1}|.not
-    |\dlt{2}|
-    seq
-      |\dlt{1}|
-      flag.write 1
-  if.
-    (eq. (flag 1)).not
-    |\sgm{3}|
-    TRUE|$\label{ln:ret3}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as $X'$.
-
-Now let's look at an example program with nested objects containing goto-forward:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @
-      X
-      |\sgm{4}|
-\end{ffcode}
-
-Applying the transformation, we get:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}|
-  X'
-  if.
-    (eq. (flag 1)).not
-    |\sgm{4}|
-    TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward inside the while-loop}
-In order to realize the functionality of cycles in EO, generators are provided. A generator is a routine that can be used to control the iteration behaviour of a loop.
-
-The language currently provides a \emph{while} generator, on which other generators are implemented.
-
-The simplest way to call goto-forward inside a \emph{while}-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-%%\begin{equation}
-%%\begin{split}
-%%& \ff{memory}(flag), \\
-%%& flag.\ff{write}(0), \\
-%%& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} %%\mapsto \varnothing, \\
-%%& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-%%& \quad \ff{if}.(\mu_1, %%\ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-%%& \quad )\rrbracket) \\
-%%\end{split}
-%%\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\br
-& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) )\rrbracket)\\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\br
-& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
-& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \rrbracket )\\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\br
-& \quad \ff{and}.(\mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 7 is semantically equivalent to expression 10:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2))\rrbracket) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{and}.( \\
-    & \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-    & \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-    & \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0))) \\
-    \end{matrix}}
-    \jrule{2}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @ |$\label{ln:ret4}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.forward |\dlt{1}|
-            |\dlt{2}|
-          |\sgm{3}||$\label{ln:ret5}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as $Y$.
-
-In this case, goto-forward is used to exit the body of the while loop. However, every iteration of a while loop checks its own condition if it is true.
-
-Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false.
-We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
-So by combining the jump condition and the while loop condition do not violate the program logic.
-But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
-So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
-
-If the jump condition is met, all objects inside the abstract object \emph{g} and following the goto-forward will not be executed.
-To do this, each of these objects should be wrapped in an additional if-statement, which will check the value of the flag, in other words - whether the jump condition is met or not.
-
-Otherwise, all statements that came after the jump in the while loop will be executed.
-So the combined condition of the while loop will be presented as: while (!flag AND condOfWhile).
-
-Thus, the transformation will be presented as:
-
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}||$\label{ln:ret6}$|
-  while.
-    and.
-      (eq. (flag 1)).not
-      |\m{0}|
-    |\sgm{1}|
-      |\sgm{2}|
-      if.
-        |\m{1}|.not
-        |\dlt{2}|
-        seq
-          |\dlt{1}|
-          flag.write 1
-      if.
-        (eq. (flag 1)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret7}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as $Y'$.
-
-We create an additional \emph{flag} object that will be equal to 1 when the jump condition is triggered and add this condition to the loop body; modify if-statement as described in Section 3.1.2, except that in the 'ELSE' branch we are changing the flag value because the jump condition has been met and the next iteration of the loop should not be executed.
-
-It is worth noting that if goto-forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
-So, every while that has a nesting less than the original nesting and more than the nesting of the abstract object \emph{g} will end without performing the next iteration.
-
-For example, a program with nested while-loops may look like this:
-\begin{ffcode}
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Y
-        |\sgm{4}|
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-memory > flag
-flag.write 0
-while.
-  and.
-    (eq. (flag 1)).not
-    |\m{9}|
-  |\sgm{9}|
-    Y'
-    if.
-      (eq. (flag 1)).not
-      |\sgm{4}|
-      TRUE
-\end{ffcode}
-
-\subsection{Backward jump}
-Goto backward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      stdout "Will be printed forever"
-      g.backward
-\end{ffcode}
-
-Same as with goto-forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
-
-\subsubsection{Simple Backward} The simplest example of using goto-backward:
-
-\begin{ffcode}
-goto
-  [g]
-    g.backward > @
-\end{ffcode}
-
-which in terms of $\varphi$-calculus appears as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{backward} \rrbracket ) \\
-\end{split}
-\end{equation}
-
-This is identical case to that discussed in Section 3.1.1. In cases where the jump is performed without condition, we need to add an additional if-statement, similar to the example in Section 3.1.1:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-Same code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.backward
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto backward wrapped in an object}
-After the conversion described in Section 3.2.1, the simplest call of backward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 13 is semantically equivalent to expression 16:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{eq}.(flag 0), \\
-    & \quad \ff{seq}(flag.\ff{write}(1), \\
-    & \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\
-    \end{matrix}}
-    \jrule{3}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret8}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.backward
-        |\dlt{1}|
-      |\sgm{3}||$\label{ln:ret9}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as $W$.
-
-Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
-So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.
-
-Since there is no direct implementation of the do-while construct in EO, but there is an implementation of the while generator, we can resort to a little trick.
-
-To create a do-while emission, we can create a flag globally that will be a condition for our outer loop, whose execution condition will depend on this value.
-The initial value of this flag will be such that the condition for the execution of the added while loop is fulfilled.
-Then, in the body of the loop, we change the value of the flag to the opposite.
-When the jump condition is met, we again change the value of the flag so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop execution condition will be met.
-
-In order to ensure that when the jump condition is met, all other objects in the body of the newly added while loop are not executed, we wrap them in an additional if-statement, in which we will check whether the jump condition was previously executed.
-
-So, after transformation, the program converts to:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{1}||$\label{ln:ret10}$|
-      |\sgm{2}|
-      if.
-        (|\m{1}|).not
-        |\dlt{1}|
-        flag.write 0
-      if.
-        (eq. (flag 0)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret11}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as $W'$.
-
-Let's look at an example of a chain of nested objects containing a goto-backward:
-
-\begin{ffcode}
-
-goto
-  [g]
-    |\sgm{0}| > @
-      W
-      |\sgm{4}|
-
-\end{ffcode}
-
-Applying transformation, we get:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}|
-      W'
-      if.
-        (eq. (flag 0)).not
-        |\sgm{4}|
-        TRUE
-
-\end{ffcode}
-
-\subsubsection{Goto backward inside the while-loop}
-Goto backward also can be called inside a while-loop body.
-
-The simplest way to call goto-backward inside a while-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2))\rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{while}.(\mu_0, \br
-& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 )))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \quad \ff{while}.( \br
-& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
-& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \ff{while}.( \br
-& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 17 is semantically equivalent to expression 20:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) ) \rrbracket ) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{eq}.(flag 0), \\
-    & \quad \ff{seq}(flag.\ff{write}(1), \\
-    & \quad \quad \ff{while}.( \\
-    & \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-    & \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\
-    \end{matrix}}
-    \jrule{4}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
-
-As discussed in section 3.1.3, the behavior of while is different from other objects in the language. Therefore, the transformation will be slightly different from that described in section 3.2.2.
-
-To understand that the logic is not broken, let's look at an abstract case of calling goto-backward inside a while-loop.
-
-Let's consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @|$\label{ln:ret12}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.backward
-            |\dlt{1}|
-          |\sgm{3}||$\label{ln:ret13}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as $Z$.
-
-Similar to the technique we used in section 3.1.3 with goto-forward inside the while loop, in this case, to avoid all subsequent iterations of the inside while loop, we combine its condition with the jump condition.
-As in Section 3.2.2, we create a global flag object, which will be an indicator of the execution of the jump condition.
-As soon as the jump condition is met, we change the flag value, and the next iteration of the inside while loop will fail during the check due to our added combined execution condition.
-
-The rest of the transformation looks identical to that described in section 3.2.2: create a global while loop with a check for moisture values, Invert the jump condition and if the goto-backward condition is met, change the value of the flag object.
-It is also necessary to wrap all objects that lie inside the abstract object \emph{g} in an additional if-statement with a check for the flag value, so that all of them are not fulfilled as soon as the jump condition is met.
-
-The transformation will be presented as:
-
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}||$\label{ln:ret14}$|
-      while.
-        and.
-          (eq. (flag 0)).not
-          |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|.not
-            |\dlt{1}|
-            flag.write 0
-          if.
-            (eq. (flag 0)).not
-            |\sgm{3}|
-            TRUE|$\label{ln:ret15}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as $Z'$.
-
-Let's take a look on a program with nested while-loops:
-\begin{ffcode}
-
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Z
-        |\sgm{4}|
-
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    while.
-      and.
-        (eq. (flag 0)).not
-        |\m{9}|
-      |\sgm{9}|
-        Z'
-        if.
-          (eq. (flag 0)).not
-          |\sgm{4}|
-          TRUE
-
-\end{ffcode}
-
-\subsection{Final algorithm}
-To sum up, we can now fully describe the algorithm itself.
-The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
-The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if needs to make a replacement in the while loop, containing a jump - use transformations 3.1.3 and 3.2.3 accordingly.
-If needs to make a replacement for a simple object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
-
-\section{Conclusion}
-As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the \emph{atom} object GOTO.
-We also showed that the program at the output will contain the same logic as the program at the input.
-
-\section{Discussion}
-Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, our proof makes it possible to remove all GOTO constructs from programs.
-
-\end{document}
-\endinput
+Thus, the main purpose of our research is:
+\begin{enumerate}
+    \item To formulate inference rules for the transformations that we propose,
+    \item proof that these 4 transformations are necessary and sufficient to solve the problem under consideration,
+    \item suggest a program tool, which
+    enables automatic elimination of jump objects in programs written in EO.
+\end{enumerate}

### 2022-10-12 paper/sections/related.tex

--- 2022-06-29 paper/skeleton.tex
@@
-\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
-\settopmatter{printfolios=false,printccs=false,printacmref=false}
-\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
-\usepackage{listings}
-\usepackage{graphicx}
-\usepackage{xcolor}
+The problem was firstly formulated by \citet{dijkstra1968letters}: he affirmed that the use of GOTO has disastrous effect and proposed to remove it from all programming languages.
+Even though a few years later \citet{knuth1974structured} showed a manner for structuring programs with the GOTO statement and argued that it could be a powerful tool if it is well used, researchers got interested in finding a way for restructuring programs and eliminating GOTO statements \citep{arsac1977construction}.
 
-\usepackage[T2A,T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[russian,english]{babel}
-  \renewcommand\ttdefault{cmtt}
-\usepackage{csquotes}
-\usepackage{ffcode}
-\usepackage{CJKutf8}
-\usepackage{paralist}
-\usepackage{cancel} % to enable \cancel command
-\usepackage{anyfontsize} % To get rid of font not found warnings
-\usepackage{tabularx} % for special tables
-\usepackage{amsmath}
-\usepackage{to-be-determined}
-\usepackage{href-ul}
-\usepackage{amsthm}
-\usepackage{tcolorbox} % for algorithm
-  \tcbuselibrary{skins}
-\usepackage{fdsymbol} % for \mathbb
-\usepackage{algpseudocode} % for algorithms
-\usepackage{multicol} % for two cols in BNF
-\usepackage{pgffor} % to enable \foreach
-\usepackage{stmaryrd}
-\usepackage{mathtools}
+To solve the problem of eliminating Jump-like statements in other programming languages, the following works were published:
+\Citet{williams1985restructuring} created a tool for restructuring Pascal code;
+\Citet{jonsson1989next} was one of the first who made a summary of so called GOTO-patches, which are design techniques for eliminating GOTO statements;
+\Citet{erosa1994taming} suggested an algorithm for automatic elimination of GOTO statements in~C;
+\Citet{zegour1994new} explained how GOTO elimination may work in any language, as long as it has jump statements and control structures;
+\Citet{morris1997goto} suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
+\Citet{ramshaw1988eliminating} proposed an algorithm for Pascal programs;
+\Citet{ganapathi2008shim} introduced optimization method for SHIM IR;
+\Citet{ceccato2008goto} suggested how to eliminate GOTO during migration of legacy code to Java.
 
-\newcommand\br{\\[-4pt]}
-\newcounter{rule}
-\renewcommand\therule{R\arabic{rule}}
-\newcommand\rr{\smalltriangleright{}}
-\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
-\newcommand{\jrule}[1]{%
-  \refstepcounter{rule}\label{rule:#1}%
-  \text{\textbf{\rrule{#1}}}}
-
-\newtheorem{definition}{Definition}[section]
-
-\graphicspath{ {./images/} }
-
-\title{Elimination Of Jump Objects}
-\author{author}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-The problem is known both computer science and soft-
-ware engineering communities for a few decades and formulated by several scientists.
-
-Many of them have offered solutions to this problem. (Look at Related Work)
-
-The presence of jump statements in the source code makes it impossible to use the functional method of analysis.
-
-There are an "object-flow" languages where we can control flow through an objects.
-An example of such language is EO (Elementary Objects language).
-This is a strictly object-oriented programming language in which any action is described by creating a new object, or decorating an existing one.
-
-We are trying to answer the following research question: "Is it possible for any program, written on "object-flow" language like EO and containing GOTO objects to find a semantically equivalent program, but without using them?"
-
-\section{Related work}
-To solve the problem of eliminating Jump statements in other programming languages, the following works were published:
-Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
-Ramshow proposed an algorithm for Pascal programs;
-Ceccato suggested how to eliminate GOTO during migration of legacy code to Java.
-
-To our knowledge, there is still no method which enables automatic elimination of jump objects in programs written in such an object-flow languages.
-
-\section{Method}
-In this article, we will describe an algorithm that will convert an EO program in such a way that the output returns a semantically equivalent program, but without using the GOTO object.
-
-Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called \emph{atoms}. 
-So all jump statements are implemented as a
-single \emph{atom}-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
-
-Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can contain others.
-It should be noted that each object in the program has its own level of \emph{nesting} relative to other objects.
-
-\begin{definition} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
-\end{definition}
-
-The solution we propose contains two types of transformations - forward jump and backward jump.
-The algorithm itself consists in applying these transformations to replace both types of jumps.
-
-\vspace{5mm}
-
-\emph{Designations:}
-
-\begin{itemize}
-\item $\sigma$ - Denotes either an object, a chain of nested objects or the absence of an object.
-
-\item $\delta$ - Denotes a not-empty object or a chain of nested objects that return a not-NULL value when accessed.
-
-\item $\mu$ - Denotes an object or a chain of nested objects that return a boolean value (TRUE/FALSE) when executed.
-\end{itemize}
-
-\newcommand\sgm[1]{$\sigma_#1$}
-\newcommand\dlt[1]{$\delta_#1$}
-\newcommand\m[1]{$\mu_#1$}
-
-We will also look at our transformations in the form of $\varphi$-calculus, on which EO is based.
-The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application, and decoration.
-The calculus introduces a formal apparatus for manipulations with objects.
-
-$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
-
-\subsection{Forward jump}
-Goto forward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      g.forward |\dlt{1}|
-      stdout "Will never be printed"
-\end{ffcode}
-
-It consists of the goto \emph{atom}-object, the abstract object \emph{g}, and the g.forward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.
-
-\subsubsection{Simple Forward}
-Consider the simplest example of using goto-forward:
-
-\begin{ffcode}
-goto
-  [g]
-    g.forward |\dlt{1}| > @
-\end{ffcode}
-
-In terms of $\varphi$-calculus, this code will appear as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{forward} (\delta_1) \rrbracket ) \\
-\end{split}
-\end{equation}
-
-Note that in this example, g.forward is simply an attribute of the abstract object \emph{g} and is executed as soon as the queue reaches it.
-Our transformation only considers the jumps that are made when a condition for it is fulfilled.
-In cases where there is unconditional jump, first of all we transform it into conditional jump by adding an additional if-statement - if (TRUE).
-This will not violate the program logic, because without the added if-statement, the jump would always be executed, and statements coming after this jump with a nesting not less that the nesting of the abstract object \emph{g} would never be executed:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing,\br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket)\\
-\end{split}
-\end{equation}
-
-Same example on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.forward |\dlt{1}|
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward wrapped in an object}
-
-After the conversion described in section 3.1.1, the simplest call of forward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \br
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \br
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1) \br
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 3 is semantically equivalent to expression 6:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket)
-    \end{matrix}}
-    {\ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1)}
-    \jrule{1}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
-
-Consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret0}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.forward |\dlt{1}|
-        |\dlt{2}|
-      |\sgm{3}| |$\label{ln:ret1}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as $X$.
-
-It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
-Otherwise statements following the goto-object itself are executed.
-So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic.
-
-Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e.
-when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change.
-This is required so that all objects following the if-statement that are attributes of the abstract object \emph{g} are not executed.
-So, by wrapping each object following the jump condition and whose nesting is at least that of the \emph{g} object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
-
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
-the \m{1} object must be inverted with (\m{1}).not;
-in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object \emph{seq}, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
-
-Thus, after transformation, the program converts to:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{1}||$\label{ln:ret2}$|
-  |\sgm{2}|
-  if.
-    |\m{1}|.not
-    |\dlt{2}|
-    seq
-      |\dlt{1}|
-      flag.write 1
-  if.
-    (eq. (flag 1)).not
-    |\sgm{3}|
-    TRUE|$\label{ln:ret3}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as $X'$.
-
-Now let's look at an example program with nested objects containing goto-forward:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @
-      X
-      |\sgm{4}|
-\end{ffcode}
-
-Applying the transformation, we get:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}|
-  X'
-  if.
-    (eq. (flag 1)).not
-    |\sgm{4}|
-    TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward inside the while-loop}
-In order to realize the functionality of cycles in EO, generators are provided. A generator is a routine that can be used to control the iteration behaviour of a loop.
-
-The language currently provides a \emph{while} generator, on which other generators are implemented.
-
-The simplest way to call goto-forward inside a \emph{while}-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-%%\begin{equation}
-%%\begin{split}
-%%& \ff{memory}(flag), \\
-%%& flag.\ff{write}(0), \\
-%%& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} %%\mapsto \varnothing, \\
-%%& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-%%& \quad \ff{if}.(\mu_1, %%\ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-%%& \quad )\rrbracket) \\
-%%\end{split}
-%%\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\br
-& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) )\rrbracket)\\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\br
-& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
-& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \rrbracket )\\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\br
-& \quad \ff{and}.(\mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 7 is semantically equivalent to expression 10:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2))\rrbracket) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{and}.( \\
-    & \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-    & \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-    & \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0))) \\
-    \end{matrix}}
-    \jrule{2}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @ |$\label{ln:ret4}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.forward |\dlt{1}|
-            |\dlt{2}|
-          |\sgm{3}||$\label{ln:ret5}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as $Y$.
-
-In this case, goto-forward is used to exit the body of the while loop. However, every iteration of a while loop checks its own condition if it is true.
-
-Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false.
-We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
-So by combining the jump condition and the while loop condition do not violate the program logic.
-But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
-So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
-
-If the jump condition is met, all objects inside the abstract object \emph{g} and following the goto-forward will not be executed.
-To do this, each of these objects should be wrapped in an additional if-statement, which will check the value of the flag, in other words - whether the jump condition is met or not.
-
-Otherwise, all statements that came after the jump in the while loop will be executed.
-So the combined condition of the while loop will be presented as: while (!flag AND condOfWhile).
-
-Thus, the transformation will be presented as:
-
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}||$\label{ln:ret6}$|
-  while.
-    and.
-      (eq. (flag 1)).not
-      |\m{0}|
-    |\sgm{1}|
-      |\sgm{2}|
-      if.
-        |\m{1}|.not
-        |\dlt{2}|
-        seq
-          |\dlt{1}|
-          flag.write 1
-      if.
-        (eq. (flag 1)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret7}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as $Y'$.
-
-We create an additional \emph{flag} object that will be equal to 1 when the jump condition is triggered and add this condition to the loop body; modify if-statement as described in Section 3.1.2, except that in the 'ELSE' branch we are changing the flag value because the jump condition has been met and the next iteration of the loop should not be executed.
-
-It is worth noting that if goto-forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
-So, every while that has a nesting less than the original nesting and more than the nesting of the abstract object \emph{g} will end without performing the next iteration.
-
-For example, a program with nested while-loops may look like this:
-\begin{ffcode}
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Y
-        |\sgm{4}|
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-memory > flag
-flag.write 0
-while.
-  and.
-    (eq. (flag 1)).not
-    |\m{9}|
-  |\sgm{9}|
-    Y'
-    if.
-      (eq. (flag 1)).not
-      |\sgm{4}|
-      TRUE
-\end{ffcode}
-
-\subsection{Backward jump}
-Goto backward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      stdout "Will be printed forever"
-      g.backward
-\end{ffcode}
-
-Same as with goto-forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
-
-\subsubsection{Simple Backward} The simplest example of using goto-backward:
-
-\begin{ffcode}
-goto
-  [g]
-    g.backward > @
-\end{ffcode}
-
-which in terms of $\varphi$-calculus appears as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{backward} \rrbracket ) \\
-\end{split}
-\end{equation}
-
-This is identical case to that discussed in Section 3.1.1. In cases where the jump is performed without condition, we need to add an additional if-statement, similar to the example in Section 3.1.1:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-Same code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.backward
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto backward wrapped in an object}
-After the conversion described in Section 3.2.1, the simplest call of backward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 13 is semantically equivalent to expression 16:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{eq}.(flag 0), \\
-    & \quad \ff{seq}(flag.\ff{write}(1), \\
-    & \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\
-    \end{matrix}}
-    \jrule{3}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret8}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.backward
-        |\dlt{1}|
-      |\sgm{3}||$\label{ln:ret9}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as $W$.
-
-Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
-So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.
-
-Since there is no direct implementation of the do-while construct in EO, but there is an implementation of the while generator, we can resort to a little trick.
-
-To create a do-while emission, we can create a flag globally that will be a condition for our outer loop, whose execution condition will depend on this value.
-The initial value of this flag will be such that the condition for the execution of the added while loop is fulfilled.
-Then, in the body of the loop, we change the value of the flag to the opposite.
-When the jump condition is met, we again change the value of the flag so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop execution condition will be met.
-
-In order to ensure that when the jump condition is met, all other objects in the body of the newly added while loop are not executed, we wrap them in an additional if-statement, in which we will check whether the jump condition was previously executed.
-
-So, after transformation, the program converts to:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{1}||$\label{ln:ret10}$|
-      |\sgm{2}|
-      if.
-        (|\m{1}|).not
-        |\dlt{1}|
-        flag.write 0
-      if.
-        (eq. (flag 0)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret11}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as $W'$.
-
-Let's look at an example of a chain of nested objects containing a goto-backward:
-
-\begin{ffcode}
-
-goto
-  [g]
-    |\sgm{0}| > @
-      W
-      |\sgm{4}|
-
-\end{ffcode}
-
-Applying transformation, we get:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}|
-      W'
-      if.
-        (eq. (flag 0)).not
-        |\sgm{4}|
-        TRUE
-
-\end{ffcode}
-
-\subsubsection{Goto backward inside the while-loop}
-Goto backward also can be called inside a while-loop body.
-
-The simplest way to call goto-backward inside a while-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2))\rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{while}.(\mu_0, \br
-& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 )))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \quad \ff{while}.( \br
-& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
-& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \ff{while}.( \br
-& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 17 is semantically equivalent to expression 20:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) ) \rrbracket ) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{eq}.(flag 0), \\
-    & \quad \ff{seq}(flag.\ff{write}(1), \\
-    & \quad \quad \ff{while}.( \\
-    & \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-    & \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\
-    \end{matrix}}
-    \jrule{4}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
-
-As discussed in section 3.1.3, the behavior of while is different from other objects in the language. Therefore, the transformation will be slightly different from that described in section 3.2.2.
-
-To understand that the logic is not broken, let's look at an abstract case of calling goto-backward inside a while-loop.
-
-Let's consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @|$\label{ln:ret12}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.backward
-            |\dlt{1}|
-          |\sgm{3}||$\label{ln:ret13}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as $Z$.
-
-Similar to the technique we used in section 3.1.3 with goto-forward inside the while loop, in this case, to avoid all subsequent iterations of the inside while loop, we combine its condition with the jump condition.
-As in Section 3.2.2, we create a global flag object, which will be an indicator of the execution of the jump condition.
-As soon as the jump condition is met, we change the flag value, and the next iteration of the inside while loop will fail during the check due to our added combined execution condition.
-
-The rest of the transformation looks identical to that described in section 3.2.2: create a global while loop with a check for moisture values, Invert the jump condition and if the goto-backward condition is met, change the value of the flag object.
-It is also necessary to wrap all objects that lie inside the abstract object \emph{g} in an additional if-statement with a check for the flag value, so that all of them are not fulfilled as soon as the jump condition is met.
-
-The transformation will be presented as:
-
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}||$\label{ln:ret14}$|
-      while.
-        and.
-          (eq. (flag 0)).not
-          |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|.not
-            |\dlt{1}|
-            flag.write 0
-          if.
-            (eq. (flag 0)).not
-            |\sgm{3}|
-            TRUE|$\label{ln:ret15}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as $Z'$.
-
-Let's take a look on a program with nested while-loops:
-\begin{ffcode}
-
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Z
-        |\sgm{4}|
-
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    while.
-      and.
-        (eq. (flag 0)).not
-        |\m{9}|
-      |\sgm{9}|
-        Z'
-        if.
-          (eq. (flag 0)).not
-          |\sgm{4}|
-          TRUE
-
-\end{ffcode}
-
-\subsection{Final algorithm}
-To sum up, we can now fully describe the algorithm itself.
-The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
-The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if needs to make a replacement in the while loop, containing a jump - use transformations 3.1.3 and 3.2.3 accordingly.
-If needs to make a replacement for a simple object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
-
-\section{Conclusion}
-As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the \emph{atom} object GOTO.
-We also showed that the program at the output will contain the same logic as the program at the input.
-
-\section{Discussion}
-Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, our proof makes it possible to remove all GOTO constructs from programs.
-
-\end{document}
-\endinput
+However, to our knowledge, there is still no method available, which enables automatic elimination of jump objects in programs written in such an object-flow languages.

### 2022-10-12 paper/sections/restrictions.tex

Based on the concept of strictly object-oriented programming languages like EO, it is not possible to get rid of \ff{forward}/\ff{backward} objects in all cases.
In such languages, some constructs are impossible to be exactly converted into code in functional languages such as Java, C++, Python, and others.

Let's consider the following example of using \ff{goto} object:
\begin{ffcode}
    goto
    [g]
    seq > @
    foo g
    [x] > foo
    x.forward 25
\end{ffcode}
In this case, the object $g$, from which the \ff{forward}/\ff{backward} objects are called, is passed as an argument to another object, and the \ff{forward} object is already will be dataized inside object $foo$.

Similarly, if the \ff{forward}/\ff{backward} objects encapsulate third-party objects whose logic is not known to us, we cannot do the correct jump transformation:
\begin{ffcode}
    goto
    [g]
    foreign_obj > @
    QQ.io.stdout
    "We don't know the logic\n"
    g.forward TRUE
\end{ffcode}

Thus, we can guarantee transformations of \ff{forward} and \ff{backward} objects only if these objects encapsulate objects whose logic is known to us and these \ff{forward} and \ff{backward} objects are inside the \ff{goto} object.

### 2022-10-12 paper/sections/defs.tex
update paper sections

\begin{eodefinition}
An \emph{object} is a collection of attributes, which are uniquely named bindings to objects.
An object is abstract if at least one of its attributes is free---isn’t bound to any object.
Objects, whose implementation is provided by the runtime are called \emph{atoms}.
One object may decorate another object by binding it to the $\varphi$ attribute of itself.
A decorator has its own attributes and bound attributes of its decoratee.
\end{eodefinition}
\begin{eodefinition}
\emph{Dataization} in $\varphi$-calculus is a process of retrieving data from an object.
The dataization of an object at the highest level of composition is similar to the execution of a program in other languages.

We also define a dataization function $\mathbb{D}(x)$, which turns an object $x$ into data.
\end{eodefinition}
\begin{eodefinition}
\emph{Forwarding goto} defines an object \ff{goto}, which encapsulate object \ff{forward} directly or through other objects:
\begin{ffcode}
goto
  [o1]
   |$\leadsto$|o1.forward o
\end{ffcode}
\end{eodefinition}
\begin{eodefinition}
\emph{Backwarding goto} defines an object \ff{goto}, which encapsulate object \ff{backward} directly or through other objects:
\begin{ffcode}
goto
  [o1]
   |$\leadsto$|o1.backward
\end{ffcode}
\end{eodefinition}

Let's consider the following EO program which demonstrates the general syntax of the language:
\begin{ffcode}
memory 0 > x|$\label{ln:def0}$|
[] > app
  [a b] > max
    goto > @
      [g]
        if. > @
          a.gt b
          g.forward a
          b
  [x] > run
    while. > @!
      and.
        x.lt 10
        (x.mod 1).eq 0
      [i]
        x.write > @
          (x.plus 1)|$\label{ln:def1}$|
\end{ffcode}
In this code snippet, \ff{goto} is an \emph{atom}-object with attribute \ff{g}, which dataizes similar to \ff{seq} object;
\ff{memory} is mutable object, which allows to reinitialize the bound object \ff{x} via \ff{.write} attribute;
\ff{eq} is an object, which checks the equality of the objects passed to it;
\ff{if} is an object, which implements behavior of branching;
\ff{seq} is an object that sequentially dataizes all objects within it;
\ff{while} is an object, implementing behavior of loops: its first bound attribute implements condition of loop dataization and second one implies "body" of loop;
\ff{backward} and \ff{forward} are objects, which implements behaviour of jumps: first of them starts dataization of object \ff{g} again, while the second one returns the object passed to it as a parameter and terminates the dataization of object \ff{goto};
\ff{and} is an objects, which implements logical operation \emph{AND}.
There are also objects \ff{or}, \ff{xor} and \ff{not} in the language, that implement the logical operators \emph{OR}, \emph{XOR} and \emph{NOT} respectively.

In terms of $\varphi$-calculus, code at \lrefs{def0}{def1} will be presented as:
\begin{equation}
\begin{split}
& app \mapsto \llbracket \br
& \quad max(a, b) \mapsto \llbracket \br
& \quad \quad \varphi \mapsto \ff{goto}(\llbracket\,g\,\mapsto\,\varnothing,\br
& \quad \quad \quad \varphi \mapsto a.\ff{gt}(b).\ff{if}(g.\ff{forward}(a), b) \,\rrbracket) \br
& \quad \rrbracket \br
& \quad run(x) \mapsto \llbracket \br
& \quad \quad \varphi\ff{!} \mapsto x.\ff{lt}(10).\ff{and}(x.\ff{mod}(1).\ff{eq}(0)) \br
& \quad \quad \quad .\ff{while}(\llbracket\,i \mapsto \varnothing, \br
& \quad \quad \quad \quad \quad \quad \quad \varphi \mapsto x.\ff{write}(x.\ff{plus}(1))\,\rrbracket) \br
& \quad \rrbracket \br
& \rrbracket \\
\end{split}
\end{equation}

\emph{Designations:}
\begin{itemize}
\item "$>$" is used to name objects, where on the left side of ">" is object itself and its name on the right side,
\item "$[]$" is used to specify object parameters,
\item "$@$" is used to denote the object being decorated,
\item "$!$" is used to declare the object as a constant,
\item "$\mapsto$" is used to defines an object, where free attributes stay in the parentheses on the left side and pairs, which represent bound attributes, stay on the right side, in double-square brackets,
\item "$\leadsto$" defines an arbitrary number of objects or chains of encapsulated objects that encapsulate the original object.
\item "$\equiv$" defines the semantic equality of objects, so result of dataization for first object is equal to result of dataization for second one:
\begin{equation}
(\forall{x, y}) (x \equiv y) \Leftrightarrow (\mathbb{D}(x) = \mathbb{D}(y)) .
\end{equation}
\end{itemize}

### 2022-10-12 paper/sections/intro.tex
update paper sections

--- 2022-06-29 paper/skeleton.tex
@@
-\documentclass[sigplan,review,11pt,nonacm,natbib=false]{acmart}
-\settopmatter{printfolios=false,printccs=false,printacmref=false}
-\usepackage[maxnames=1,minnames=1,maxbibnames=100,natbib=true,citestyle=authoryear,bibstyle=authoryear,doi=false,url=false,isbn=false,isbn=false]{biblatex}
-\usepackage{listings}
-\usepackage{graphicx}
-\usepackage{xcolor}
-
-\usepackage[T2A,T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[russian,english]{babel}
-  \renewcommand\ttdefault{cmtt}
-\usepackage{csquotes}
-\usepackage{ffcode}
-\usepackage{CJKutf8}
-\usepackage{paralist}
-\usepackage{cancel} % to enable \cancel command
-\usepackage{anyfontsize} % To get rid of font not found warnings
-\usepackage{tabularx} % for special tables
-\usepackage{amsmath}
-\usepackage{to-be-determined}
-\usepackage{href-ul}
-\usepackage{amsthm}
-\usepackage{tcolorbox} % for algorithm
-  \tcbuselibrary{skins}
-\usepackage{fdsymbol} % for \mathbb
-\usepackage{algpseudocode} % for algorithms
-\usepackage{multicol} % for two cols in BNF
-\usepackage{pgffor} % to enable \foreach
-\usepackage{stmaryrd}
-\usepackage{mathtools}
-
-\newcommand\br{\\[-4pt]}
-\newcounter{rule}
-\renewcommand\therule{R\arabic{rule}}
-\newcommand\rr{\smalltriangleright{}}
-\newcommand\rrule[1]{{\scshape\sffamily\ref{rule:#1}}}
-\newcommand{\jrule}[1]{%
-  \refstepcounter{rule}\label{rule:#1}%
-  \text{\textbf{\rrule{#1}}}}
-
-\newtheorem{definition}{Definition}[section]
-
-\graphicspath{ {./images/} }
-
-\title{Elimination Of Jump Objects}
-\author{author}
-
-\begin{document}
-
-\maketitle
-
-\section{Introduction}
-The problem is known both computer science and soft-
-ware engineering communities for a few decades and formulated by several scientists.
-
-Many of them have offered solutions to this problem. (Look at Related Work)
+The problem of eliminating Jump-like statements is known for both computer science and software engineering communities for a few decades and formulated by several scientists, some of which have suggested solutions for this problem.
 
 The presence of jump statements in the source code makes it impossible to use the functional method of analysis.
+Other program analysis methods, including those based on symbolic execution techniques, will also benefit from the removal of jump statements, which are well-known obstacles to the precision of analysis, as explained by \citet{baldoni2018survey}.
 
-There are an "object-flow" languages where we can control flow through an objects.
-An example of such language is EO (Elementary Objects language).
+There are an "object-flow" languages where the execution flow is controlled by object composition.
+An example of such a language is EO, which is based on $\varphi$-calculus introduced by \citet{bugayenko2021eolang} and formalized by \citet{kudasov2021}.
 This is a strictly object-oriented programming language in which any action is described by creating a new object, or decorating an existing one.
 
-We are trying to answer the following research question: "Is it possible for any program, written on "object-flow" language like EO and containing GOTO objects to find a semantically equivalent program, but without using them?"
-
-\section{Related work}
-To solve the problem of eliminating Jump statements in other programming languages, the following works were published:
-Morris suggested to use regular expressions for replacing GOTO with IF-THEN-ELSE constructs;
-Ramshow proposed an algorithm for Pascal programs;
-Ceccato suggested how to eliminate GOTO during migration of legacy code to Java.
-
-To our knowledge, there is still no method which enables automatic elimination of jump objects in programs written in such an object-flow languages.
-
-\section{Method}
-In this article, we will describe an algorithm that will convert an EO program in such a way that the output returns a semantically equivalent program, but without using the GOTO object.
-
-Some objects in EO programs may need to be platform specific and can’t be composed from other existing objects—they are called \emph{atoms}. 
-So all jump statements are implemented as a
-single \emph{atom}-object GOTO. The implementation of goto-object in EO implies two types of jumps - goto forward and goto backward. So we should consider transformations for both cases.
-
-Since we consider a solution to the problem in strictly object-oriented programming languages, which means that the whole program is a set of objects where some objects can contain others.
-It should be noted that each object in the program has its own level of \emph{nesting} relative to other objects.
-
-\begin{definition} The \emph{nesting} of the current object means the number of objects that contain the current object directly, or that contain objects that contain the current object.
-\end{definition}
-
-The solution we propose contains two types of transformations - forward jump and backward jump.
-The algorithm itself consists in applying these transformations to replace both types of jumps.
-
-\vspace{5mm}
-
-\emph{Designations:}
-
-\begin{itemize}
-\item $\sigma$ - Denotes either an object, a chain of nested objects or the absence of an object.
-
-\item $\delta$ - Denotes a not-empty object or a chain of nested objects that return a not-NULL value when accessed.
-
-\item $\mu$ - Denotes an object or a chain of nested objects that return a boolean value (TRUE/FALSE) when executed.
-\end{itemize}
-
-\newcommand\sgm[1]{$\sigma_#1$}
-\newcommand\dlt[1]{$\delta_#1$}
-\newcommand\m[1]{$\mu_#1$}
-
-We will also look at our transformations in the form of $\varphi$-calculus, on which EO is based.
-The proposed $\varphi$-calculus represents an object model through data and objects, while operations with them are possible through abstraction, application, and decoration.
-The calculus introduces a formal apparatus for manipulations with objects.
-
-$\varphi$-calculus uses an alternative “arrow notation” to denote an object in a more compact way, where free attributes of an abstract object stay in the parentheses on the left side of the mapping symbol $\mapsto$ and pairs, which represent bound attributes, stay on the right side, in double-square brackets.
-
-\subsection{Forward jump}
-Goto forward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      g.forward |\dlt{1}|
-      stdout "Will never be printed"
-\end{ffcode}
-
-It consists of the goto \emph{atom}-object, the abstract object \emph{g}, and the g.forward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.forward} can be called to each of them.
-
-\subsubsection{Simple Forward}
-Consider the simplest example of using goto-forward:
-
-\begin{ffcode}
-goto
-  [g]
-    g.forward |\dlt{1}| > @
-\end{ffcode}
-
-In terms of $\varphi$-calculus, this code will appear as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{forward} (\delta_1) \rrbracket ) \\
-\end{split}
-\end{equation}
-
-Note that in this example, g.forward is simply an attribute of the abstract object \emph{g} and is executed as soon as the queue reaches it.
-Our transformation only considers the jumps that are made when a condition for it is fulfilled.
-In cases where there is unconditional jump, first of all we transform it into conditional jump by adding an additional if-statement - if (TRUE).
-This will not violate the program logic, because without the added if-statement, the jump would always be executed, and statements coming after this jump with a nesting not less that the nesting of the abstract object \emph{g} would never be executed:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing,\br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{forward}(\delta_1), TRUE ) \rrbracket)\\
-\end{split}
-\end{equation}
-
-Same example on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.forward |\dlt{1}|
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward wrapped in an object}
-
-After the conversion described in section 3.1.1, the simplest call of forward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \\
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket) \br
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.(\mu_1.\ff{not}, \delta_2, \delta_1) \rrbracket) \br
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1) \br
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 3 is semantically equivalent to expression 6:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    \varphi \mapsto \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) \rrbracket)
-    \end{matrix}}
-    {\ff{if.}(\mu_1.\ff{not}, \delta_2, \delta_1)}
-    \jrule{1}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
-
-Consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret0}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.forward |\dlt{1}|
-        |\dlt{2}|
-      |\sgm{3}| |$\label{ln:ret1}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret0}-\ref{ln:ret1} as $X$.
-
-It is not difficult to notice that statements which goto-forward "jumps through" will be executed if the condition in the if-statement is not equal to TRUE.
-Otherwise statements following the goto-object itself are executed.
-So we can swap statements and invert the condition into if-statement to get rid of the \emph{g.forward} attribute without violating program logic.
-
-Also, after replacing the jump, we must create an additional \emph{flag} object, which will be changed if the jump condition is met, i.e.
-when in the new if-statement, the 'ELSE' branch will be executed - value of flag will change.
-This is required so that all objects following the if-statement that are attributes of the abstract object \emph{g} are not executed.
-So, by wrapping each object following the jump condition and whose nesting is at least that of the \emph{g} object in an if-statement with a flag value check condition, we make sure that these objects will not be executed when the jump condition is met.
-
-By swapping the statements that follow the if-statement body and after the jump itself, as described above, we get the following replacement for this example:
-the \m{1} object must be inverted with (\m{1}).not;
-in 'THEN' brunch of if-statement places \dlt{2}; in the 'ELSE' brunch creates new object \emph{seq}, consisting of two elements - \dlt{1} and flag's value change, because the jump condition is satisfied.
-
-Thus, after transformation, the program converts to:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{1}||$\label{ln:ret2}$|
-  |\sgm{2}|
-  if.
-    |\m{1}|.not
-    |\dlt{2}|
-    seq
-      |\dlt{1}|
-      flag.write 1
-  if.
-    (eq. (flag 1)).not
-    |\sgm{3}|
-    TRUE|$\label{ln:ret3}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret2}-\ref{ln:ret3} as $X'$.
-
-Now let's look at an example program with nested objects containing goto-forward:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @
-      X
-      |\sgm{4}|
-\end{ffcode}
-
-Applying the transformation, we get:
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}|
-  X'
-  if.
-    (eq. (flag 1)).not
-    |\sgm{4}|
-    TRUE
-\end{ffcode}
-
-\subsubsection{Goto forward inside the while-loop}
-In order to realize the functionality of cycles in EO, generators are provided. A generator is a routine that can be used to control the iteration behaviour of a loop.
-
-The language currently provides a \emph{while} generator, on which other generators are implemented.
-
-The simplest way to call goto-forward inside a \emph{while}-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2) ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-%%\begin{equation}
-%%\begin{split}
-%%& \ff{memory}(flag), \\
-%%& flag.\ff{write}(0), \\
-%%& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} %%\mapsto \varnothing, \\
-%%& \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-%%& \quad \ff{if}.(\mu_1, %%\ff{g}.\ff{forward}(\delta_1), \delta_2) \\
-%%& \quad )\rrbracket) \\
-%%\end{split}
-%%\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\br
-& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \quad \ff{if}.(\mu_1,  \ff{g}.\ff{forward}(\delta_1), \delta_2) )\rrbracket)\\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\br
-& \quad \quad \ff{and}.( \mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
-& \quad \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \rrbracket )\\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\br
-& \quad \ff{and}.(\mu_0, \ff{eq}.(flag  1).\ff{not}), \br
-& \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \br
-& \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0) ) ) ) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 7 is semantically equivalent to expression 10:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto} ( \alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{forward}(\delta_1), \delta_2))\rrbracket) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{and}.( \\
-    & \quad \mu_0, \ff{eq}.(flag  1).\ff{not}), \\
-    & \quad \ff{if}.(\mu_1.\ff{not}, \delta_2, \\
-    & \quad \quad \ff{seq}( \delta_1, flag.\ff{write}(0))) \\
-    \end{matrix}}
-    \jrule{2}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-forward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @ |$\label{ln:ret4}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.forward |\dlt{1}|
-            |\dlt{2}|
-          |\sgm{3}||$\label{ln:ret5}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret4}-\ref{ln:ret5} as $Y$.
-
-In this case, goto-forward is used to exit the body of the while loop. However, every iteration of a while loop checks its own condition if it is true.
-
-Since the jump is executed once the jump condition is true, the while loop will be executed as long as the jump condition is false.
-We can deduce that the condition for the jump is tested at every iteration of the loop, exactly the same as the condition in the while body itself.
-So by combining the jump condition and the while loop condition do not violate the program logic.
-But the point is, once the jump condition is true, the next iteration of the while loop will fail and the loop will end.
-So we only care about the first triggering of the jump condition for goto-forward. To do this, we can create an auxiliary object \emph{flag} that will be TRUE as soon as the jump condition is met.
-
-If the jump condition is met, all objects inside the abstract object \emph{g} and following the goto-forward will not be executed.
-To do this, each of these objects should be wrapped in an additional if-statement, which will check the value of the flag, in other words - whether the jump condition is met or not.
-
-Otherwise, all statements that came after the jump in the while loop will be executed.
-So the combined condition of the while loop will be presented as: while (!flag AND condOfWhile).
-
-Thus, the transformation will be presented as:
-
-\begin{ffcode}
-memory > flag
-flag.write 0
-|\sgm{0}||$\label{ln:ret6}$|
-  while.
-    and.
-      (eq. (flag 1)).not
-      |\m{0}|
-    |\sgm{1}|
-      |\sgm{2}|
-      if.
-        |\m{1}|.not
-        |\dlt{2}|
-        seq
-          |\dlt{1}|
-          flag.write 1
-      if.
-        (eq. (flag 1)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret7}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret6}-\ref{ln:ret7} as $Y'$.
-
-We create an additional \emph{flag} object that will be equal to 1 when the jump condition is triggered and add this condition to the loop body; modify if-statement as described in Section 3.1.2, except that in the 'ELSE' branch we are changing the flag value because the jump condition has been met and the next iteration of the loop should not be executed.
-
-It is worth noting that if goto-forward represent several nested while-loops, then in each of them should be added to the condition of the loop check whether the flag is equal to 1, as in the inner while, from where the jump is made.
-So, every while that has a nesting less than the original nesting and more than the nesting of the abstract object \emph{g} will end without performing the next iteration.
-
-For example, a program with nested while-loops may look like this:
-\begin{ffcode}
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Y
-        |\sgm{4}|
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-memory > flag
-flag.write 0
-while.
-  and.
-    (eq. (flag 1)).not
-    |\m{9}|
-  |\sgm{9}|
-    Y'
-    if.
-      (eq. (flag 1)).not
-      |\sgm{4}|
-      TRUE
-\end{ffcode}
-
-\subsection{Backward jump}
-Goto backward in EO is implemented as:
-
-\begin{ffcode}
-+import org.eolang.gray.goto
-+import org.eolang.io.stdout
-
-goto
-  [g]
-    |\sgm{1}| > @
-      stdout "Will be printed forever"
-      g.backward
-\end{ffcode}
-
-Same as with goto-forward, there is the goto \emph{atom}-object, the abstract object \emph{g}, and the g.backward attribute.
-Several abstract objects such as \emph{g} can be declared inside of goto-object, and the attribute \emph{.backward} can be called to each of them.
-
-\subsubsection{Simple Backward} The simplest example of using goto-backward:
-
-\begin{ffcode}
-goto
-  [g]
-    g.backward > @
-\end{ffcode}
-
-which in terms of $\varphi$-calculus appears as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \varphi \mapsto \ff{g}.\ff{backward} \rrbracket ) \\
-\end{split}
-\end{equation}
-
-This is identical case to that discussed in Section 3.1.1. In cases where the jump is performed without condition, we need to add an additional if-statement, similar to the example in Section 3.1.1:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.( TRUE, \ff{g}.\ff{backward}, TRUE ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-Same code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    if. > @
-      TRUE
-      g.backward
-      TRUE
-\end{ffcode}
-
-\subsubsection{Goto backward wrapped in an object}
-After the conversion described in Section 3.2.1, the simplest call of backward jump will be presented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad  \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 13 is semantically equivalent to expression 16:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 ) \rrbracket) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{eq}.(flag 0), \\
-    & \quad \ff{seq}(flag.\ff{write}(1), \\
-    & \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))) \\
-    \end{matrix}}
-    \jrule{3}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
-
-Consider the following code on EO:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{1}| > @ |$\label{ln:ret8}$|
-      |\sgm{2}|
-      if.
-        |\m{1}|
-        g.backward
-        |\dlt{1}|
-      |\sgm{3}||$\label{ln:ret9}$|
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret8}-\ref{ln:ret9} as $W$.
-
-Note that goto-backward works the same as do-while construction in other languages: the first iteration of the new loop is always executed, and the next only if the condition of loop is TRUE.
-So, all objects that occurs between the declaration of an abstract object \emph{g} and the "jump" itself should be executed before the new while loop once, and all subsequent times were executed depending on the condition of the loop.
-
-Since there is no direct implementation of the do-while construct in EO, but there is an implementation of the while generator, we can resort to a little trick.
-
-To create a do-while emission, we can create a flag globally that will be a condition for our outer loop, whose execution condition will depend on this value.
-The initial value of this flag will be such that the condition for the execution of the added while loop is fulfilled.
-Then, in the body of the loop, we change the value of the flag to the opposite.
-When the jump condition is met, we again change the value of the flag so that as soon as the iteration of the loop is completed, the next iteration will begin, since the loop execution condition will be met.
-
-In order to ensure that when the jump condition is met, all other objects in the body of the newly added while loop are not executed, we wrap them in an additional if-statement, in which we will check whether the jump condition was previously executed.
-
-So, after transformation, the program converts to:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{1}||$\label{ln:ret10}$|
-      |\sgm{2}|
-      if.
-        (|\m{1}|).not
-        |\dlt{1}|
-        flag.write 0
-      if.
-        (eq. (flag 0)).not
-        |\sgm{3}|
-        TRUE|$\label{ln:ret11}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret10}-\ref{ln:ret11} as $W'$.
-
-Let's look at an example of a chain of nested objects containing a goto-backward:
-
-\begin{ffcode}
-
-goto
-  [g]
-    |\sgm{0}| > @
-      W
-      |\sgm{4}|
-
-\end{ffcode}
-
-Applying transformation, we get:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}|
-      W'
-      if.
-        (eq. (flag 0)).not
-        |\sgm{4}|
-        TRUE
-
-\end{ffcode}
-
-\subsubsection{Goto backward inside the while-loop}
-Goto backward also can be called inside a while-loop body.
-
-The simplest way to call goto-backward inside a while-loop is represented as:
-
-\begin{equation}
-\begin{split}
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\mu_0, \br
-& \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2))\rrbracket) \br
-\end{split}
-\end{equation}
-
-The transformation under consideration involves the following steps:
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{while}.(\mu_0, \br
-& \quad \quad \quad \ff{if}.( \mu_1, \ff{g}.\ff{backward}, \delta_1 )))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \br
-& \quad \varphi \mapsto \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \quad \ff{while}.( \br
-& \quad \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
-& \quad \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) ))))\rrbracket) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{equation}
-\begin{split}
-& \ff{memory}(flag), \\
-& flag.\ff{write}(0), \\
-& \ff{while}.(\ff{eq}.(flag 0), \br
-& \quad \ff{seq}(flag.\ff{write}(1), \br
-& \quad \quad \ff{while}.( \br
-& \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \br
-& \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\[-1pt]
-\end{split}
-\end{equation}
-
-\begin{theorem}
-Expression 17 is semantically equivalent to expression 20:
-\end{theorem}
-
-\begin{equation*}
-\dfrac
-    {\begin{matrix}
-    & \ff{goto}(\alpha_1 \mapsto \llbracket \ff{g} \mapsto \varnothing, \\
-    & \quad \varphi \mapsto \ff{while}.(\mu_0, \\
-    & \quad \quad \ff{if}.(\mu_1, \ff{g}.\ff{backward}, \delta_2) ) \rrbracket ) \\
-    \end{matrix}}
-    {\begin{matrix}
-    & \ff{memory}(flag), \\
-    & flag.\ff{write}(0), \\
-    & \ff{while}.(\ff{eq}.(flag 0), \\
-    & \quad \ff{seq}(flag.\ff{write}(1), \\
-    & \quad \quad \ff{while}.( \\
-    & \quad \quad \quad \ff{and}.(\mu_0, \ff{eq}.(flag 0).\ff{not}), \\
-    & \quad \quad \quad \ff{if}.( \mu_1.\ff{not}, \delta_1, flag.\ff{write}(0) )))) \\
-    \end{matrix}}
-    \jrule{4}
-\end{equation*}
-
-To prove that the transformation does not violate program logic, let's consider it with the following abstract case of calling goto-backward.
-
-As discussed in section 3.1.3, the behavior of while is different from other objects in the language. Therefore, the transformation will be slightly different from that described in section 3.2.2.
-
-To understand that the logic is not broken, let's look at an abstract case of calling goto-backward inside a while-loop.
-
-Let's consider the following code:
-
-\begin{ffcode}
-goto
-  [g]
-    |\sgm{0}| > @|$\label{ln:ret12}$|
-      while.
-        |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|
-            g.backward
-            |\dlt{1}|
-          |\sgm{3}||$\label{ln:ret13}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret12}-\ref{ln:ret13} as $Z$.
-
-Similar to the technique we used in section 3.1.3 with goto-forward inside the while loop, in this case, to avoid all subsequent iterations of the inside while loop, we combine its condition with the jump condition.
-As in Section 3.2.2, we create a global flag object, which will be an indicator of the execution of the jump condition.
-As soon as the jump condition is met, we change the flag value, and the next iteration of the inside while loop will fail during the check due to our added combined execution condition.
-
-The rest of the transformation looks identical to that described in section 3.2.2: create a global while loop with a check for moisture values, Invert the jump condition and if the goto-backward condition is met, change the value of the flag object.
-It is also necessary to wrap all objects that lie inside the abstract object \emph{g} in an additional if-statement with a check for the flag value, so that all of them are not fulfilled as soon as the jump condition is met.
-
-The transformation will be presented as:
-
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    |\sgm{0}||$\label{ln:ret14}$|
-      while.
-        and.
-          (eq. (flag 0)).not
-          |\m{0}|
-        |\sgm{1}|
-          |\sgm{2}|
-          if.
-            |\m{1}|.not
-            |\dlt{1}|
-            flag.write 0
-          if.
-            (eq. (flag 0)).not
-            |\sgm{3}|
-            TRUE|$\label{ln:ret15}$|
-
-\end{ffcode}
-
-Let's denote lines \ref{ln:ret14}-\ref{ln:ret15} as $Z'$.
-
-Let's take a look on a program with nested while-loops:
-\begin{ffcode}
-
-goto
-  [g]
-    while. > @
-      |\m{9}|
-      |\sgm{9}|
-        Z
-        |\sgm{4}|
-
-\end{ffcode}
-
-After transformation it will look like:
-\begin{ffcode}
-
-memory > flag
-flag.write 0
-while.
-  eq. (flag 0)
-  seq
-    flag.write 1
-    while.
-      and.
-        (eq. (flag 0)).not
-        |\m{9}|
-      |\sgm{9}|
-        Z'
-        if.
-          (eq. (flag 0)).not
-          |\sgm{4}|
-          TRUE
-
-\end{ffcode}
-
-\subsection{Final algorithm}
-To sum up, we can now fully describe the algorithm itself.
-The first step is to make the transformations, if necessary, described in sections 3.1.1 and 3.2.1, depending on the current transformation.
-The second step is going through all the jumps in the program - forward and backward, and depending on the jump we carry out the required transformations: if needs to make a replacement in the while loop, containing a jump - use transformations 3.1.3 and 3.2.3 accordingly.
-If needs to make a replacement for a simple object that frames the jump - use transformations 3.1.2 and 3.2.2 respectively.
-
-\section{Conclusion}
-As a result of our research, we described an algorithm that automatically converts an input program to an equivalent analog, but without using the \emph{atom} object GOTO.
-We also showed that the program at the output will contain the same logic as the program at the input.
-
-\section{Discussion}
-Our software will simplify programs in EO language and make them more readable without using GOTO objects. In addition, our proof makes it possible to remove all GOTO constructs from programs.
-
-\end{document}
-\endinput
+We are trying to answer the following research question: "Is it possible for any program, written in 'object-flow' language like EO and containing GOTO objects, to find a semantically equivalent program, but without GOTO objects?"
